---
title: "Quickstart"
author: "Alison Appling"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#about

in this  r script I take the get_started vinnette and use my own data

*notes from matt*
> mm@mcmc 
> Rhat, lower is better ~1

#think about getting on a better computer
> vcl - pick windows full blade, base, no apps
>long leaf (cluster)

```{r knitr_init, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=80)
```

# Introduction

This tutorial shows how to estimate stream metabolism using `streamMetabolizer`
and some example data supplied by Bob Hall for French Creek in Laramie, WY.

There are four steps to fitting a metabolism model in `streamMetabolizer`.

1. Prepare and inspect the input data.
2. Choose a model configuration appropriate to your data.
3. Fit the model.
4. Inspect the output.

In this tutorial we will demonstrate these steps for a single model structure and a single set of specifications, but you should also consider other structures and should always tailor the specifications to your dataset and site knowledge. For more details, see:

* [Bayesian Models](models_bayes.html)
* [MLE Models](models_mle.html)
* [Model Types](models_other.html)

# Preliminaries

If you haven't already installed the package, see the [Installation](installation.html) tutorial.

Next load the R libraries. Only `streamMetabolizer` is required to run models, but we'll also be using `dplyr` to inspect the results.
```{r libs, warning=FALSE, message=FALSE}
library(streamMetabolizer)
library(dplyr)
library(here)
library(tidyr)
library(ggplot2)
library(MALDIquant)
library(zoo)
```

# 1. Preparing the input data

Load a small example dataset from the package (data are from French
Creek in Laramie, WY, courtesy of Bob Hall).
We'll use the `streamMetabolizer` standard in defining our day to run from 4 am
(`day_start=4`) to 4 am (`day_end=28`).

Read in data from station 2 and subset... 1 week data?

#depth
depth is one of the trickiest things with the stream metabolizer (according to Maite). We have a couple of options:
1. convert discharge to depth using raymond equation as in calc_depth()
    - potential issue is that the coeffeicients that raymond provides were developed based on an average of a bunch of streams in the US. OUr streams, of course, are in Ecuador, they are peatland, they are very incised. That said, this is the equation that Bernhardt and Battin papers use... so diffensible
2. we also have stage data that can be converted using data collected by kayla and amy.

*we can do both and compare the 2 results*


first let's use the calc_depth() and get some model results

note: stream metabolizer can take NAs but not an empty row

```{r data}


stn03 <- read.csv(here::here("metabolizer_dataframe/stn03_df_feb11_2.csv"))
stn03$solar.time <- as.POSIXct(stn03$solar.time,format="%Y-%m-%d %H:%M:%S",tz="UTC")

#so bad news, DO is mostly at saturation all the time. 
#but looks like after 2022 field season it is below 100%, so lets see if we can get some bettwe number from this
dat <-  stn03%>%filter(
  solar.time > as.POSIXct("2022-09-15 14:00:00",tz="UTC")&
    solar.time < as.POSIXct("2023-06-01 14:00:00",tz="UTC"))

#sort by date time
dat <- dat[order(dat$solar.time , decreasing = FALSE),]


#plot
ggplot(dat,aes(x=solar.time,y=DO.obs)) + geom_point()
```

See the `?metab` help document and the [Data Preparation](data_prep.html) tutorial for more on how to properly format and inspect a dataset.


# Configuring the model: Choose a model structure
I want to use the same model as Maite:

"b_kb_oipi_tr_plrckm"

b = baysian
kb = partial pooling of k600
oipi = both process and observational errors: "oipi"
tr = trapazoidal (the way that they calculate the metabolism); maite uses this way, and this is generally what others use too.

```{r bayes_name}

bayes_name <- mm_name(type='bayes', pool_K600='binned', err_obs_iid=TRUE, err_proc_iid=TRUE)
bayes_name

```

## 2b. Set the specifications/ priors

We now pass the model name to `specs()` to get a
list of default specifications for this model.
```{r bayes_specs}
bayes_specs <- specs(bayes_name)

bayes_specs <- specs(bayes_name, burnin_steps=500, saved_steps=1000, n_cores=1, GPP_daily_mu=3, GPP_daily_sigma=2)


#this is a function the maite uses in here data, I 
prior_K600_lnQ_nodes_meanlog <- function(depth, slope) {
  4.77 + 0.55*log(slope) + (-0.52*log(depth))
}

#look at min and max discharge, 
#for stn2 it is: 0.002120185 to 0.10986061
#take the ln() and enter in as prior
bayes_specs$K600_lnQ_nodes_centers<-seq(-6, -1.5, 0.5)

#do below later? maybe I don't need to??

###CHANGE DEPTH AND SLOPE FOR EACH SITE
#specs$K600_lnQ_nodes_meanlog <- rep(prior_K600_lnQ_nodes_meanlog(slope=0.005, depth=0.68),length(specs$K600_lnQ_nodes_centers))
#specs$K600_lnQ_nodes_sdlog <- rep(0.7, length(specs$K600_lnQ_nodes_centers))


```



#run model

fingers crossed ova heya

crossed fingas ova theeer

crossed fingas everywh\eeer

```{r bayes_fit}

#remove discharge if not pooling k600
mm <- metab(bayes_specs, data=dat#%>%select(!discharge)
            )
```

Feb 11, stn03 all data, k600 partialy poiled start=1:49 end = before 2:18
Feb 11, stn03 summer 2021, k600 partialy poiled start=3:06 end = before 3:46
Feb 11, stn03 fall 2021 - 6136 obs, k600 partialy poiled start=3:56 end = before 3:46

# 4. Inspecting the model

Once you've fit a model, you can inspect the output with functions including
`predict_metab()` and `plot_metab_preds()`, `predict_DO()` and `plot_DO_preds()`,
`get_params()`, and `get_fit()`.

Start by simply printing the model to the console.
```{r}
mm
```

Here are the daily metabolism predictions from the model:
```{r bayes_pred_tbl}
predict_metab(mm)
```

```{r bayes_pred_fig, fig.width=5, fig.height=5}
plot_metab_preds(mm)
```

You can inspect more of the fitted daily parameters, including K600, with `get_params()`:
```{r}
get_params(mm)
```

Here are the first few dissolved oxygen predictions from the model (`DO.mod`).
They are returned along with the input data for convenience.
```{r bayes_pdo_tbl, results='asis'}
predict_DO(mm) %>% head()
```

And here are the dissolved oxygen predictions in a figure:
```{r bayes_pdo_fig, fig.width=5, fig.height=5}
plot_DO_preds(mm)

#dots are my date, line is model
```
#save model

```{r save model, fig.width=5, fig.height=5}

#save model
#save(mm, file = "model_stn03_partially-pooled_stn04_feb11_all.RData")

predictions <- predict_metab(mm)
#write.csv(predictions,here::here("StreamMetabolizer/Predictions/MetabPredictions_stn03_all_feb11df.csv"))

```


#inspect model

For Bayesian models only, you can dig even deeper using `get_mcmc`, which
returns a `stanfit` object that can be inspected using the `rstan` package.
(These traceplots are pretty bad because we used so few MCMC iterations. You
should strive for better in your final models.)


```{r, fig.width=5, fig.height=5}

mcmc <- get_mcmc(mm)
rstan::traceplot(mcmc, pars='K600_daily', nrow=3)
```

The `get_fit()` function returns a list of data.frames, one per temporal
resolution, containing all fitted values and details about their distributions
and convergence. Here are just the overall metrics of model convergence
(`Rhat`s, or potential scale reduction statistics; see Gelman and Rubin 1992 or
Brooks and Gelman 1998):
```{r}
get_fit(mm)$overall %>%
  select(ends_with('Rhat'))
```

And here is a list of all column names available through `get_fit()`:
```{r}
get_fit(mm) %>%
  lapply(names)
```
#maite's model inspection:

###how to evaluate?
1. R hat associated with entire model - R hat for process error (you want lower than 1.1)
check relationship between k600 and ER -- you don't want a strong relationship!!

2. range of variability in k600 (shouldn't be too variable!)
3. relationship between k600 and discharge (shouldn't be too strong!)



ASSESSMENT
K600_daily_sigma_Rhat<-in KQ_overall
err_obs_iid_sigma_Rhat<-in overall
err_proc_iid_sigma_Rhat<-in overall
K_range<-??
neg_GPP<-check percentage and if looks ok just remove days with the wrong sign
pos_ER<-idem


"sensitivity test"

mmspecs$GPP_daily_mu<-10
specs$ER_daily_mu<--15
mm2<-metab(specs = specs, data = s_ts)

Hau idatzi du Maite Arroita (arroita.maite@gmail.com) erabiltzaileak (2024 uzt. 9(a), ar. (12:47)):

```{r}
#K600_daily_sigma_Rhat
mm@fit$KQ_overall$K600_daily_sigma_Rhat

#err_obs_iid_sigma_Rhat
mm@fit$overall$err_obs_iid_sigma_Rhat

#err_proc_iid_sigma_Rhat
mm@fit$overall$err_proc_iid_sigma_Rhat

#K_range


###inspect data
data_inspection <- get_params(mm)


```

```{r plot}
dat$date <- as.Date(dat$solar.time,format="%Y-%m-%d")

dat_summary<- dat%>%group_by(date)%>%
  summarise(
    discharge = mean(discharge),
    light = mean(light)
  )
data_inspection <- left_join(data_inspection,dat_summary,by="date")

ggplot(data_inspection,aes(x=date,y=GPP.daily)) + geom_point()
ggplot(data_inspection,aes(x=date,y=ER.daily)) + geom_point()

ggplot(data_inspection,aes(x=date,y=K600.daily)) + geom_point()

ggplot(data_inspection,aes(x=discharge,y=GPP.daily)) + geom_point()
ggplot(data_inspection,aes(x=discharge,y=ER.daily)) + geom_point()
ggplot(data_inspection,aes(x=GPP.daily,y=ER.daily)) + geom_point()


ggplot(data_inspection,aes(x=K600.daily,y=GPP.daily)) + geom_point()

ggplot(data_inspection,aes(x=light,y=GPP.daily)) + geom_point()


ggplot(data_inspection,aes(x=discharge,y=light)) + geom_point()

```

#write out data inspection

```{r write out}

#write.csv(data_inspection,here::here("StreamMetabolizer/Predictions/data_inspection_stn03_feb11_2021summer.csv"))

#save model
#save(mm, file = "model_stn03_partially-pooled_stn04_feb11_all.RData")


#write.csv(predictions,here::here("StreamMetabolizer/Predictions/MetabPredictions_stn03_2021summer_feb11df.csv"))

```