---
title: "DeparturePlot_metrics"
author: "K. M. Whitmore"
date: "2025-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load library
library(dplyr)
library(tidyr)
library(here)
#Load library to plot ellipse and to calcuate type II regressions
library(ellipse)
library(lmodel2)
library(streamMetabolizer)
library(ggplot2)
library(unitted)
```

## About
In this R markdown I will use pCO2 and DO data collected at the Gavilán wetland outlet to calculate metrics in Vachon et al 2024

https://aslopubs.onlinelibrary.wiley.com/doi/10.1002/lol2.10135


#read WL data
```{r WL data}
WL_02 <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_02$DateTime_1 <- as.POSIXct(WL_02$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_02$DateTime <- ifelse(is.na(WL_02$DateTime_1)==TRUE,paste(WL_02$DateTime,"00:00:00",sep=" "),WL_02$DateTime )
WL_02$DateTime <- as.POSIXct(WL_02$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_02$DateTime_1 <- NULL

#test for duplicates
test <- WL_02$DateTime[duplicated(WL_02$DateTime)]
test2 <- as.data.frame(test)

```
#read DO data
```{r DO data}

DO_df <- read.csv(here::here("data_cleaned/DO_01_cleaned.csv"))

DO_df$DateTime_1 <- as.POSIXct(DO_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
DO_df$DateTime <- ifelse(is.na(DO_df$DateTime_1)==TRUE,paste(DO_df$DateTime,"00:00:00",sep=" "),DO_df$DateTime )
DO_df$DateTime <- as.POSIXct(DO_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
DO_df$DateTime_1 <- NULL

DO_df <- unique(DO_df)
#test for duplicates
test <- DO_df$DateTime[duplicated(DO_df$DateTime)]
test2 <- as.data.frame(test)

```
#read CO2 data
```{r CO2 data}

CO2_df <- read.csv(here::here("data_cleaned/CO2_01_max10000_cleaned.csv"))

CO2_df$DateTime_1 <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime <- ifelse(is.na(CO2_df$DateTime_1)==TRUE,paste(CO2_df$DateTime,"00:00:00",sep=" "),CO2_df$DateTime )
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime_1 <- NULL

CO2_df <- unique(CO2_df)
CO2_df <- CO2_df%>%drop_na(CO2_ppm_adjusted)


#convert to umol per l
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15
CO2_df$pCO2_air_ppm <- 418.53 # 2022 average manoa
CO2_df$air_pressure_atm <- CO2_df$Total_hPa / 1013.25 - 0.000967841
CO2_df$pCO2_air_atm <-  CO2_df$pCO2_air_ppm / 10^6  * CO2_df$air_pressure_atm
CO2_df$pCO2_w_atm <- CO2_df$CO2_ppm_adjusted / 10^6 
#henry's constant adjust for temp
CO2_df$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(CO2_df$WLTemp_01_c+273.15) - 1/T_STP_K))
CO2_df$KH_mol.m3.atm <- CO2_df$KH_mol.l.atm * 1000
CO2_df$CO2_sat_mol.L <- CO2_df$KH_mol.l.atm*CO2_df$pCO2_air_atm
CO2_df$CO2_sat_umol.L <- CO2_df$CO2_sat_mol.L*10^6
CO2_df$CO2_mol.L <- CO2_df$KH_mol.l.atm*CO2_df$pCO2_w_atm
CO2_df$CO2_umol.L <- CO2_df$CO2_mol.L*10^6

CO2_df <- CO2_df%>%select(DateTime,CO2_ppm_adjusted,pCO2_air_ppm,air_pressure_atm,CO2_umol.L,CO2_sat_umol.L)

#test for duplicates
test <- CO2_df$DateTime[duplicated(CO2_df$DateTime)]
test2 <- as.data.frame(test)

```
#join data
```{r join data}

Stn01 <- left_join(WL_02,DO_df, by=c("DateTime"))
Stn01 <- full_join(Stn01,CO2_df, by=c("DateTime"))



Stn01$DO_sat <- calc_DO_sat(temp=u(Stn01$WLTemp_c,"degC"), press=u(Stn01$AirPres_kpa*10,"mb"), sal=u(0,"PSU")) # units are checked

#convert to umol
Stn01$DO_sat_umolperL <- as.numeric(Stn01$DO_sat)/1000 / 32 * 10^6
Stn01$DO_umolperL <- Stn01$DO_mgL/1000 / 32 * 10^6
Stn01$DO_departure <- Stn01$DO_sat_umolperL - Stn01$DO_umolperL

#convert to umol
Stn01$DO_sat_umolperL <- as.numeric(Stn01$DO_sat)/1000 / 32 * 10^6
Stn01$DO_umolperL <- Stn01$DO_mgL/1000 / 32 * 10^6
Stn01$DO_departure <- Stn01$DO_umolperL - Stn01$DO_sat_umolperL 

Stn01$CO2_departure <-  Stn01$CO2_umol.L - Stn01$CO2_sat_umol.L 

#date
Stn01$Date <- as.Date(Stn01$DateTime)

Stn01 <- unique(Stn01)


#test for duplicates
test <- Stn01$DateTime[duplicated(Stn01$DateTime)]
test2 <- as.data.frame(test)

#write.csv(Stn01,here::here("MergedFiles/Stn01_May7.csv"))
```

## visualize data 


```{r plots, echo=FALSE}
p <- ggplot(Stn01 %>%filter(Date>as.Date("2021-05-05")&Date<as.Date("2022-07-01"))) +
  geom_point(aes(x=DateTime,y=as.numeric(DO_umolperL)),color="green") +
  geom_point(aes(x=DateTime,y=Q_m3s*1000),color="blue")
  
```

## summarise daily data
```{r daily ave, echo=FALSE}
new_df_bind <- Stn01 %>%group_by(Date)%>%
  summarise(Q_m3s_ave = mean(Q_m3s,na.rm = T),
            Q_m3s_min = min(Q_m3s,na.rm = T),
            Q_m3s_max = max(Q_m3s,na.rm = T),
            DO_mgL_ave = mean(DO_mgL,na.rm = T),
            WLTemp_c_ave = mean(WLTemp_c,na.rm=T))
new_df_bind$Q_mgL_delta <- new_df_bind$Q_m3s_max - new_df_bind$Q_m3s_min

new_df_bind <- unique(new_df_bind)

```

##calc centroid & offset

Centroid:	Time averages of O2 and CO2 departure values
> The quadrant in which a cloud is located provides information about the average net effect of different environmental processes influencing O2 and CO2 dynamics

Offset: Sum of CO2 and O2 departures averages
> Characterizes extent or relative role of external inputs, anaerobic respiration, carbonate precipitation and/or increase in water temperature

#1/[slope] 
Inverse of the absolute slope of type II linear regression 
> The inverse of the cloud absolute slope (i.e., 1/[slope]) is the EQ, reflecting the integrated stoichiometry of the ecosystem.

##Stretch
Major axis length of 95% covariance error ellipse 
> Characterizes the strength of the dominant process (usually metabolism) driving O2 and CO2 departures

#Width 
Minor axis length of 95% covariance error ellipse 
> Characterizes the variability around the dominant process (major axis)


```{r stretch and Width, echo=FALSE}


new_df <- Stn01%>%drop_na(CO2_departure)%>%drop_na(DO_departure)%>%select(Date)
new_df <- unique(new_df)

metrics <- data.frame(date=NA, meanCO2dep=NA,meanO2dep=NA,minCO2dep=NA,minO2dep=NA,offset=NA,EQ=NA,width=NA,stretch=NA,slope=NA,n.obs=NA)

for(i in 1:nrow(new_df)){
  Date_select <- new_df$Date[i]
  Stn01_Date_select <- Stn01%>%
    filter(Date==Date_select)%>%drop_na(CO2_departure)%>%drop_na(DO_departure)
  if(nrow(Stn01_Date_select)> 88){ #only process days that are missing 2hr or less worth of data
  n.obs <- nrow(Stn01_Date_select)
  
  x <- Stn01_Date_select$CO2_departure
  y <- Stn01_Date_select$DO_departure
  
  #calculating means
  mu <- c(mean(x,na.rm=TRUE),mean(y,na.rm=TRUE))
  min <- c(min(x,na.rm=TRUE),min(y,na.rm=TRUE))
  
  #ellipe axis length calculation
  corMat = cor(cbind(x,y))
  covMat <- var(cbind(x,y))
  evals <- eigen(covMat)$values
  ell.len <- 2*sqrt(5.991*evals)
  
  #Type II regression for slope calculation
  reg <- lmodel2(y~x,nperm=99)
  inter <- reg$regression.results[2,2]
  slope <- reg$regression.results[2,3]
  corr <- reg$r
  #reg
  
  #gathering all metrics in a data frame
  metrics_add <- data.frame(date=Date_select, meanCO2dep=mu[1],meanO2dep=mu[2],minCO2dep=min[1],minO2dep=min[2],offset=mu[1]+mu[2],EQ=1/abs(slope),width=ell.len[2],stretch=ell.len[1],slope=slope,n.obs=n.obs)
  
  metrics <- rbind(metrics_add,metrics)
  }
}

departure_metrics <- left_join(metrics,new_df_bind,by=c("date"="Date"))
```
#write out
```{r write out, echo=FALSE}
#write.csv(departure_metrics,here::here("Departure_files/departure_metrics_may6.csv"),row.names = FALSE)
```

#plot it
```{r plot, echo=FALSE}

plot_df <- left_join(departure_metrics# %>%select(date)
                     ,Stn01,by=c("date"="Date"))

ggplot(plot_df %>%filter(slope<0)) +
#  stat_ellipse(aes(x = CO2_departure, y = DO_departure,color=as.factor(date)))+
  geom_smooth(aes(x = CO2_departure, y = DO_departure,color=as.factor(date)), formula = y ~ x,method='lm')+
    geom_point(aes(x = meanCO2dep, y = meanO2dep),color="black",shape=1) +
    geom_abline(intercept = 0, slope = -1) +
  theme(legend.position="none")

```


#plot it
```{r plot, echo=FALSE}
p1 <- ggplot(departure_metrics,aes(x=Q_ave,y=offset)) + geom_point()
p2 <- ggplot(departure_metrics,aes(x=DO_ave,y=offset)) + geom_point()
p3 <- ggplot(departure_metrics,aes(x=WLTemp_ave,y=offset)) + geom_point()

p4 <- ggplot(departure_metrics,aes(x=WLTemp_ave,y=width)) + geom_point()
p5 <- ggplot(departure_metrics ,aes(x=date,y=stretch)) + geom_point()

```

