---

title: "CO2_EC"
author: "Kayla Emerson"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Bolstad2)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About

date: 2021-07-14
Injection in tributary of Gavilan

### We start by reading in an then cleaning data, file 

## read in CO2 data

Select data collected during injection period
```{r co2, echo=FALSE}

inj_df <- read.csv(here::here("MergedFiles/Inj_df_2019July14.csv"))
inj_df$DateTime <- as.POSIXct(inj_df$DateTime,format="%Y-%m-%d %H:%M:%S", tz="UTC")
```


## Plot CO2 for Viasala @ 80m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(inj_df,
    x = ~DateTime, y = ~pCO2_120m, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for 100m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
p <- plot_ly(inj_df,
    x = ~DateTime, y = ~log(pCO2_120m_adj), type = 'scatter', mode = 'markers') 

p2 <- add_trace(p, x = inj_df$DateTime, y = log(inj_df$pCO2_80m_adj), 
                       type = "scatter")

p2
```


## Finding the mean for before, during, and after the plateau

EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau

preplat_80m <- filter(inj_df, DateTime >= as.POSIXct("2021-07-14 10:05:00", tz = "UTC") & DateTime < as.POSIXct("2021-07-14 10:20:00", tz = "UTC"))
preplat_120m <- filter(inj_df, DateTime >= as.POSIXct("2021-07-14 10:05:00", tz = "UTC") & DateTime < as.POSIXct("2021-07-14 10:20:00", tz = "UTC"))


#calculate mean
preplatmean80m = mean(preplat_80m$pCO2_80m_adj)
preplatmean120m = mean(preplat_120m$pCO2_120m)


### Change data frame, date and wanted time frame as needed 
plat_80m <- filter(inj_df, DateTime >= as.POSIXct("2021-07-14 11:50:00", tz = "UTC") & DateTime < as.POSIXct("2021-07-14 11:55:00", tz = "UTC"))
plat_120m <- filter(inj_df, DateTime >= as.POSIXct("2021-07-14 11:50:00", tz = "UTC") & DateTime < as.POSIXct("2021-07-14 11:55:00", tz = "UTC"))

#now find the mean of this filtered subset
platmean80m = mean(plat_80m$pCO2_80m_adj)
platmean120m = mean(plat_120m$pCO2_120m_adj)


```


## Calculating CO2 in the air (look at data before or after vaisalas went into the water)
```{r plot, echo=FALSE}
# use manoa for this
```


##calc kc02 for river stretch using kriddie's own brain 
I'm going off road, baby

#First comes the flux

We are pulling from methods in stream ecology now 
eq) 31.1  describes decay rate of leaves over time
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: final weight
  wi: initial weight
  t: time
  
adjusted for decay rate of CO2 over meters
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: co2 mass at 50 m (concentration * discharge)
  wi: co2 mass at 10m  (concentration * discharge)
  t: meters

```{r kdub rules the roost}
#convert ppm to mg/l is the easiest thing in the world becaust it is 1:1

#difference between plateu and baseline for upstream and downstream
C_mgperL_80m <- (platmean80m - preplatmean80m)

C_mgperL_120m <- (platmean120m - mean(preplatmean120m))

#We don't have discharge (as far as I can tell), but let's assume Q is the same


#stream reach length
dist = 120-80

km <- -log(C_mgperL_120m/(C_mgperL_80m))/dist
#km units: 1/m
```
#convert k in meters to time
kgas,t = kgas,m * v

kgas,t: decay rate over time
kgas,m: decay rate over meters (calculates in chunk above)
v: mean velocity of stream

```{r meters to time }


#mean velocity of stream reach from salt injection

#we will use the EC data collected at 120m
EC_Data <- read.csv(here::here("Inj_2021July14/SaltInjectionData_120m_2021-07-14.csv"))
#colnames(EC_Data) <- c("DateTime","LowRange","HighRange","Temp_c")
EC_Data$DateTime <- as.POSIXct(paste("07/14/2021",EC_Data$Time,sep=" "),format="%m/%d/%Y %H:%M:%S", tz = "UTC")

plot_ly(EC_Data, x = ~DateTime, y = ~conductivity_uS, type = 'scatter', mode = 'markers') 

#manually found plateau time
plateau <- as.POSIXct("2021-07-14 11:54",tz="UTC")

#isolate time between salt injection and plateu, subtract out background

df <- EC_Data%>%filter(DateTime<plateau)
df$conductivity_uS <- df$conductivity_uS - 8.7 #background is 8.7
df$Time <- format(as.POSIXct(df$DateTime), format = "%H:%M:%S")
df$seconds <- period_to_seconds(hms(df$Time)) - min(period_to_seconds(hms(df$Time)))
df <- df%>%drop_na(conductivity_uS)

#find Mean Travel Time (MTT)
x <- sintegral(df$seconds, df$conductivity_uS, n.pts = nrow(df))
df_int <- data.frame(matrix(ncol = 2, nrow = nrow(as.data.frame(x$x))))
colnames(df_int) <- c("sec","sum")
df_int$sec <- x$x
df_int$sum <- x$y
AUC <- x$int

MTT <- df_int[which.min(abs(AUC/2-df_int$sum)),]$sec

dist = 120-0


v = dist/MTT #units (m/s)
kt = km * v #units (1/s)
kCO2_mperd <- kt*86400


#wat if we used the co2 injection wich we actually have at both 80m and 120m? 
#80 comes to platue at 10:32:25, 120m comes to platue at 10:35:20

x80m_time <- as.POSIXct("2021-07-14 10:32:25", format="%Y-%m-%d %H:%M:%S",tz="UTC")
x120m_time <- as.POSIXct("2021-07-14 10:35:20", format="%Y-%m-%d %H:%M:%S",tz="UTC")

MTT <- as.numeric(difftime(x120m_time,x80m_time,units="secs"))

dist = 120-80

v = dist/MTT #units (m/s)
kt = km * v #units (1/s)
kCO2_mperd <- kt*86400
  
```

#k600
convert to k to k600
```{r convert to k6000}

# Find average water temp for injection
wdv_df <- read.csv(here::here("Inj_2021July14/SaltInjectionNotes_2021-07-14.csv"))

WaterTempC_ave <- mean(wdv_df$finaltemp_C,na.rm=TRUE)

#calc sc
Sc <- 1911.1 - 118.11*WaterTempC_ave + 3.4527*(WaterTempC_ave)^2 - 0.04132*(WaterTempC_ave)^3

K600 <- kCO2_mperd * (600/Sc)^(-0.5)

print(K600)
```



