---
title: "LongTermData Plots Feb17"
author: "Kriddie"
date: "2025-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This R markdown is intended to contain all plots used for the publication of continuous long term data collected at cayambe coaca national park from 2019 to 2023

```{r import library}
library(here)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(zoo)
library(plotly)
library(cowplot)
```

## Read in data

```{r read in data and merge, echo=FALSE}
####stn01
WL_df <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df <- read.csv(here::here("data_cleaned/CO2_01_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

stn01 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))

#### station 2
WL_df <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df <- read.csv(here::here("data_cleaned/CO2_02_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

stn02 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))

###stn03
WL_df <- read.csv(here::here("data_cleaned/WL_03_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df <- read.csv(here::here("data_cleaned/CO2_03_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

stn03 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))
stn03 <- stn03%>%filter(DateTime > as.POSIXct("2021-03-15 03:30:00"))

### station 04
WL_df <- read.csv(here::here("data_cleaned/WL_04_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df <- read.csv(here::here("data_cleaned/CO2_04_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

stn04 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))

### station 05 & 06
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))%>%drop_na(WL_m)
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")

stn06 <- read.csv(here::here("data_cleaned/WL_06_cleaned.csv"))%>%drop_na(WL_m)
stn06$DateTime <- as.POSIXct(stn06$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")

stn_colmillo <- full_join(stn05,stn06,by=c("DateTime"))

### join all
all_stn <- full_join(stn01%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_01 = Q_m3s,CO2_ppm_01=CO2_ppm_adjusted),
                     stn02%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_02 = Q_m3s,CO2_ppm_02=CO2_ppm_adjusted),
                     by="DateTime")
all_stn <- full_join(all_stn,
                     stn03%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_03 = Q_m3s,CO2_ppm_03=CO2_ppm_adjusted),
                     by="DateTime")
all_stn <- full_join(all_stn,
                     stn04%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_04 = Q_m3s,CO2_ppm_04=CO2_ppm_adjusted),
                     by="DateTime")

all_stn <- all_stn%>%filter(DateTime < as.POSIXct("2023-04-01 11:15:00",tz="UTC"))


```

# context stats


```{r context stats, echo=FALSE}

#how many days were above detection?
stn01_summary <- stn01
stn01_summary$date <- as.Date(stn01_summary$DateTime)
stn01_summary_1 <- stn01_summary%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))%>%drop_na(mean_co2_adj)

stn01_above_detection  <- stn01
stn01_above_detection$CO2_ppm <- ifelse(stn01_above_detection$CO2_ppm< 10000,NA,stn01$CO2_ppm)
stn01_above_detection$date <- as.Date(stn01_above_detection$DateTime)
stn01_above_detection_sumary <- stn01_above_detection%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm))%>%drop_na(mean_co2)

#how many days of data collection?
stn01_summary_2 <- stn01_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

stn02_summary <- stn02
stn02_summary$date <- as.Date(stn02_summary$DateTime)
stn02_summary_2 <- stn02_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))


stn03_summary <- stn03
stn03_summary$date <- as.Date(stn03_summary$DateTime)
stn03_summary_1 <- stn03_summary%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))%>%drop_na(mean_co2_adj)
#how many days of data collection?
stn03_summary_2 <- stn03_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

#how many days of data collection?
stn04_summary <- stn04
stn04_summary$date <- as.Date(stn04_summary$DateTime)
stn04_summary_2 <- stn04_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

colm_summary <- stn_colmillo
colm_summary$date <- as.Date(colm_summary$DateTime)
colm_summary_2 <- colm_summary%>%group_by(date)%>%
  summarise(mean_Q5 = mean(Q_m3s.x,na.rm=TRUE),
            mean_Q6 = mean(Q_m3s.y,na.rm=TRUE))%>%
  filter(mean_Q6!="NaN")


precip <- read.csv(here::here("Weather_station/M5025_Precipitation.csv"))
precip$DateTime <- as.POSIXct(precip$fecha,format="%m/%d/%y %H:%M",tz="UTC")
precip$date <- as.Date(precip$DateTime)

precip_daily <- precip%>%group_by(date)%>%
  summarise(daily_accu = sum(precipt_mm))

temp <- read.csv(here::here("Weather_station/M5025_AirTemp.csv"))
temp$DateTime <- as.POSIXct(temp$fecha,format="%m/%d/%y %H:%M",tz="UTC")
temp$date <- as.Date(temp$DateTime)

temp_daily <- temp%>%group_by(date)%>%
  summarise(daily_temp = mean(AirTemp_c))

```

## Research Question 1:

How do carbon concentration respond to storm events at station 1

## extract highest peaks from each month

```{r storm hysterises, echo=FALSE}

storm1_peak = as.POSIXct("2019-07-14 14:30:00",tz="UTC")
storm1_begin = as.POSIXct("2019-07-14 00:45:00",tz="UTC")
storm1_end = as.POSIXct("2019-07-16 08:00:00",tz="UTC")

storm2_peak = as.POSIXct("2019-08-14 07:45:00",tz="UTC")
storm2_begin = as.POSIXct("2019-08-13 18:30:00",tz="UTC")
storm2_end = as.POSIXct("2019-08-15 05:15:00",tz="UTC")

storm2.1_peak = as.POSIXct("2019-08-04 18:30:00",tz="UTC")
storm2.1_begin = as.POSIXct("2019-08-01 13:45:00",tz="UTC")
storm2.1_end = as.POSIXct("2019-08-08 06:15:00",tz="UTC")

storm3_peak = as.POSIXct("2019-09-20 20:45:00",tz="UTC")
storm3_begin = as.POSIXct("2019-09-20 14:30:00",tz="UTC")
storm3_end = as.POSIXct("2019-09-22 07:00:00",tz="UTC")

storm4_peak = as.POSIXct("2019-10-24 05:00:00",tz="UTC")
storm4_begin = as.POSIXct("2019-10-23 11:00:00",tz="UTC")
storm4_end = as.POSIXct("2019-10-29 00:30:00",tz="UTC")


storm5_peak = as.POSIXct("2021-06-21 04:45:00",tz="UTC")
storm5_begin = as.POSIXct("2021-06-19 00:45:00",tz="UTC")
storm5_end = as.POSIXct("2021-06-23 02:15:00",tz="UTC")

storm6_peak = as.POSIXct("2021-07-01 02:45:00",tz="UTC")
storm6_begin = as.POSIXct("2021-06-29 22:45:00",tz="UTC")
storm6_end = as.POSIXct("2021-07-03 22:30:00",tz="UTC")

storm7_peak = as.POSIXct("2021-08-02 15:30:00",tz="UTC")
storm7_begin = as.POSIXct("2021-08-01 23:00:00",tz="UTC")
storm7_end = as.POSIXct("2021-08-04 12:00:00",tz="UTC")

storm8_peak = as.POSIXct("2021-09-06 17:00:00",tz="UTC")
storm8_begin = as.POSIXct("2021-09-05 00:30:00",tz="UTC")
storm8_end = as.POSIXct("2021-09-07 08:30:00",tz="UTC")

storm9_peak = as.POSIXct("2021-10-21 19:30:00",tz="UTC")
storm9_begin = as.POSIXct("2021-10-20 07:30:00",tz="UTC")
storm9_end = as.POSIXct("2021-10-22 16:00:00",tz="UTC")

storm10_peak = as.POSIXct("2021-11-19 10:00:00",tz="UTC")
storm10_begin = as.POSIXct("2021-11-18 22:15:00",tz="UTC")
storm10_end = as.POSIXct("2021-11-20 06:00:00",tz="UTC")

storm11_peak = as.POSIXct("2021-12-18 15:15:00",tz="UTC")
storm11_begin = as.POSIXct("2021-12-16 09:30:00",tz="UTC")
storm11_end = as.POSIXct("2021-12-24 11:00:00",tz="UTC")

storm12_peak = as.POSIXct("2022-03-15 14:15:00",tz="UTC")
storm12_begin = as.POSIXct("2022-03-13 20:00:00",tz="UTC")
storm12_end = as.POSIXct("2022-03-16 20:15:00",tz="UTC")

storm13_peak = as.POSIXct("2022-04-21 01:00:00",tz="UTC")
storm13_begin = as.POSIXct("2022-04-18 20:00:00",tz="UTC")
storm13_end = as.POSIXct("2022-04-23 05:15:00",tz="UTC")

storm14_peak = as.POSIXct("2022-05-16 11:45:00",tz="UTC")
storm14_begin = as.POSIXct("2022-05-14 07:45:00",tz="UTC")
storm14_end = as.POSIXct("2022-05-22 14:00:00",tz="UTC")

storm15_peak = as.POSIXct("2022-06-25 12:00:00",tz="UTC")
storm15_begin = as.POSIXct("2022-06-22 08:15:00",tz="UTC")
storm15_end = as.POSIXct("2022-06-30 03:15:00",tz="UTC")

storm16_peak = as.POSIXct("2022-07-04 07:30:00",tz="UTC")
storm16_begin = as.POSIXct("2022-07-01 22:00:00",tz="UTC")
storm16_end = as.POSIXct("2022-07-08 21:00:00",tz="UTC")

storm17_peak = as.POSIXct("2022-08-10 12:15:00",tz="UTC")
storm17_begin = as.POSIXct("2022-08-09 06:00:00",tz="UTC")
storm17_end = as.POSIXct("2022-08-18 23:30:00",tz="UTC")

storm18_peak = as.POSIXct("2022-09-11 06:30:00",tz="UTC")
storm18_begin = as.POSIXct("2022-09-10 01:45:00",tz="UTC")
storm18_end = as.POSIXct("2022-09-16 07:15:00",tz="UTC")

storm19_peak = as.POSIXct("2022-10-19 12:15:00",tz="UTC")
storm19_begin = as.POSIXct("2022-10-18 21:45:00",tz="UTC")
storm19_end = as.POSIXct("2022-10-21 21:00:00",tz="UTC")

storm20_peak = as.POSIXct("2022-11-20 22:30:00",tz="UTC")
storm20_begin = as.POSIXct("2022-11-20 12:45:00",tz="UTC")
storm20_end = as.POSIXct("2022-11-23 19:15:00",tz="UTC")

storm21_peak = as.POSIXct("2022-12-14 18:15:00",tz="UTC")
storm21_begin = as.POSIXct("2022-12-14 10:00:00",tz="UTC")
storm21_end = as.POSIXct("2022-12-21 10:30:00",tz="UTC")

storm22_peak = as.POSIXct("2023-01-24 16:00:00",tz="UTC")
storm22_begin = as.POSIXct("2023-01-23 22:15:00",tz="UTC")
storm22_end = as.POSIXct("2023-01-28 00:30:00",tz="UTC")

storm23_peak = as.POSIXct("2023-02-21 06:00:00",tz="UTC")
storm23_begin = as.POSIXct("2023-02-20 15:30:00",tz="UTC")
storm23_end = as.POSIXct("2023-02-26 16:30:00",tz="UTC")

storm24_peak = as.POSIXct("2023-03-04 15:15:00",tz="UTC")
storm24_begin = as.POSIXct("2023-03-03 10:30:00",tz="UTC")
storm24_end = as.POSIXct("2023-03-07 15:45:00",tz="UTC")


allstn_storm1 <- all_stn%>%filter(DateTime>storm1_begin&DateTime<storm1_end)
allstn_storm2 <- all_stn%>%filter(DateTime>storm2_begin&DateTime<storm2_end)
allstn_storm2.1 <- all_stn%>%filter(DateTime>storm2.1_begin&DateTime<storm2.1_end)
allstn_storm3 <- all_stn%>%filter(DateTime>storm3_begin&DateTime<storm3_end)
allstn_storm4 <- all_stn%>%filter(DateTime>storm4_begin&DateTime<storm4_end)
allstn_storm5 <- all_stn%>%filter(DateTime>storm5_begin&DateTime<storm5_end)
allstn_storm6 <- all_stn%>%filter(DateTime>storm6_begin&DateTime<storm6_end)
allstn_storm7 <- all_stn%>%filter(DateTime>storm7_begin&DateTime<storm7_end)
allstn_storm8 <- all_stn%>%filter(DateTime>storm8_begin&DateTime<storm8_end)
allstn_storm9 <- all_stn%>%filter(DateTime>storm9_begin&DateTime<storm9_end)
allstn_storm10 <- all_stn%>%filter(DateTime>storm10_begin&DateTime<storm10_end)
allstn_storm11 <- all_stn%>%filter(DateTime>storm11_begin&DateTime<storm11_end)
allstn_storm12 <- all_stn%>%filter(DateTime>storm12_begin&DateTime<storm12_end)
allstn_storm13 <- all_stn%>%filter(DateTime>storm13_begin&DateTime<storm13_end)
allstn_storm14 <- all_stn%>%filter(DateTime>storm14_begin&DateTime<storm14_end)
allstn_storm15 <- all_stn%>%filter(DateTime>storm15_begin&DateTime<storm15_end)
allstn_storm16 <- all_stn%>%filter(DateTime>storm16_begin&DateTime<storm16_end)
allstn_storm17 <- all_stn%>%filter(DateTime>storm17_begin&DateTime<storm17_end)
allstn_storm18 <- all_stn%>%filter(DateTime>storm18_begin&DateTime<storm18_end)
allstn_storm19 <- all_stn%>%filter(DateTime>storm19_begin&DateTime<storm19_end)
allstn_storm20 <- all_stn%>%filter(DateTime>storm20_begin&DateTime<storm20_end)
allstn_storm21 <- all_stn%>%filter(DateTime>storm21_begin&DateTime<storm21_end)
allstn_storm22 <- all_stn%>%filter(DateTime>storm22_begin&DateTime<storm22_end)
allstn_storm23 <- all_stn%>%filter(DateTime>storm23_begin&DateTime<storm23_end)
allstn_storm24 <- all_stn%>%filter(DateTime>storm24_begin&DateTime<storm24_end)

#label storms
allstn_storm1$storm_name <- "July 2019"
allstn_storm2$storm_name <- "Aug. 2019 incomplete"
allstn_storm2.1$storm_name <- "Aug. 2019"
allstn_storm3$storm_name <- "Sept. 2019"
allstn_storm4$storm_name <- "Oct. 2019"
allstn_storm5$storm_name <- "June 2021"
allstn_storm6$storm_name <- "July 2021"
allstn_storm7$storm_name <- "Aug. 2021"
allstn_storm8$storm_name <- "Sept. 2021"
allstn_storm9$storm_name <- "Oct. 2021"
allstn_storm10$storm_name <- "Nov. 2021"
allstn_storm11$storm_name <- "Dec. 2021"
# no large storms Jan and feb
allstn_storm12$storm_name <- "March 2022"
allstn_storm13$storm_name <- "April 2022"
allstn_storm14$storm_name <- "May 2022"
allstn_storm15$storm_name <- "June 2022"
allstn_storm16$storm_name <- "July 2022"
allstn_storm17$storm_name <- "Aug. 2022"
allstn_storm18$storm_name <- "Sept. 2022"
allstn_storm19$storm_name <- "Oct. 2022"
allstn_storm20$storm_name <- "Nov. 2022"
allstn_storm21$storm_name <- "Dec. 2022"
allstn_storm22$storm_name <- "Jan. 2023"
allstn_storm23$storm_name <- "Feb. 2023"
allstn_storm24$storm_name <- "March 2023"

#now calc time elapsed since storm start
allstn_storm1$time_elapsed <- allstn_storm1$DateTime - storm1_begin
allstn_storm2$time_elapsed <- allstn_storm2$DateTime - storm2_begin
allstn_storm2.1$time_elapsed <- allstn_storm2.1$DateTime - storm2.1_begin
allstn_storm3$time_elapsed <- allstn_storm3$DateTime - storm3_begin
allstn_storm4$time_elapsed <- allstn_storm4$DateTime - storm4_begin
allstn_storm5$time_elapsed <- allstn_storm5$DateTime - storm5_begin
allstn_storm6$time_elapsed <- allstn_storm6$DateTime - storm6_begin
allstn_storm7$time_elapsed <- allstn_storm7$DateTime - storm7_begin
allstn_storm8$time_elapsed <- allstn_storm8$DateTime - storm8_begin
allstn_storm9$time_elapsed <- allstn_storm9$DateTime - storm9_begin
allstn_storm10$time_elapsed <- allstn_storm10$DateTime - storm10_begin
allstn_storm11$time_elapsed <- allstn_storm11$DateTime - storm11_begin
allstn_storm12$time_elapsed <- allstn_storm12$DateTime - storm12_begin
allstn_storm13$time_elapsed <- allstn_storm13$DateTime - storm13_begin
allstn_storm14$time_elapsed <- allstn_storm14$DateTime - storm14_begin
allstn_storm15$time_elapsed <- allstn_storm15$DateTime - storm15_begin
allstn_storm16$time_elapsed <- allstn_storm16$DateTime - storm16_begin
allstn_storm17$time_elapsed <- allstn_storm17$DateTime - storm17_begin
allstn_storm18$time_elapsed <- allstn_storm18$DateTime - storm18_begin
allstn_storm19$time_elapsed <- allstn_storm19$DateTime - storm19_begin
allstn_storm20$time_elapsed <- allstn_storm20$DateTime - storm20_begin
allstn_storm21$time_elapsed <- allstn_storm21$DateTime - storm21_begin
allstn_storm22$time_elapsed <- allstn_storm22$DateTime - storm22_begin
allstn_storm23$time_elapsed <- allstn_storm23$DateTime - storm23_begin
allstn_storm24$time_elapsed <- allstn_storm24$DateTime - storm24_begin

allstn_storm <- rbind(allstn_storm1,allstn_storm2,allstn_storm2.1,allstn_storm3,allstn_storm4,allstn_storm5,allstn_storm6,allstn_storm7,allstn_storm8,allstn_storm9,allstn_storm10,allstn_storm11,allstn_storm12,allstn_storm13,allstn_storm14,allstn_storm15,allstn_storm16,allstn_storm17,allstn_storm18,allstn_storm19,allstn_storm20,allstn_storm21,allstn_storm22,allstn_storm23,allstn_storm24)
allstn_storm$month <- format(as.Date(allstn_storm$Date), "%m")
allstn_storm$year_month <- format(as.Date(allstn_storm$DateTime), "%Y-%m")


ggplot(allstn_storm11,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point()
ggplot(allstn_storm12,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point()

ggplot(allstn_storm,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point() + 
  scale_x_continuous(transform = "log") + scale_y_continuous(transform = "log")

```

## storm plots

```{r storm sterf, echo=FALSE}

storm_subset <- allstn_storm %>%filter(storm_name!="Aug. 2019 incomplete"& storm_name!="Aug. 2022"& storm_name!="Aug. 2022"& storm_name!="Dec. 2022"& storm_name!="Feb. 2023"& storm_name!="Jan. 2023"& storm_name!="June 2022"& storm_name!="July 2022"& storm_name!="Jan. 2022"& storm_name!="March 2022" & storm_name!="March 2023"& storm_name!="Oct. 2019"& storm_name!="Sept. 2019"& storm_name!="Sept. 2022")
storm_subset$pCO2_ppm <- NA
#use CO2_ppm_02 for June 2021 storm
storm_subset$pCO2_ppm <- ifelse(storm_subset$storm_name == "June 2021", storm_subset$CO2_ppm_02, storm_subset$CO2_ppm_01)

storm_subset <- storm_subset%>%rename(Q = Q_m3s_02)

storm_subset$storm_name_1= factor(storm_subset$storm_name, levels=c("July 2019","Aug. 2019","June 2021","July 2021","Aug. 2021","Sept. 2021","Oct. 2021","Nov. 2021","Dec. 2021","April 2022","May 2022","Oct. 2022","Nov. 2022")) 

storm_subset$time_elapsed_day <- as.numeric(storm_subset$time_elapsed)/60/24

#facet wrap
p1 <- ggplot(storm_subset, aes(x=Q*1000,y=pCO2_ppm,color=as.numeric(time_elapsed)/60/24))+ 
  facet_wrap( ~ storm_name_1#, scales = "free"
              )  + geom_point() + 
  scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
    scale_color_viridis_c() +
  theme_bw(base_size = 18)

p2 <- ggplot(storm_subset%>%filter(storm_name!="July 2019"&storm_name!="Aug. 2019"&storm_name!="Nov. 2022"&storm_name!="Oct. 2022"), aes(x=Q*1000,y=pCO2_ppm,color=time_elapsed_day))+ 
  facet_wrap( ~ storm_name_1#, scales = "free"
              )  + geom_point() + 
  scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
    scale_color_viridis(option = "H",name= "days since\nstart of storm",guide=guide_colourbar(reverse = TRUE)) +
  ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18)

#now for all storms
allstn_storm$month_number <- format(as.Date(allstn_storm$Date), "%m")
allstn_storm$month_number  <- as.numeric(allstn_storm$month_number )
allstn_storm$month <- format(as.Date(allstn_storm$Date), "%B")

allstn_storm$month <- reorder(allstn_storm$month, allstn_storm$month_number)

p3 <- ggplot(allstn_storm,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) + geom_point() +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 


```

# Base flow

```{r base flow stn01, echo=FALSE}

all_stn$month_number <- format(as.Date(all_stn$Date), "%m")
all_stn$month_number  <- as.numeric(all_stn$month_number )
all_stn$month <- format(as.Date(all_stn$Date), "%B")

all_stn$month <- reorder(all_stn$month, all_stn$month_number)

p1<-ggplot(all_stn,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) + geom_point() +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

p2<-ggplot() + geom_point(data=all_stn,aes(x=Q_m3s_02*1000,y=CO2_ppm_01),color="black") +
  geom_point(data=allstn_storm,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 


```

# Station 2

```{r  stn02, echo=FALSE}
all_stn$dif <- all_stn$CO2_ppm_01 - all_stn$CO2_ppm_02

test1 <- all_stn%>%filter(dif>0) 
test2 <- all_stn%>%filter(dif<0) 

p1 <- ggplot(all_stn%>%filter(dif>40)%>%
               filter(DateTime>"2020-01-01") , aes(x=Q_m3s_02,y=dif)) + geom_point() +  #scale_y_continuous(transform="log10", 
  theme_bw(base_size = 18)

p2 <- ggplot(all_stn %>%filter(dif< -40)%>%
               filter(DateTime>"2020-01-01"),
            aes(x=Q_m3s_02,y=abs(dif),color=CO2_ppm_02)) + geom_point() + scale_y_reverse()+ 
 # scale_x_log10() + 
  theme_bw(base_size = 18)

p3 <- ggplot(all_stn# %>%filter(dif < -40 |dif > 40 )
             %>%
               filter(DateTime>"2020-01-01"),
            aes(x=Q_m3s_02,y=dif,color=CO2_ppm_02)) + geom_point() + #scale_y_reverse()+ 
 # scale_x_log10() + 
  theme_bw(base_size = 18)

p_full <- plot_grid(p1,p2,ncol=1, align = "hv")

```
#station 3
```{r  stn03, echo=FALSE}

#plot_ly(data=all_stn%>%filter(DateTime > as.POSIXct("2021-06-05 00:00:00")), x=~DateTime,y= ~CO2_ppm_03)

all_stn_remove_3 <- all_stn%>%filter(DateTime>as.POSIXct("2021-06-24 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-06-25 12:15:00",tz="UTC") | DateTime>as.POSIXct("2021-07-07 06:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-08-13 22:45:00",tz="UTC") | DateTime>as.POSIXct("2021-08-18 00:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-10-03 11:00:00",tz="UTC") | DateTime>as.POSIXct("2021-12-18 13:45:00",tz="UTC"))

all_stn_remove_3 <- all_stn_remove_3%>%filter(DateTime>as.POSIXct("2021-09-02 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-09-26 00:00:00",tz="UTC") | DateTime>as.POSIXct("2021-12-31 00:00:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-12-27 00:00:00",tz="UTC") | DateTime>as.POSIXct("2022-02-09 00:00:00",tz="UTC"))

#plot_ly(data=all_stn_remove, x=~DateTime,y= ~CO2_ppm_03)

stn3_p <- ggplot() + 
  geom_point(data=all_stn_remove_3,aes(x=CO2_ppm_01,y=CO2_ppm_03,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 

p4 <- ggplot() + 
  geom_point(data=all_stn,aes(x=Q_m3s_04,y=CO2_ppm_03,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 


```


# Station 4

```{r  stn04, echo=FALSE}

#plot_ly(data=all_stn%>%filter(DateTime > as.POSIXct("2021-06-05 00:00:00")), x=~DateTime,y= ~CO2_ppm_04)

all_stn_remove_4 <- all_stn%>%filter(DateTime!=as.POSIXct("2021-07-05 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-10-20 12:30:00",tz="UTC") | DateTime>as.POSIXct("2021-12-30 16:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2022-03-17 12:30:00",tz="UTC") | DateTime>as.POSIXct("2022-06-16 00:00:00",tz="UTC"))

p1 <-ggplot() + geom_point(data=allstn_storm,aes(x=Q_m3s_04*1000,y=CO2_ppm_04,color=month)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

p2 <-ggplot() + geom_point(data=all_stn,aes(x=Q_m3s_04*1000,y=CO2_ppm_04)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ 
  scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
  ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 


p3 <- ggplot() + 
  geom_point(data=all_stn,aes(x=CO2_ppm_01,y=CO2_ppm_04,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 


#now for all storms
all_stn_remove$month_number <- format(as.Date(all_stn_remove$Date), "%m")
all_stn_remove$month_number  <- as.numeric(all_stn_remove$month_number )
all_stn_remove$month <- format(as.Date(all_stn_remove$Date), "%B")

all_stn_remove$month <- reorder(all_stn_remove$month, all_stn_remove$month_number)

all_stn_remove_4 <- all_stn_remove_4%>%rename(Month=month)
p4_stn4 <- ggplot() + 
  geom_point(data=all_stn_remove_4%>%filter(DateTime>"2021-06-06 00:00:00"), aes(x=CO2_ppm_01,y=CO2_ppm_04,color=Month)) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression('Station 4')) +    xlab(expression(italic(p)*CO[2] ~~'at outlet (ppm)')) +  theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1) 

all_stn_remove_3 <- all_stn_remove_3%>%rename(Month=month)
p3_stn3 <- ggplot() + 
  geom_point(data=all_stn_remove_3%>%filter(DateTime>"2021-06-06 00:00:00"),aes(x=CO2_ppm_01,y=CO2_ppm_03,color=Month)) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,5000,10000,15000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression('Station 3')) +   
  xlab(expression(italic(p)*CO[2] ~~'at outlet (ppm)')) +  theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1) 

all_stn <- all_stn%>%rename(Month=month)
p2_stn2 <- ggplot() + 
  geom_point(data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
             ,aes(x=CO2_ppm_01,y=CO2_ppm_02,color=Month)) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,15000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression('Station 2')) +   
  xlab(expression(italic(p)*CO[2] ~~'at outlet (ppm)')) +  theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1)


lm_2 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_02), data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
           )
summary(lm_2)

lm_2 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_02), data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
           )
summary(lm_2)

lm_1 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_04), data=all_stn_remove)
summary(lm_1)

#this one for paper
ggarrange(p2_stn2+ rremove("xlab"),p3_stn3+ rremove("xlab"),p4_stn4, ncol=1, nrow=3, common.legend = TRUE, legend="right",labels="auto",heights = c(1,1,1.3))
```

#summarize days of deployment
```{r  summarize, echo=FALSE}
#summarize days
all_stn_remove_4$Date <-as.Date(all_stn_remove_4$DateTime)
stn4_remove_sum <- all_stn_remove_4%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_04,na.rm=TRUE))
stn4_remove_sum <- all_stn_remove_4%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_04,na.rm=TRUE))
stn4_remove_sum <- stn4_remove_sum%>%filter(mean_Q!="NaN")

all_stn_remove_3$Date <-as.Date(all_stn_remove_3$DateTime)
stn3_remove_sum <- all_stn_remove_3%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_03,na.rm=TRUE))
stn3_remove_sum <- stn3_remove_sum%>%filter(mean_co2!="NaN")
stn3_remove_sum <- all_stn_remove_3%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_03,na.rm=TRUE))
stn3_remove_sum <- stn3_remove_sum%>%filter(mean_Q!="NaN")

all_stn$Date <-as.Date(all_stn$DateTime)
all_stn_sum_01 <- all_stn%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_01,na.rm=TRUE))
all_stn_sum_01 <- all_stn_sum_01%>%filter(mean_co2!="NaN")
stn1_remove_sum <- all_stn%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_01,na.rm=TRUE))
stn1_remove_sum <- stn1_remove_sum%>%filter(mean_Q!="NaN")

all_stn_sum_02 <- all_stn%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_02,na.rm=TRUE))
all_stn_sum_02 <- all_stn_sum_02%>%filter(mean_co2!="NaN")
all_stn_sum_02 <- all_stn%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_02,na.rm=TRUE))
all_stn_sum_02 <- all_stn_sum_02%>%filter(mean_Q!="NaN")



DO_05 <- read.csv(here::here("data_cleaned/DO_05_cleaned.csv"))
DO_05$DateTime <- as.POSIXct(DO_05$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
DO_05$date <- as.Date(DO_05$DateTime)
DO_05_sum <- DO_05%>%group_by(date)%>%summarise(
  DO_mean = mean(DO_mgL,rm.na=TRUE))%>%filter(DO_mean!="NaN")

```

## DOC

```{r  DOC read in data, echo=FALSE}
DOC_2022 <- read.csv(here::here("DOC/DOC_KW_08-25-2022.csv"))%>%select(Date,time,site,DOC..mg.L.,TDN..mg.L.)%>%rename(Time=time,DOC=DOC..mg.L.,TDN=TDN..mg.L.,Station=site)%>%filter(Station=="Stn02"|Station=="Stn05")
DOC_2022$SampleType <- "Station"
DOC_2021 <- read.csv(here::here("DOC/DOC_9-1-2021_UNC_EDIT3.csv"))%>%select(Date,Time,Station,SampleType,DOC,TDN)
DOC_synop <-  read.csv(here::here("DOC/WaterChem_synoptic_2022-01-28.csv")) 
DOC_2019 <- read.csv(here::here("DOC/WaterChem_2019_EDIT.csv"))%>%select(Date,Time,Station,DOC..mg.L.,TDN..mg.L.)%>%rename(
  DOC=DOC..mg.L.,TDN=TDN..mg.L.)%>%drop_na(DOC)
DOC_2019$SampleType <- "Station"

DOC_df <- rbind(DOC_2022,DOC_2021,DOC_2019)

DOC_df$DateTime <- as.POSIXct(paste(DOC_df$Date, DOC_df$Time), format="%m/%d/%y %H:%M", tz = "UTC")
DOC_df$DateTime <- round_date(DOC_df$DateTime,unit="15 minutes")

#formating 2021 DOC data
DOC_2021$Distance_from_peatland <- 
  ifelse(DOC_2021$Station=="Stn01",5,
         ifelse(DOC_2021$Station=="Stn02",56,
                ifelse(DOC_2021$Station=="Stn03",288,
                       ifelse(DOC_2021$Station=="Stn04",454,
                              ifelse(DOC_2021$Station=="Stn05",0+1,52+1)))))
DOC_2021$WS <- ifelse(DOC_2021$Station=="Stn05"|DOC_2021$Station=="Stn06","Colmillo","Gavilan")



#c6 data
C6_df <-read.csv(here::here("DOC/C6_df.csv"))
C6_df$DateTime <- as.POSIXct(C6_df$DateTime, format="%Y-%m-%d %H:%M:%S", tz = "UTC")
C6_df$DateTime <- round_date(C6_df$DateTime, unit="15 minute")
C6_df <- C6_df%>%drop_na(DateTime)
C6_df <- unique(C6_df)


#### station 2
WL_df <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")

##merge with doc
mergeDOC_df <- left_join(DOC_df,WL_df%>%select(!Station), by=(c("DateTime")))

#DOC data from stn02 just seems a bit better than stn01
mergeDOC_df_subset1 <- mergeDOC_df%>%filter(DateTime < "2021-01-01")%>%filter(Station=="Stn01")
mergeDOC_df_subset2 <- mergeDOC_df%>%filter(DateTime > "2021-01-01")%>%filter(Station=="Stn02")

DOC_PeatlandOutlet <- rbind(mergeDOC_df_subset1,mergeDOC_df_subset2)

#merge C with station01 Q
C6_Q_df <- left_join(C6_df,WL_df%>%select(!Station),by="DateTime")
C6_Q_df <- C6_Q_df%>%filter(DateTime != as.POSIXct("2019-07-15 14:45",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 15:15",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 15:45",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 21:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 22:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 22:15",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 23:00",tz="UTC"))
C6_Q_df <- C6_Q_df[order(as.Date(C6_Q_df$DateTime, format="%Y-%m-%d %H:%M:%S")),]
#merge c6 (I think I will do this manually because otherwise it is too complicated)
C6_Q_df$DOC <- NA
C6_Q_df$TDN <- NA

#this sample was collected 2019-07-11 14:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-11 15:30:00",tz="UTC"), "DOC"] <- 3.7630
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-11 15:30:00",tz="UTC"), "TDN"] <- 0.11140

#This sample was collected at 2019-07-16 14:30:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-16 08:45:00",tz="UTC"), "DOC"] <- 4.6100
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-16 08:45:00",tz="UTC"), "TDN"] <- 0.16920

#This sample was collected at 2019-07-19 13:15:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-19 13:00:00",tz="UTC"), "DOC"] <- 3.7400
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-19 13:00:00",tz="UTC"), "TDN"] <- 0.10280


start <- as.POSIXct("2019-07-14 00:15",tz="UTC")
end <- as.POSIXct("2019-07-16 09:00",tz="UTC")
C6_Q_df_storm <- C6_Q_df%>%filter(DateTime>start&DateTime<end)
C6_Q_df_storm$time_elapsed <- C6_Q_df_storm$DateTime - start


#merge with co3 data
C6_Q_df <- left_join(C6_Q_df,all_stn,by="DateTime")
```

#plot DOC

```{r  plot DOC, echo=FALSE}

p1 <- ggplot(DOC_PeatlandOutlet)+
  geom_point(aes(x=Q_m3s*1000, y=DOC, fill=DateTime), shape=21,size=3) + 
  ylab(expression(paste('DOC (mg ' , l^-1,")"))) +
  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  scale_x_continuous(transform = "log",breaks=c(10,30,100,300,1000)) + scale_y_continuous(transform = "log",breaks=c(3,4,5)) +
   theme_bw(base_size = 14) +
  labs(fill="Date time")

p1.TDN <- ggplot(DOC_PeatlandOutlet)+
  geom_point(aes(x=Q_m3s*1000, y=TDN, fill=DateTime), shape=21,size=3) + 
  ylab(expression(paste('TDN (mg ' , l^-1,")"))) +
  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  scale_x_continuous(transform = "log",breaks=c(10,30,100,300,1000)) + scale_y_continuous(transform = "log",breaks=c(.08,.14,.23)) +
   theme_bw(base_size = 14) +
  labs(fill="Date time")

#spatial variance upstream to down
DOC_2021_plot <- DOC_2021%>%drop_na(WS)
DOC_2021_plot$Date_plot <- as.character(format(DOC_2021_plot$Date_format,format="%d %B"))
DOC_2021_plot$Date_plot <- reorder(DOC_2021_plot$Date_plot, DOC_2021_plot$Date_format)

#with colmillo data
p2.1 <- ggplot(DOC_2021_plot %>%filter(SampleType=="Station"))+
  geom_point(aes(x=Distance_from_peatland, y=DOC, fill=Date_plot), shape=21,size=3) + 
  facet_grid(.~fct_rev(WS), scales = "free_x", space='free') +
  ylab(expression(paste('DOC (mg ' , l^-1,")"))) +
   theme_bw(base_size = 18)

#without colmillo data
p2.2 <- ggplot(DOC_2021_plot %>%filter(SampleType=="Station")%>%filter(WS=="Gavilan"))+
  geom_point(aes(x=Distance_from_peatland, y=DOC, fill=Date_plot), shape=21,size=3) + 
    xlab("Distance from peatland outlet") +
  ylab(expression(paste('DOC (mg ' , l^-1,")"))) +
  labs(fill="Date") +
   theme_bw(base_size = 18)

##TDN
p2.2 <- ggplot(DOC_2021_plot %>%filter(SampleType=="Station")%>%filter(WS=="Gavilan"))+
  geom_point(aes(x=Distance_from_peatland, y=TDN, fill=Date_plot), shape=21,size=3) + 
    xlab("Distance from peatland outlet") +
  ylab(expression(paste('TDN (mg ' , l^-1,")"))) +
  labs(fill="Date") +
   theme_bw(base_size = 18)

#stn01 vs stno4 data
DOC_2021_melt <- DOC_2021
DOC_2021_melt$Station <- ifelse(DOC_2021_melt$SampleType=="synoptic"&DOC_2021_melt$Station=="Stn01","Stn02",DOC_2021_melt$Station)
DOC_2021_melt <- DOC_2021_melt%>%filter(Station=="Stn02"|Station=="Stn04")%>%select(Date_format,Station,DOC)%>%spread(Station, DOC)
DOC_2021_melt$Date_plot <- as.character(format(DOC_2021_melt$Date_format,format="%d %B"))
DOC_2021_melt$Date_plot <- reorder(DOC_2021_melt$Date_plot, DOC_2021_melt$Date_format)

p.2 <- ggplot(DOC_2021_melt)+
  geom_point(aes(x=Stn02, y=Stn04, fill=Date_plot), shape=21,size=4)+
  geom_abline(intercept = 0, slope = 1) +
  annotate(geom = "text", x = 3.9, y = 4.2, label = "1:1",size=10, color = "black",
             angle = 45) +
  xlab(expression(paste('Upstream DOC (mg ' , l^-1,")"))) +
    ylab(expression(paste('Downstream (mg ' , l^-1,")"))) +
  labs(fill="Date") +
   theme_bw(base_size = 18)

#hysteresis
C6_p3 <- ggplot(C6_Q_df_storm) + 
  geom_point(aes(x=Q_m3s*1000,y=CDOM_ppb,color=time_elapsed/60/24),size=4)+
    scale_color_viridis_c(name= "days since\nstart of storm",guide=guide_colourbar(reverse = TRUE)) +
  scale_y_log10() + scale_x_log10() +
 ylab('CDOM (ppb)') + 
  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 14)

#DOC v CDOM
p2 <- ggplot(C6_Q_df%>%drop_na(DOC))+
  geom_point(aes(x=CDOM_ppb,y=DOC),size=3) +
    xlab(expression(paste('DOC (mg ' , l^-1,")"))) +
 ylab('CDOM (ppb)') + 
    scale_y_continuous(transform = "log") +
  scale_x_continuous(transform = "log") +
  theme_bw()+theme(text=element_text(size=14))

#CDOM v CO2
p3 <- ggplot(C6_Q_df)+
  geom_point(aes(x=CO2_ppm_01, y=CDOM_ppb, fill=DateTime), shape=21,size=3) +
 ylab('CDOM (ppb)') +  
 xlab(expression(italic(p)~CO[2] ~'upstream (ppm)')) + 
   theme_bw(base_size = 18)

p_doc_combine <- ggarrange(p1, p1.TDN, ncol=2, nrow=1, common.legend = TRUE, legend="right",labels=c("b","c"))

p_hyst <- ggarrange(NULL, C6_p3,NULL, ncol=3, nrow=1, labels=c("","a",""),widths = c(.2,1,.2))
 
p_full <- plot_grid(p_hyst,p_doc_combine, ncol=1)
```

# methane

```{r  plot CH4, echo=FALSE}
CH4_df <- read.csv(here::here("WaterChem/methane_df_merged.csv"))
CH4_df$DateTime <- as.POSIXct(CH4_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

CH4_df_summary <- CH4_df%>%group_by(Site,Site2,DateTime)%>%
  summarise(
    Watertemp_c = mean(Watertemp_c),
    DO_mgL = mean(DO_mgL,na.rm=TRUE),
    Q_m3s = mean(Q_m3s),
    pCH4_ppm = mean(pCH4_ppm),
    CH4_umol.L = mean(CH4_umol.L)
  )

#DO a good predictor
site_names <- list(
  'Gavilan Outlet'="Wetland outlet",
  'Gavilan Center'="Wetland center")

site_labeller <- function(variable,value){
  return(site_names[value])
}

p1 <- ggplot(CH4_df_summary%>%filter(Site!="Gavilan Edges")%>%filter(Site2!="50m")%>%filter(Site2!="100m")%>%filter(DateTime<"2022-09-01")) +
  geom_smooth(method='lm',aes(x=DO_mgL,y=pCH4_ppm,color=Site),color="grey50",linewidth=.5 ,se = FALSE) +
      facet_wrap(.~Site, labeller=site_labeller,ncol=1,scales="free_y") +
    geom_point(aes(x=DO_mgL,y=pCH4_ppm,fill=as.factor(as.Date(DateTime,format="%m-%d"))),size=3,shape=21) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("DO at outlet (mg/l)")  + labs(fill="Date collected") +
    scale_fill_manual(labels = c("June-06","July-01","July-06","July-22","July-27"),values=c("#e41a1c","#377eb8","#4daf4a","#984ea3","#ff7f00")) +
  scale_y_log10() + scale_x_log10() +
  theme_bw(base_size = 18) 

##longitudinal
p2 <- ggplot(CH4_df_summary%>%filter(Site=="Gavilan Outlet")#%>%filter(DateTime<"2022-09-01")
            ) +
    geom_point(aes(x=as.numeric(gsub('m','',Site2)),y=pCH4_ppm,
                #   fill=as.factor(signif(Q_m3s,2))
                   fill=as.factor(as.Date(DateTime,format="%m-%d"))
                   ),
               size=3,shape=21) + scale_y_continuous(transform = "log",breaks=c(2000,1000,500,200)) +
  scale_fill_manual(labels = c("June-06","July-01","July-06"),values=c("#e41a1c","#377eb8","#4daf4a")) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("Distance from outlet (m)")  + labs(fill="Date collected") +
  theme_bw(base_size = 18)


#get legend
# Extract the legend. Returns a gtable
leg <- get_legend(p1)

# Convert to a ggplot and print
p_leg <- as_ggplot(leg)


##all

p_full_1 <- plot_grid(p_leg,p2+rremove("legend"),ncol=1,labels=c("","b."),label_fontface = "bold",label_size = 18) 
p_full_2 <- plot_grid(p1+rremove("legend"),p_full_1,ncol=2,labels=c("a.",""),label_fontface = "bold",label_size = 18)


#discharge not as good a relationship

p3 <- ggplot(CH4_df_summary%>%filter(Site!="Gavilan Edges")%>%filter(Site2!="50m")%>%filter(Site2!="100m"),
       aes(x=Q_m3s,y=pCH4_ppm,fill=as.factor(as.Date(DateTime)))) + geom_point(size=3,shape=21) +
  facet_wrap(Site~., labeller=site_labeller) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("Q (m3/s)")  + labs(fill="Date Collected") +
  scale_y_log10() + scale_x_log10() +
  theme_bw(base_size = 18)


#stats
model <- lm(log(pCH4_ppm) ~ log(Q_m3s), data = CH4_df_summary %>%filter(Site=="Gavilan Outlet")%>%filter(Site2!="50m")%>%filter(Site2!="100m"))
summary(model)

model <- lm(log(pCH4_ppm) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Outlet")%>%filter(Site2!="50m")%>%filter(Site2!="100m"))
summary(model)

#wetland denter
model <- lm(log(pCH4_ppm) ~ log(Q_m3s), data = CH4_df_summary %>%filter(Site=="Gavilan Center"))
summary(model)

model <- lm(log(pCH4_ppm) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Center"))
summary(model)

```

#plot DO

```{r  O2, echo=FALSE}

stn01_df <- read.csv(here::here("metabolizer_dataframe/stn01_df_march9.csv"))
stn01$solar.time <- as.POSIXct(stn01$solar.time,format="%Y-%m-%d %H:%M:%S",tz="UTC")

ggplot(stn01$DateTime,aes(x=))

#how many days are DO = 0?
#stn 1 144
#stn 5 
do_stn1 <- read.csv(here::here("data_cleaned/DO_01_cleaned.csv"))
do_stn1$DateTime <- as.POSIXct(do_stn1$DateTime,format="%m/%d/%Y %H:%M",tz="UTC")
do_stn1$Date <- as.Date(do_stn1$DateTime)
do_stn1 <- do_stn1%>%filter(DO_mgL<=0)%>%group_by(Date)%>%summarise(mean_do = mean(DO_mgL,na.rm=TRUE))
ggplot(do_stn1,aes(x=DateTime,y=DO_mgL)) + geom_point()
```

# waterfall

```{r  waterfall, echo=FALSE}
inj_df <- read.csv(here::here("MergedFiles/all_2019_Data.csv"))%>%filter(Inj.x=="Yes")
inj_df$DateTime <- as.POSIXct(inj_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

inj_df_2021 <- read.csv(here::here("MergedFiles/Inj_df_2019July14.csv"))%>%select(DateTime,pCO2_80m_adj,pCO2_120m_adj)
inj_df_2021$DateTime <- as.POSIXct(inj_df_2021$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
inj_df_2021 <- inj_df_2021%>%melt(id.vars = "DateTime")

#discharge
WL_df <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
WL_df <- WL_df%>%filter(DateTime<"2019-08-31")%>%select(DateTime,Q_m3s)

inj_df <- left_join(inj_df,WL_df,by="DateTime")
inj_df_summary <- inj_df%>%group_by(as.Date(DateTime))%>%
  summarise(Q_mean = mean(Q_m3s,na.rm=TRUE))

#injection 1
inj_df_1 <- inj_df%>%filter(DateTime < "2019-07-22")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_1$inj_number <- "inj_1"

inj_df_2 <- inj_df%>%
  filter(DateTime > "2019-07-22"&
            DateTime < "2019-07-24")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_2$inj_number <- "inj_2"

inj_df_3 <- inj_df%>%
  filter(DateTime > "2019-07-24"&DateTime < "2019-07-29")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_3$inj_number <- "inj_3"

inj_df_4 <- inj_df%>%filter(DateTime > "2019-07-29"&
                              DateTime < "2019-08-05")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_4$inj_number <- "inj_4"

inj_df_5 <- inj_df%>%
  filter(DateTime > "2019-08-05"& DateTime < "2019-08-08")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% 
  melt(id.vars = "DateTime")
inj_df_5$inj_number <- "inj_5"

inj_df_6 <- inj_df%>%
  filter(DateTime > "2019-08-08")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>%
  melt(id.vars = "DateTime")
inj_df_6$inj_number <- "inj_6"

inj_all <- rbind(inj_df_1,inj_df_2,inj_df_3,inj_df_4,inj_df_5,inj_df_6)


p_2 <- ggplot(inj_df_2,aes(x=DateTime,y=value,color=variable)) + geom_point()

p_3 <- ggplot(inj_df_3,aes(x=DateTime,y=value,color=variable)) + geom_point()


p_5 <- ggplot(inj_df_5,aes(x=DateTime,y=value,color=variable)) + geom_point()

p_6 <- ggplot(inj_df_6,aes(x=DateTime,y=value,color=variable)) + geom_point()



p_45 <- ggplot(inj_df_2021%>%filter(variable!="pCO2_45m")%>%filter(DateTime < as.POSIXct("2021-07-14 12:00:00",tz="UTC")),aes(x=DateTime,y=value,color=variable)) + geom_point() + 
  x_lab()


```

# metabolism

```{r  metabolism, echo=FALSE}

#station 1
stn01 <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
stn01$DateTime <- as.POSIXct(stn01$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn01$date <- as.Date(stn01$DateTime,format="%Y-%m-%d")
stn01_summary<- stn01 %>%group_by(date)%>%summarise(discharge_stn01 = mean(Q_Ls))

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn1_metab$GPP_mean <- ifelse(df_stn1_metab$GPP_mean < 0,0,df_stn1_metab$GPP_mean )
df_stn1_metab$date <- as.Date(df_stn1_metab$date)

stn01_summary <- left_join(df_stn1_metab,stn01_summary,by="date")

p_test <- ggplot(stn01_summary,aes(x=discharge_stn01,y=ER_mean)) + geom_point()

m.stn1 <- lm(ER_mean~discharge_stn01,data=stn01_summary)
summary(m.stn1)

#staton 2
df_stn2_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station2_fieldlight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn2_metab$GPP_mean <- ifelse(df_stn2_metab$GPP_mean < 0,0,df_stn2_metab$GPP_mean )
df_stn2_metab$date <- as.Date(df_stn2_metab$date)


#station 5
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn05$date <- as.Date(stn05$DateTime,format="%Y-%m-%d")
stn05_summary<- stn05 %>%group_by(date)%>%
  summarise(discharge_stn05 = mean(Q_m3s))

df_stn5_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station5_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%
  filter(ER_Rhat < 1.05)%>%
  filter(GPP_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn5_metab$GPP_mean <- ifelse(df_stn5_metab$GPP_mean < 0,0,df_stn5_metab$GPP_mean )
df_stn5_metab$date <- as.Date(df_stn5_metab$date)

df_stn5_metab <- left_join(df_stn5_metab,stn05_summary,by="date")

m.stn5 <- lm(ER_mean~discharge_stn05,data=df_stn5_metab)
summary(m.stn5)
#evaluate Q v ER correlation
p_test <- ggplot(df_stn5_metab,aes(x=discharge_stn05,y=ER_mean)) + geom_point()

p_test <-ggplot(df_stn5_metab,aes(x=date,y=discharge_stn05)) + geom_point()

#remove high flows
df_stn5_metab <- df_stn5_metab%>%filter(discharge_stn05 < .1)



m2.stn5 <- lm(ER_mean~discharge_stn05,data=df_stn5_metab)
summary(m2.stn5)
#merge dataframes
df_metabe <- full_join(df_stn5_metab,df_stn1_metab,by="date")
#plot

dates <- data.frame(
  seq(as.Date('2019-07-13'), as.Date('2022-04-03'), by = 'days'))
colnames(dates) <- "date"

df_stn1_metab <- full_join(df_stn1_metab,dates,by="date")

df_stn1_metab$GPP_mean_CO2 <- (df_stn1_metab$GPP_mean*44/32)
df_stn1_metab$GPP_97.5pct_CO2 <- (df_stn1_metab$GPP_97.5pct*44/32)
df_stn1_metab$ER_mean_CO2 <- (df_stn1_metab$ER_mean*44/32)
df_stn1_metab$ER_97.5pct_CO2 <- (df_stn1_metab$ER_97.5pct*44/32)

p_1.1 <-ggplot(df_stn1_metab%>%
               filter(date > as.Date("2021-07-01")&date < as.Date("2021-10-01")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
  ylab(expression(paste('Metabolim (g C' ,~m^-2~y^-1,")"))) + xlab("Station 1: 2022") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2021-07-05"),as.Date("2021-07-05")), y = c(8,9), label = c("ER", "GPP"),size = 3)


p_1.2 <-ggplot(df_stn1_metab%>%
               filter(date < as.Date("2020-01-10")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
  ylab(expression(paste('Metabolim (g C' ,~m^-2~y^-1,")"))) + xlab("Station 1: 2019 - 2020") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2019-07-20"), xend = as.Date("2019-07-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2019-07-20"), xmax = as.Date("2019-07-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2019-07-20"), xend = as.Date("2019-07-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2019-07-20"), xmax = as.Date("2019-07-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2019-08-07"),as.Date("2019-08-07")), y = c(8,9), label = c("ER", "GPP"),size = 3)



df_stn5_metab <- full_join(df_stn5_metab,dates,by="date")

df_stn5_metab$GPP_mean_CO2 <- (df_stn5_metab$GPP_mean*44/32)
df_stn5_metab$GPP_97.5pct_CO2 <- (df_stn5_metab$GPP_97.5pct*44/32)
df_stn5_metab$ER_mean_CO2 <- (df_stn5_metab$ER_mean*44/32)
df_stn5_metab$ER_97.5pct_CO2 <- (df_stn1_metab$ER_97.5pct*44/32)


p_2 <- ggplot(df_stn5_metab%>%
            filter(date > as.Date("2021-06-15")& date < as.Date("2021-10-20")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
    ylab(expression(paste('Metabolim (g C' ~m^-2~y^-1,")"))) + xlab("Station 5: 2022") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2021-07-05"),as.Date("2021-07-05")), y = c(8,9), label = c("ER", "GPP"),size = 3)


full_p <- plot_grid(p_1.2,p_1.1,NULL,p_2,labels =c("a","b","","c"),nrow=2,ncol=2)

```
#stn 1 and 5 comparison
```{r  compare, echo=FALSE}

#station 1
stn01 <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
stn01$DateTime <- as.POSIXct(stn01$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn01$Date <- as.Date(stn01$DateTime,format="%Y-%m-%d")
stn01_summary<- stn01 %>%group_by(Date)%>%
  summarise(discharge_stn01 = mean(Q_m3s),
            Watertemp_c = mean(WLTemp_c))

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn1_metab$GPP_mean <- ifelse(df_stn1_metab$GPP_mean < 0,0,df_stn1_metab$GPP_mean )
df_stn1_metab$Date <- as.Date(df_stn1_metab$date)
df_stn1_metab <- left_join(df_stn1_metab,stn01_summary,by="Date")
df_stn1_metab <- df_stn1_metab%>%select(Date,GPP_mean,ER_mean,Watertemp_c)
df_stn1_metab$Station <- "Stn01"
df_stn1_metab$GPP_mean_CO2 <- (df_stn1_metab$GPP_mean*44/32)
df_stn1_metab$ER_mean_CO2 <- (df_stn1_metab$ER_mean*44/32)
df_stn1_metab <- df_stn1_metab%>%select(Station,Date,GPP_mean_CO2,ER_mean_CO2,Watertemp_c)

#stn 5
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn05$Date <- as.Date(stn05$DateTime,format="%Y-%m-%d")
stn05_summary<- stn05 %>%group_by(Date)%>%
  summarise(discharge_stn05 = mean(Q_m3s),
            Watertemp_c = mean(WLTemp_c))

df_stn5_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station5_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn5_metab$GPP_mean <- ifelse(df_stn5_metab$GPP_mean < 0,0,df_stn5_metab$GPP_mean )
df_stn5_metab$Date <- as.Date(df_stn5_metab$date)
df_stn5_metab <- left_join(df_stn5_metab,stn05_summary,by="Date")
#remove high flows
df_stn5_metab <- df_stn5_metab%>%filter(discharge_stn05 < .1)
df_stn5_metab$Station <- "Stn05"
df_stn5_metab$GPP_mean_CO2 <- (df_stn5_metab$GPP_mean*44/32)
df_stn5_metab$ER_mean_CO2 <- (df_stn5_metab$ER_mean*44/32)
df_stn5_metab <- df_stn5_metab%>%select(Station,Date,GPP_mean_CO2,ER_mean_CO2,Watertemp_c)

df_metab <- rbind(df_stn1_metab,df_stn5_metab)

DOC_2021 <- read.csv(here::here("DOC/DOC_9-1-2021_UNC_EDIT3.csv"))%>%select(Date,Station,DOC,TDN)%>%filter(Station=="Stn01"|Station=="Stn05")
DOC_2021$Date <- as.Date(DOC_2021$Date,format="%m/%d/%y")

df_full <- full_join(df_metab,DOC_2021,by=c("Date","Station"))




df_full_pivot <- df_full%>%select(!Date)%>%
  pivot_longer(!Station, names_to = "variable", values_to = "value")%>%drop_na(value)



p1 <- ggplot(df_full ,aes(x=Station,y=DOC,fill=Station)) +geom_boxplot()+   ylab(expression(paste('DOC'))) + xlab("") +
  scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(DOC ~ Station, data = df_full)
#summary(model)

p2 <- ggplot(df_full ,aes(x=Station,y=TDN,fill=Station)) +geom_boxplot()+   ylab(expression(paste('TDN'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 14)

model <- aov(TDN ~ Station, data = df_full)
#summary(model)

p3 <- ggplot(df_full ,aes(x=Station,y=GPP_mean_CO2,fill=Station)) +geom_boxplot()+  ylab(expression(paste('GPP'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(GPP_mean_CO2 ~ Station, data = df_full)
#summary(model)

p4 <- ggplot(df_full ,aes(x=Station,y=ER_mean_CO2,fill=Station)) +geom_boxplot() +
  ylab(expression(paste('ER'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(ER_mean_CO2 ~ Station, data = df_full)
#summary(model)

p5 <- ggplot(df_full ,aes(x=Station,y=Watertemp_c,fill=Station)) +geom_boxplot() +
  ylab("Water temp.") + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(Watertemp_c ~ Station, data = df_full)
#summary(model)

p_full <- plot_grid(p3 + rremove("legend"),
                    p4 + rremove("legend"),
                 #   p5 + rremove("legend"),
                    p1 + rremove("legend"),
                    p2 + rremove("legend"),
                    #labels = "auto",
                    ncol=2,nrow=2)

full_p <- plot_grid(p_1.2,p_1.1,p_full,p_2,labels =c("a","b","c","d"),nrow=2,ncol=2)

```

# Departure

```{r  departure, echo=FALSE}
library(streamMetabolizer)
library(unitted)
WL_02 <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_02$DateTime <- as.POSIXct(WL_02$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")

DO_df <- read.csv(here::here("data_cleaned/DO_01_cleaned.csv"))
DO_df$DateTime <- as.POSIXct(DO_df$DateTime,format="%m/%d/%Y %H:%M",tz="UTC")
DO_df$DOTemp_c <- ifelse(DO_df$DOTemp_c > 30, (DO_df$DOTemp_c-23)/9*5,DO_df$DOTemp_c)

CO2_df <- read.csv(here::here("data_cleaned/CO2_01_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

#convert to umol per l
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15
CO2_df$pCO2_air_ppm <- 418.53 # 2022 average manoa
CO2_df$air_pressure_atm <- CO2_df$Total_hPa / 1013.25 - 0.000967841
CO2_df$pCO2_air_atm <-  CO2_df$pCO2_air_ppm / 10^6  * CO2_df$air_pressure_atm
CO2_df$pCO2_w_atm <- CO2_df$CO2_ppm_adjusted / 10^6 
#henry's constant adjust for temp
CO2_df$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(CO2_df$WLTemp_01_c+273.15) - 1/T_STP_K))
CO2_df$KH_mol.m3.atm <- CO2_df$KH_mol.l.atm * 1000
CO2_df$CO2_sat_mol.L <- CO2_df$KH_mol.l.atm*CO2_df$pCO2_air_atm
CO2_df$CO2_sat_umol.L <- CO2_df$CO2_sat_mol.L*10^6
CO2_df$CO2_mol.L <- CO2_df$KH_mol.l.atm*CO2_df$pCO2_w_atm
CO2_df$CO2_umol.L <- CO2_df$CO2_mol.L*10^6

CO2_df <- CO2_df%>%select(DateTime,CO2_ppm_adjusted,pCO2_air_ppm,air_pressure_atm,CO2_umol.L,CO2_sat_umol.L)

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)
df_stn1_metab$date <- as.Date(df_stn1_metab$date)

Stn01 <- full_join(WL_02,DO_df, by=c("DateTime"))
Stn01 <- full_join(Stn01,CO2_df, by=c("DateTime"))


Stn01$DO_sat <- calc_DO_sat(temp=u(Stn01$WLTemp_c,"degC"), press=u(Stn01$AirPres_kpa*10,"mb"), sal=u(0,"PSU")) # units are checked

#convert to umol
Stn01$DO_sat_umolperL <- as.numeric(Stn01$DO_sat)/1000 / 32 * 10^6
Stn01$DO_umolperL <- Stn01$DO_mgL/1000 / 32 * 10^6
Stn01$DO_departure <- Stn01$DO_sat_umolperL - Stn01$DO_umolperL

#convert to umol
Stn01$DO_sat_umolperL <- as.numeric(Stn01$DO_sat)/1000 / 32 * 10^6
Stn01$DO_umolperL <- Stn01$DO_mgL/1000 / 32 * 10^6
Stn01$DO_departure <- Stn01$DO_umolperL - Stn01$DO_sat_umolperL 

Stn01$CO2_departure <-  Stn01$CO2_umol.L - Stn01$CO2_sat_umol.L 

Stn01$Date <- as.Date(Stn01$DateTime)

Stn01_summ <- Stn01%>%group_by(Date)%>%
  summarise(DO_departure= mean(DO_departure,na.rm=TRUE),
            CO2_departure = mean (CO2_departure,na.rm=TRUE),
            Q_m3s = mean(Q_m3s,na.rm=TRUE))
Stn01_summ <- full_join(Stn01_summ,df_stn1_metab%>%rename(Date=date), by=c("Date"))


ggplot(Stn01#%>%filter(Date=="2021-09-20")
       ,aes(x=DateTime,y=DO_departure,color=DateTime))

ggplot(Stn01%>%filter(Date>"2021-07-12"&Date<"2021-08-14")
       ,aes(x=CO2_departure,y=DO_departure,color=DateTime)) + 
    geom_abline(intercept = 0, slope = -.8,linetype="dashed",linewidth=1) + xlim(0,800) +
  geom_point() +
  geom_abline(intercept = 0, slope = -1)


p <- ggplot(Stn01_summ %>%drop_na(Q_m3s),aes(x=CO2_departure,y=DO_departure,color=log(Q_m3s*1000))) + 
  geom_point(size=3) + 
  geom_abline(intercept = 0, slope = -.8,linetype="dashed",linewidth=1) + 
  annotate('text',# x = 280, y = -190, 
            x = 200, y = -190, 
           label = 'RQ = .8', size = 5, angle='285') +
 xlab(expression(CO[2] ~'departure ('~mu*'mol' ~ L^-1~')')) +
  ylab(expression(O[2] ~'departure ('~mu*'mol' ~ L^-1~')')) +
  scale_color_continuous(
    name= expression('Discharge ( L'~s^-1~')'),
    breaks = c(4.6, 3.4, 2.3), 
    labels = c("100", "30", "10")) +
  theme_bw(base_size = 16)



```


