---
title: 'Long Term Data: Station01'
author: "Kriddie"
date: "2022-11-09"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
library(ggpubr)
library(gridExtra)

```

## R Markdown

long term data for station 1


#water level

```{r Solinst, echo=FALSE}

setwd(here::here("WL"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "WL_01"

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      Trash_WLData <- read.csv(file, skip=0, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                    quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*9.8064
#        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kPa")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
            quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
      }
    }
    if (exists("WLData")){
      Trash_WLData <- read.csv(file, skip=0, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*9.8064
#        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kpa")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
      }
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData=unique(WLData)
  WLData$DateTime <- paste(WLData$Date, WLData$Time)
  WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  WLData$DateTime <- round_date(WLData$DateTime, "5 mins")
  WLData <- WLData[,c("DateTime","WLPres_kpa","WLTemp_c")]
  WLData$Station <- "Stn01"
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

rm(Trash_WLData)

```
##read in wl 02 and wl 03
we also need to read in wl02 data because we will use it to fill in a gap in station 01 data

and we will try to also fil in data from 2019 with station 3 data from 2019 (note that station 3 moved to a different location between 2019 and 2021)
```{r Hobo WL}
#First the Hobos

setwd(here::here("WL"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("WL_02","WL_03")

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000

      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        }
      
#      WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
    WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
#      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        }
      
#      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
          Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData$Station <- site
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

WL_02 <- WL_02%>%filter(WLPres_kpa != 62.566)

### stn 03
WLData <- read.csv(here::here("WL/WL_2019stn3_2019-08-19NOTcompensated.csv"), skip=11, header = TRUE, sep = ",",quote = "\"",dec = ".", fill = TRUE, comment.char = "")

colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
WLData$DateTime <- paste(WLData$Date, WLData$Time)
WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%Y %H:%M:%S", tz="UTC")
WLData$DateTime <- round_date(WLData$DateTime, "5 mins")
WLData <- WLData[,c("DateTime","WLPres_kpa","WLTemp_c")]
WLData$Station <- "Stn03"

WL_03 <- WLData

rm(WLData)

```
## plot 
plot the water level so that each station data can be cleaned

```{r plot, echo=FALSE}

##clean data

plot_ly(WL_01, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```


#clean up some messy data

```{r clean, echo=FALSE}

WL_01$DateTime <- round_date(WL_01$DateTime,unit="15 minutes")

WL_01 <- WL_01%>%filter(WLPres_kpa > 63 & WLPres_kpa < 70)

#clean 2019 data 
WL_01 <- WL_01%>%filter(DateTime < as.POSIXct("2019-07-23 11:45", tz="UTC")|DateTime > as.POSIXct("2019-07-25 16:30"))
WL_01 <- WL_01%>%filter(DateTime < as.POSIXct("2019-07-16 13:00", tz="UTC")|DateTime > as.POSIXct("2019-07-17 13:00"))
#looks like WL changed in febuary
#Actually no - wierd
WL_01$WLPres_kpa[which(WL_01$DateTime < as.POSIXct("2022-02-12 13:00", tz="UTC"))] <- WL_01$WLPres_kpa[which(WL_01$DateTime < as.POSIXct("2022-02-12 13:00", tz="UTC"))] - (64.3919-63.8785)
WL_01 <- WL_01%>%filter(DateTime != as.POSIXct("2022-06-07 10:45", tz="UTC"))%>%filter(DateTime != as.POSIXct("2022-06-07 11:00", tz="UTC"))
```

##More issues
there i a discontinuity on February 12 2022. My best guess is that a damn built up, raising water level, and then broke through dropping it down again

 I'm not sure what I should doooo
 
 I think I will remove the data between December 29 2921 and march 8 - this looks like when the wierd build up started. Then I will use the discontinuity in October to bring down the water level. 
 
 now I'm realizing I just want to remove discharge readings during this time. So I will be deleting Q from Dec 24- march 3rd in a future chung

```{r clean 2, echo=FALSE}

#delete (commented out here so that i can keep wl by remove Q once Q is calculated)
#WL_01 <- WL_01%>%filter(DateTime < as.POSIXct("2021-12-24 23:45", tz="UTC")|DateTime > as.POSIXct("2022-03-03 13:45", tz="UTC"))
#move down
WL_01_subset <- WL_01%>%filter(DateTime > as.POSIXct("2022-03-03 13:45", tz="UTC") & 
                                 DateTime < as.POSIXct("2022-10-12 13:00", tz="UTC"))
WL_01_subset2 <- WL_01%>%filter(DateTime < as.POSIXct("2022-03-03 13:45", tz="UTC") | 
                                  DateTime > as.POSIXct("2022-10-12 13:00", tz="UTC"))
WL_01_subset$WLPres_kpa <- WL_01_subset$WLPres_kpa - (64.1242 - 63.6786)

#rbind
WL_01 <- rbind(WL_01_subset,WL_01_subset2)

rm(WL_01_subset,WL_01_subset2)

```
 
### Use WL_02 to predict WL_01
we are missing some data from WL_01. I'm hoping there is a strong enough relationship between WL_01 and WL_02 to fill in missing data

July 13th 10:15 to July 28 14:15


```{r fill in wl_01, echo=FALSE}
WL_01_02 <- full_join(WL_01,WL_02, by= "DateTime")
WL_01_02 <- WL_01_02[,c("DateTime","WLPres_kpa.x","WLPres_kpa.y")]
colnames(WL_01_02) <- c("DateTime","WL_01","WL_02")
WL_01_02 <- WL_01_02%>%filter(DateTime > as.POSIXct("2021-07-01 10:15:00", tz = "UTC")& DateTime < as.POSIXct("2021-07-13 14:15:00", tz = "UTC"))

mdl1_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02)
mdl2_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02 + I(WL_01_02$WL_02^2))
mdl3_1 <- lm(WL_01_02$WL_01 ~ WL_01_02$WL_02 + I(WL_01_02$WL_02^2) + I(WL_01_02$WL_02^3))
mdl4_1 <- lm(WL_01_02$WL_01 ~ I(WL_01_02$WL_02^2))

set.seed(20)
q <- seq(from=0, to=66, by=0.5)
y_mdl1 <- mdl1_1$coefficients[1] + mdl1_1$coefficients[2]*q
y_mdl2 <- mdl2_1$coefficients[1] + mdl2_1$coefficients[2]*q + mdl2_1$coefficients[3]*q^2
y_mdl3 <- mdl3_1$coefficients[1] + mdl3_1$coefficients[2]*q + mdl3_1$coefficients[3]*q^2 + mdl3_1$coefficients[4]*q^3
y_mdl4 <- mdl4_1$coefficients[1] + mdl4_1$coefficients[2]*q^2


plot(WL_01 ~ WL_02, data = WL_01_02 )
#lines(q,y_mdl1,col='firebrick1',lwd=1)
lines(q,y_mdl2,col='blue',lwd=1)
#lines(q,y_mdl3,col='yellow',lwd=1)
#lines(q,y_mdl4,col='green',lwd=1)
mtext("y=  - 72380  + 3420 *x - 53.81 *x^2 + 0.2823*x^3", side=3)

rm(mdl1_1,mdl2_1,mdl3_1,mdl4_1)
rm(WL_01_02)
```



```{r wl_01 gap, echo=FALSE}
WL_01_fill <- WL_02
WL_01_fill$WLPres_kpa <-   1351.0808 - 40.9546  *WL_01_fill$WLPres_kpa + 0.3257 *(WL_01_fill$WLPres_kpa)^2 
WL_01_fill <- WL_01_fill%>%filter(DateTime > as.POSIXct("2021-07-14 10:15:00", tz = "UTC")&
                          DateTime < as.POSIXct("2021-07-27 14:15:00", tz = "UTC"))
WL_01_fill$Station <- "WL_01"

WL_01 <- rbind(WL_01,WL_01_fill)
rm(WL_01_fill,WL_02)

#ggplot(WL_01, aes(x=DateTime, y=WLPres_kpa)) + geom_point()
```

#fill in data from 2019 with data from stn03

as wih previous chunk,  I'm hoping there is a strong enough relationship between WL_01 and WL_03 to fill in missing data

July 13th 10:15 to July 28 14:15


```{r fill in wl_01 2, echo=FALSE}
WL_01_03 <- right_join(WL_01,WL_03, by= "DateTime")
WL_01_03 <- WL_01_03[,c("DateTime","WLPres_kpa.x","WLPres_kpa.y")]
colnames(WL_01_03) <- c("DateTime","WL_01","WL_03")
#WL_01_03 <- WL_01_03%>%filter(DateTime < as.POSIXct("2019-0-01 10:15:00", tz = "UTC")& DateTime < as.POSIXct("2021-07-13 14:15:00", tz = "UTC"))

mdl1_1 <- lm(WL_01_03$WL_01 ~ WL_01_03$WL_03)
mdl2_1 <- lm(WL_01_03$WL_01 ~ WL_01_03$WL_03 + I(WL_01_03$WL_03^2))
mdl3_1 <- lm(WL_01_03$WL_01 ~ WL_01_03$WL_03 + I(WL_01_03$WL_03^2) + I(WL_01_03$WL_03^3))
mdl4_1 <- lm(WL_01_03$WL_01 ~ I(WL_01_03$WL_03^2))

set.seed(20)
q <- seq(from=0, to=66, by=0.5)
y_mdl1 <- mdl1_1$coefficients[1] + mdl1_1$coefficients[2]*q
y_mdl2 <- mdl2_1$coefficients[1] + mdl2_1$coefficients[2]*q + mdl2_1$coefficients[3]*q^2
y_mdl3 <- mdl3_1$coefficients[1] + mdl3_1$coefficients[2]*q + mdl3_1$coefficients[3]*q^2 + mdl3_1$coefficients[4]*q^3
y_mdl4 <- mdl4_1$coefficients[1] + mdl4_1$coefficients[2]*q^2


plot(WL_01 ~ WL_03, data = WL_01_03 )
#lines(q,y_mdl1,col='firebrick1',lwd=2)
lines(q,y_mdl2,col='blue',lwd=2)
#lines(q,y_mdl3,col='yellow',lwd=2)
#lines(q,y_mdl4,col='green',lwd=2)
mtext("y= 485.6142  - 13.92432*x + 0.1144849*x^2", side=3)

rm(mdl1_1,mdl2_1,mdl3_1,mdl4_1)
rm(WL_01_03)
```

##that looks pretty good
use equation to fill in data

```{r wl_01 gap, echo=FALSE}

WL_01_fill <- WL_03
WL_01_fill$WLPres_kpa <-   485.6142 - 13.92432 *WL_01_fill$WLPres_kpa + 0.1144849 *(WL_01_fill$WLPres_kpa)^2
WL_01_fill <- WL_01_fill%>%filter(DateTime > as.POSIXct("2019-07-23 11:30:00", tz = "UTC")&
                          DateTime < as.POSIXct("2019-07-25 21:45:00", tz = "UTC"))
WL_01_fill$Station <- "WL_01"

WL_01 <- rbind(WL_01,WL_01_fill)
rm(WL_01_fill,WL_03)

WL_01 <- WL_01%>%filter(DateTime != as.POSIXct("2019-07-23 12:45:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-25 16:30:00",tz="UTC"))

WL_01$Station <- "Stn01"

#ggplot(WL_01, aes(x=DateTime, y=WLPres_kpa)) + geom_point()
```


## barometric data
now read in the barometric data

```{r baro loop, echo=FALSE}

###merge data with baro data###
setwd(here::here("Baro"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names=unique(sites_rp) #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","AirPres_kpa","AirTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}
```

### clean baro
```{r clean baro, echo=FALSE}

##clean BaroData

Baro <- Baro%>%filter(DateTime < as.POSIXct("2021-07-27 15:00:00", tz = "UTC")|
                          DateTime > as.POSIXct("2021-07-28 13:30:00", tz = "UTC"))

#ggplot(Baro,aes(x=DateTime,y=AirPres_kpa))+ geom_point()

```

### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

WL_01 <- left_join(Baro,WL_01,by="DateTime")

WL_01$Corrected_kpa <- WL_01$WLPres_kpa - WL_01$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_01$Total_kpa <- 
  WL_01$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_01$WL_m <- WL_01$Corrected_kpa * 0.101972
WL_01$Corrected_kpa <- NULL

```
#plot data
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_01 #%>% filter(DateTime > "2021-06-10")
       , 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Water level",
    y = "water level [m]", x = "") 

```

#Time for discharge!
this will take awhile so buckle up, baby

```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2019-07-24"
#enter start and end time that wetland was sampled
time <- "13:00:00"


WL_m <- WL_01%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m$WL_m)

```

#dischage rating curve
see excel file for station 01
field season 2022 looks compatible with field season 2021

This is before adding dummy data to improve x axis intercet
y = -0.0647x2 + 0.4162x - 0.0554
R² = 0.9567

This is after dummey data
y = .1789x2 + 0.2095x - 0.0246
R² = 0.9478

This is breaking up low and high flows
>low 
y = 2.0906x2 - 0.5608x + 0.0439
R² = 0.8983

>high with dummy values
y = 0.126*x2 + 0.255x - 0.0314
R² = 0.9473

intersect: 0.3019385

##change of plans!
I've desided to add in data from 2019, and also they seem somewhat compatible - so:
This is with added dummy data to improve x intercept

y = 0.3086*x2 + 0.1186x - 0.007
R² = 0.8801





```{r discharge, echo=FALSE}

#low
WL_01$Q_m3s <- NA
#WL_01[which(WL_01$WL_m < intercept),]$Q_m3s <- 2.0906*(WL_01[which(WL_01$WL_m < intercept),]$WL_m)^2 - 0.5608*WL_01[which(WL_01$WL_m < intercept),]$WL_m + 0.0439
#high
#WL_01[which(WL_01$WL_m > intercept),]$Q_m3s <- 0.126*(WL_01[which(WL_01$WL_m > intercept),]$WL_m)^2 + 0.255*WL_01[which(WL_01$WL_m > intercept),]$WL_m - 0.0314

WL_01$Q_m3s <- .3168*WL_01$WL_m^2 + 0.1123 * WL_01$WL_m - 0.0062
WL_01$Q_Ls <- WL_01$Q_m3s*1000


#WL_01$Q_m3s <- 0.126*(WL_01$WL_m)^2 + 0.255*WL_01$WL_m - 0.0314

#delete Q when there was a damn build up below station1 - this is so that I can keep WL for CO2 correction calculations
WL_01_subset1 <- WL_01%>%filter(DateTime < as.POSIXct("2021-12-24 23:45", tz="UTC")|DateTime > as.POSIXct("2022-03-03 13:45", tz="UTC"))
WL_01_subset2 <- WL_01%>%filter(DateTime > as.POSIXct("2021-12-24 23:45", tz="UTC")&DateTime < as.POSIXct("2022-03-03 13:45", tz="UTC"))
WL_01_subset2$Q_m3s <- NA
WL_01_subset2$Q_Ls <- NA

WL_01 <- rbind(WL_01_subset1,WL_01_subset2)

rm(WL_01_subset1,WL_01_subset2)

```

#plot discharge
```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = WL_01 #%>% filter(DateTime > "2021-06-10")
       , 
       aes(DateTime, Q_Ls)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Discharge",
    y = "Q [L s-1]", x = "") 

ggplot(data = WL_01# %>% filter(DateTime > "2021-06-10")
       , 
       aes(DateTime, WL_m)) +
  geom_point(color = "steelblue") +
  labs(title = "Station 01 Water level",
    y = "water level [m]", x = "") 

```

#CO2 time

```{r pressure, echo=FALSE}

setwd(here::here("CO2"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names=c("CO2_01","CO2wellV_01")


#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time),  format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
#   CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins")

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}

CO2_01$DateTime <- round_date(CO2_01$DateTime, "15 mins")
CO2wellV_01$DateTime <- round_date(CO2wellV_01$DateTime, "15 mins")

CO2_01$Station <- "Stn01"
CO2wellV_01$Station <- "Stn01"

```
# 2019 data

```{r add CO2 data rom 2019, echo=FALSE}

CO2_2019 <- read.csv(here::here("CO2/Vaisala_Data_2019.csv"))
CO2_2019 <- CO2_2019%>%filter(Inj.x=="No")
CO2_2019 <- CO2_2019[c(1,3)]
colnames(CO2_2019) <- c("DateTime","ppm")
CO2_2019$DateTime <- as.POSIXct(CO2_2019$DateTime,format="%m/%d/%y %H:%M", tz = "UTC")
#interpolate to 15 min
DateTime <- seq(ISOdate(2019,07,12), ISOdate(2019,08,14), by = "15 min")
DateTime_df <- data.frame(DateTime)
DateTime_df$DateTime <- as.POSIXct(DateTime_df$DateTime, format="%y-%m-%d %H:%M:%S", tz="UTC")  
CO2_2019 <- left_join(DateTime_df, CO2_2019, by = "DateTime")
CO2_2019$Station  <- "Stn01"
CO2_2019 <- CO2_2019%>%drop_na(ppm)

#bind
CO2_01 <- rbind(CO2_01,CO2_2019)

CO2_01 <- CO2_01[ order(CO2_01$DateTime , decreasing = TRUE ),]

rm(DateTime_df,CO2_2019)
```



#check data 

```{r check CO2 data plot, echo=FALSE}


##check data
plot_ly(CO2_01, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

plot_ly(CO2wellV_01, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```

```{r clean, echo=FALSE}
#CO2_01
#old from 2019 to 2022
CO2_01$ppm <- as.numeric(CO2_01$ppm)
CO2_01  <- CO2_01%>%
  filter(DateTime != as.POSIXct("2019-08-09 09:57:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2019-08-14 12:00:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2021-06-09 11:30:00", tz = "UTC") | DateTime >= as.POSIXct("2021-06-09 12:15:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-13 10:30:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 11:30:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-23 10:30:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-27 13:00:00", tz = "UTC"))%>%
#sensor out of water
  filter(DateTime < as.POSIXct("2021-06-19 04:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-25 10:30:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-06-02 12:00:00", tz = "UTC"))

#clean data from well vaisala wich has is different from the other vaisala in that it maxes out at 30,000. But it's tricky, the battery was having a big problem around this time so cleaning will be tricky. We will clean up everything that looks like it is having batter problems, as opposed to being in an error state because it is over 30000

#CO2wellV_01_test <- CO2wellV_01%>%rename("ppm_wellV"="ppm")
#CO2_01_test <- CO2_01%>%rename("ppm_oldV"="ppm")
#test <- left_join(CO2wellV_01_test,CO2_01_test,by = c("Station", "DateTime"))

CO2wellV_01 <-  CO2wellV_01%>%filter(DateTime < as.POSIXct("2023-01-14 01:00:00", tz = "UTC") &
                                       DateTime > as.POSIXct("2022-11-29 14:00:00", tz = "UTC"))

#bind
CO2_01 <- rbind(CO2_01,CO2wellV_01)
#CO2_01 <- CO2_01%>%filter(ppm>20)
#CO2_01 <- CO2_01%>%filter(ppm<15000)

rm(CO2wellV_01)
```

#plot

```{r plot, echo=FALSE}


ggplot(data = CO2_01, aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 

```

##Create Station Dataframes
we two different models of vaisala


```{r stations df, echo=FALSE}

Stn01 <- full_join(WL_01,CO2_01, by=c("DateTime","Station"))

#convert baro to hpa
#1 kPa = 10 hPa
#1 kPa = 0.101972 m
Stn01$Total_hPa <- Stn01$Total_kpa * 10

```

#correction vaisala data
make adjustments to ppm using water level data

```{r corect viaslal, echo=FALSE}

#old:
#Temperature dependence: -0.3% of reading / celcius (reference 25c/77F)
#Pressure dependence: +0.15% of reading / hPa (reference 1013hPa)

#Station 1 and 4 are old
#but it's more complicated than that, because 2019 data has already been corrected
#and then I added a differnt viasala that was set to have a higher maximum - 30,000


Stn01_subset1 <- Stn01%>%filter(DateTime < as.POSIXct("2021-06-09 11:30:00",tz="UTC"))
Stn01_subset1$adjusted_ppm <- Stn01_subset1$ppm

Stn01_subset2 <- Stn01%>%filter(DateTime > as.POSIXct("2021-06-09 11:30:00",tz="UTC")&
                                  DateTime < as.POSIXct("2022-11-29 14:00:00", tz = "UTC"))
Stn01_subset2$adjusted_ppm <- Stn01_subset2$ppm * (1 + (1013 - Stn01_subset2$Total_hPa) * 0.0015) * (1 - (25 - Stn01_subset2$WLTemp_c) * 0.003)

Stn01_subset3 <- Stn01%>%filter(DateTime > as.POSIXct("2022-11-29 14:00:00", tz = "UTC"))
Stn01_subset3$adjusted_ppm <- Stn01_subset3$ppm * (1 + (700 - Stn01_subset3$Total_hPa) * 0.0015) * (1 - (25 - Stn01_subset3$WLTemp_c) * 0.003)

Stn01 <- rbind(Stn01_subset1,Stn01_subset2,Stn01_subset3)
rm(Stn01_subset1,Stn01_subset2,Stn01_subset3)


```

#plot

```{r plot, echo=FALSE}


co2 <- ggplot(data = Stn01, aes(DateTime, adjusted_ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 
  
Q <- ggplot(data = Stn01, aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(#title = "Q  stations",
       y = "Q", x = "") 


grid.arrange(co2, Q, ncol=1)

all.figs <- ggarrange(NULL,co2, NULL,Q, ncol = 1,
               heights = c(0.2,1,0.2,1),
               labels = c("A","","B",""),
               font.label = list(size = 24, color = "black", face = "bold"),
              # label.x = .1,
              # label.y = .1,
               align="h", common.legend = FALSE
               )

```


#dissolved o2

```{r loop}

setwd(here::here("DO"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "DO_01"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(DOData)
rm(Temp_DOData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("DOData")){
      DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
  
        colnames(DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        DOData <- DOData[2:4]
        DOData$DO_mgL <- as.numeric(as.character(DOData$DO_mgL), digits=6)
        DOData$DOTemp_c <- as.numeric(as.character(DOData$DOTemp_c), digits=5)
      

    DOData$DateTime <- as.POSIXct(DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("DOData")){
      Temp_DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  

        colnames(Temp_DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        Temp_DOData <- Temp_DOData[2:4]
        Temp_DOData$DO_mgL <- as.numeric(as.character(Temp_DOData$DO_mgL), digits=6)
        Temp_DOData$DOTemp_c <- as.numeric(as.character(Temp_DOData$DOTemp_c), digits=5)
        }
      

          Temp_DOData$DateTime <- as.POSIXct(Temp_DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      DOData <- rbind(DOData, Temp_DOData)
      rm(Temp_DOData)
#    }
    
  }
  DOData$DateTime <- round_date(DOData$DateTime, "15 mins")
  DOData$Station <- site
  DOData=unique(DOData)
  assign((paste(site,sep="_")),DOData) #creates object with new appended data
  rm(DOData) #removes DOdata so that multiple sites aren't appended together
}

DO_01$Station <- "Stn01"

```

#check do data

```{r check CO2 data plot, echo=FALSE}


##check data
plot_ly(DO_01, x = ~DateTime, y = ~DO_mgL, type = 'scatter', mode = 'markers') 

#clean
DO_01 <- DO_01%>%filter(DO_mgL > -100)
```

#now for lux


```{r check Lux data plot, echo=FALSE}
##set folder for site ##

setwd(here::here("Lux"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("LUXabajo_01","LUXarriba_01")

#rm old files, if they exist
rm(LuxData)
rm(Temp_LuxData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("LuxData")){
      LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      LuxData=LuxData[,2:4]
      colnames(LuxData)=c("DateTime","Temp_C","Lux")  
      
    }
    if (exists("LuxData")){
      Temp_LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #if (!"Temp_C" %in% colnames(Temp_LuxData)){Temp_LuxData$Temp_C <- NA}
      Temp_LuxData=Temp_LuxData[,2:4]
      colnames(Temp_LuxData)=c("DateTime","Temp_C","Lux")  
      
      
      LuxData <- rbind(LuxData, Temp_LuxData)
      rm(Temp_LuxData)
    }
    
    
  }
  #colnames(LuxData)=c("row","DateTime","Temp_C","Lux")
  #LuxData=LuxData[,2:4]
  LuxData=unique(LuxData)
  LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
 # LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %H:%M", tz="UTC")
  assign((paste(site,"Lux_data",sep="_")),LuxData) #creates object with new appended data
  rm(LuxData) #removes WLdata so that multiple sites aren't appended together
}

LUXabajo_01_Lux_data$Station <- "Stn01"
LUXabajo_01_Lux_data <- LUXabajo_01_Lux_data %>%rename("Luxabajo" = "Lux")

LUXarriba_01_Lux_data$Station <- "Stn01"
LUXarriba_01_Lux_data <- LUXarriba_01_Lux_data %>%rename("Luxarriba" = "Lux")
```

#plot lux

```{r check CO2 data plot, echo=FALSE}


##check data
plot_ly(LUXabajo_01_Lux_data, x = ~DateTime, y = ~Luxabajo, type = 'scatter', mode = 'lines') 


plot_ly(LUXarriba_01_Lux_data, x = ~DateTime, y = ~Luxarriba, type = 'scatter', mode = 'lines') 

#clean 
#DO_06 <- DO_06%>%filter(DO_mgL > -100)
```

#merge data

```{r merge data, echo=FALSE}


Stn01 <- full_join(Stn01,DO_01, by=c('DateTime','Station'))
Stn01 <- full_join(Stn01,LUXabajo_01_Lux_data, by=c('DateTime','Station'))
Stn01 <- full_join(Stn01,LUXarriba_01_Lux_data, by=c('DateTime','Station'))

Stn01 <- Stn01[ order(Stn01$DateTime , decreasing = TRUE ),]

```

#read out data 
```{r read out data, echo=FALSE}

write.csv(Stn01, here::here("All_Station_Data/Stn01_2023-03-29.csv"),row.names = FALSE)

```


#plot for prelim paper

```{r merge data, echo=FALSE}

Stn01_filter <- Stn01%>%filter(DateTime > as.POSIXct("2021-0-01 00:00:00", tz = "UTC") & DateTime <= as.POSIXct("2022-06-01 12:00:00", tz = "UTC"))

DO_filter <- DO_01%>%filter(DateTime > as.POSIXct("2021-08-10 00:00:00", tz = "UTC") & DateTime <= as.POSIXct("2021-08-25 00:00:00", tz = "UTC"))%>%filter(DO_mgL < 2)


O2 <- ggplot(data = Stn01_filter , aes(DateTime, DO_mgL)) +
  geom_point(color = "#E69F00") +
  labs(#title = "CO2  stations",
       y = "O2 mg/L", x = "") 
co2 <- ggplot(data = Stn01_filter, aes(DateTime, ppm)) +
  geom_point(color = "#56B4E9") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 
Stn01_filter$Q_Ls <- Stn01_filter$Q_m3s * 1000
Q <- ggplot(data = Stn01_filter, aes(DateTime, Q_Ls)) +
  geom_point(color = "#009E73") +
  labs(#title = "Q  stations",
       y = "Q L/s", x = "") 
LuxUP <- ggplot(data = Stn01_filter, aes(DateTime, Luxarriba)) +
  geom_point(color = "#F0E442") +
  labs(#title = "Q  stations",
       y = "LUX above water", x = "") 
LuxDOWN <- ggplot(data = Stn01_filter, aes(DateTime, Luxabajo)) +
  geom_point(color = "#0072B2") +
  labs(#title = "Q  stations",
       y = "LUX below water", x = "") 

grid.arrange(O2, co2, Q, LuxUP,LuxDOWN, ncol=1)

all.figs <- ggarrange(NULL,co2, NULL,Q, ncol = 1,
               heights = c(0.2,1,0.2,1),
               labels = c("A","","B",""),
               font.label = list(size = 24, color = "black", face = "bold"),
              # label.x = .1,
              # label.y = .1,
               align="h", common.legend = FALSE
               )


#########
Stn01_filter2 <- Stn01_filter%>%select(c("DateTime","DO_mgL","ppm","Q_Ls","Luxarriba","Luxabajo"))

mdata <- melt(Stn01_filter2, id=c("DateTime")) 

#fall
f <- ggplot(mdata,
            aes(x=DateTime, y=value,color = variable)) + 
  geom_line(size = 3) 

f2 <-f + facet_wrap(~variable,ncol=1, scales = "free") +
  theme_bw(base_size = 18) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())  + 
theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
) +
       scale_color_discrete(labels=c('DO [mg/L]', 'CO2 [ppm]', 'Q [L/s]', 'Light above water [LUX]','Light below water [LUX]'))


#using tiff() and dev.off
tiff('LongTermData.tiff', units="in", width=5, height=4, res=300, compression = 'lzw')
f2
dev.off()


```