---
title: 'Long Term Data: Station04'
author: "Kriddie"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
```

##station 5 water level 

```{r read in data}
WL_05 <- read.csv(here::here("merged_data_raw/WL_05_merged_raw.csv"))
WL_05$DateTime <- as.POSIXct(WL_05$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

Baro <- read.csv(here::here("data_cleaned/Baro_data_all.csv"))
Baro$DateTime <- as.POSIXct(Baro$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")
Baro$X <- NULL

```

## plot 
plot the water level so that each station data can be cleaned
xs

```{r plot, echo=FALSE}
##clean data
p1 <- plot_ly(WL_05, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```


#clean

```{r clean, echo=FALSE}

WL_05 <- WL_05%>%
  filter(DateTime != as.POSIXct("2021-07-28 14:00:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-03-16 15:30:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-26 11:30:00", tz = "UTC"))

```


### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 
WL_05 <- left_join(Baro,WL_05,by="DateTime")

WL_05$Corrected_kpa <- WL_05$WLPres_kpa - WL_05$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_05$Total_kpa <- 
  WL_05$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_05$WL_m <- WL_05$Corrected_kpa * 0.101972
WL_05$Corrected_kpa <- NULL

```

#plot 2
plot with wl
```{r plot, echo=FALSE}
##clean data
p2 <- plot_ly(WL_05, x = ~DateTime, y = ~WL_m, type = 'scatter', mode = 'markers') 

```


#Time for discharge!


```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2021-07-19"
#enter start and end time that wetland was sampled
time <- "10:15:00"


WL_m <- WL_05%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m$WL_m)

```

#dischage rating curve
see excel file for station 05
field season 2022 looks compatible with field season 2021

high
y = 0.5715x2 + 0.5144x - 0.337
R² = 0.9577

low
y = 0.3109*x^2.2675
R² = 0.5347

intercept  = .5019

#oh dang discharge is 0 why?

```{r discharge, echo=FALSE}

WL_05_sub1 <- WL_05%>%filter(WL_m > .5019)
WL_05_sub2 <- WL_05%>%filter(WL_m < .5019)

WL_05_sub1$Q_m3s <- 0.5715*(WL_05_sub1$WL_m)^2 + 0.5144*WL_05_sub1$WL_m - 0.337
WL_05_sub2$Q_m3s <- 0.3109*(WL_05_sub2$WL_m)^2.2675

WL_05 <- rbind(WL_05_sub1,WL_05_sub2)

```

#plot 3
plot with Q

```{r plot, echo=FALSE}
##clean data
p3 <- plot_ly(WL_05, x = ~DateTime, y = ~Q_m3s, type = 'scatter', mode = 'markers') 

```

```{r write out wl, echo=FALSE}

#write.csv(WL_05, here::here("data_cleaned/WL_05_cleaned.csv"),row.names = FALSE)

```


#dissolved o2
```{r loop}

setwd(here::here("DO"))
all_files=list.files(pattern=".csv") #pulls out the csv files 
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "DO_05"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(DOData)
rm(Temp_DOData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("DOData")){
      DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
  
        colnames(DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        DOData <- DOData[2:4]
        DOData$DO_mgL <- as.numeric(as.character(DOData$DO_mgL), digits=6)
        DOData$DOTemp_c <- as.numeric(as.character(DOData$DOTemp_c), digits=5)
      

    DOData$DateTime <- as.POSIXct(DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("DOData")){
      Temp_DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  

        colnames(Temp_DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        Temp_DOData <- Temp_DOData[2:4]
        Temp_DOData$DO_mgL <- as.numeric(as.character(Temp_DOData$DO_mgL), digits=6)
        Temp_DOData$DOTemp_c <- as.numeric(as.character(Temp_DOData$DOTemp_c), digits=5)
        }
      

          Temp_DOData$DateTime <- as.POSIXct(Temp_DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      DOData <- rbind(DOData, Temp_DOData)
      rm(Temp_DOData)
#    }
    
  }
  DOData$DateTime <- round_date(DOData$DateTime, "15 mins")
  DOData$Station <- site
  DOData=unique(DOData)
  assign((paste(site,sep="_")),DOData) #creates object with new appended data
  rm(DOData) #removes DOdata so that multiple sites aren't appended together
}

DO_05$Station <- "Stn05"

```

#check do data

```{r check CO2 data plot, echo=FALSE}

#clean 
DO_05 <- DO_05%>%filter(DO_mgL > -100)%>%
   filter(DateTime < as.POSIXct("2021-07-11 10:10:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-12 18:30:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-18 05:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-21 12:45:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-22 05:30:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-22 13:30:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-23 12:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-23 15:30:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-24 08:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-26 03:00:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-26 13:00:00", tz = "UTC")|DateTime > as.POSIXct("2021-07-26 23:45:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2021-07-27 16:45:00", tz = "UTC")|DateTime > as.POSIXct("2021-07-28 14:30:00", tz = "UTC"))

##check data
p1 <- plot_ly(DO_05, x = ~DateTime, y = ~DO_mgL, type = 'scatter', mode = 'markers') 



#write out
#write.csv(DO_05, here::here("data_cleaned/DO_05_cleaned.csv"),row.names = FALSE)
```



#lux data

```{r check Lux data plot, echo=FALSE}
##set folder for site ##

setwd(here::here("Lux"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("LUXabajo_05","LUXarriba_05")

#rm old files, if they exist
rm(LuxData)
rm(Temp_LuxData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("LuxData")){
      LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      LuxData=LuxData[,2:4]
      colnames(LuxData)=c("DateTime","Temp_C","Lux")  
      
    }
    if (exists("LuxData")){
      Temp_LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #if (!"Temp_C" %in% colnames(Temp_LuxData)){Temp_LuxData$Temp_C <- NA}
      Temp_LuxData=Temp_LuxData[,2:4]
      colnames(Temp_LuxData)=c("DateTime","Temp_C","Lux")  
      
      
      LuxData <- rbind(LuxData, Temp_LuxData)
      rm(Temp_LuxData)
    }
    
    
  }
  #colnames(LuxData)=c("row","DateTime","Temp_C","Lux")
  #LuxData=LuxData[,2:4]
  LuxData=unique(LuxData)
  LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
  assign((paste(site,"Lux_data",sep="_")),LuxData) #creates object with new appended data
  rm(LuxData) #removes WLdata so that multiple sites aren't appended together
}

LUXabajo_05_Lux_data$Station <- "Stn05"
LUXarriba_05_Lux_data$Station <- "Stn05"

```

#plot lux

```{r check CO2 data plot, echo=FALSE}


##check data
p1 <- plot_ly(LUXabajo_05_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 


p2 <- plot_ly(LUXarriba_05_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 

#read out

#write.csv(LUXabajo_05_Lux_data, here::here("data_cleaned/LUX_underwater_05_cleaned.csv"),row.names = FALSE)

#write.csv(LUXarriba_05_Lux_data, here::here("data_cleaned/LUX_abovewater_05_cleaned.csv"),row.names = FALSE)
```


