---
title: 'Long Term Data: Station04'
author: "Kriddie"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

long term data for station 1

```{r library}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
```

##station 4 water level 

```{r read in data}
WL_04 <- read.csv(here::here("merged_data_raw/WL_04_merged_raw.csv"))
WL_04$DateTime <- as.POSIXct(WL_04$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

Baro <- read.csv(here::here("data_cleaned/Baro_data_all.csv"))
Baro$DateTime <- as.POSIXct(Baro$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")
Baro$X <- NULL

```


##clean data

```{r clean, echo=FALSE}


#WL_04 <- WL_04%>%filter(WLPres_kpa > 63)
WL_04 <- WL_04%>%
  filter(DateTime != as.POSIXct("2021-06-18 13:45:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2021-07-28 12:00:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2022-03-16 11:15:00",tz="UTC"))%>%
    filter(DateTime != as.POSIXct("2022-10-12 11:00:00",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2023-04-01 11:00:00",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2022-06-29 12:30:00",tz="UTC")|DateTime >= as.POSIXct("2022-06-29 14:45:00",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2022-07-12 12:15:00",tz="UTC")|DateTime >= as.POSIXct("2022-07-12 12:30:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-27 12:30:00",tz="UTC")|DateTime > as.POSIXct("2022-07-28 11:30:00",tz="UTC"))


```

```{r clean 2, echo=FALSE}
#shift oct 20 2021
WL_04[WL_04$DateTime < as.POSIXct("2021-10-20 13:00",tz="UTC"),]$WLPres_kpa <- WL_04[WL_04$DateTime < as.POSIXct("2021-10-20 13:00",tz="UTC"),]$WLPres_kpa - (64.16333 - 63.871)

#shift Dec 29 2021
WL_04[WL_04$DateTime < as.POSIXct("2021-12-29 13:15",tz="UTC"),]$WLPres_kpa <- WL_04[WL_04$DateTime < as.POSIXct("2021-12-29 13:15",tz="UTC"),]$WLPres_kpa - (63.834 - 63.719)

#shift 0ct 12 2022
WL_04[WL_04$DateTime < as.POSIXct("2022-10-12 10:45",tz="UTC"),]$WLPres_kpa <- WL_04[WL_04$DateTime < as.POSIXct("2022-10-12 10:45",tz="UTC"),]$WLPres_kpa - (63.763 - 63.59)

#shift Dec 01 2022 (0.1184201, .1138109)
WL_04[WL_04$DateTime < as.POSIXct("2022-12-01 13:15",tz="UTC"),]$WLPres_kpa <- WL_04[WL_04$DateTime < as.POSIXct("2022-12-01 13:15",tz="UTC"),]$WLPres_kpa - (63.437 - 63.378)

# Feb 18 2023, some wierd data around time of download. maybe there is also a shift, but not possbile to tell (check after baro pressure is subtracted out)
WL_04[WL_04$DateTime > as.POSIXct("2023-02-18 10:45",tz="UTC") & WL_04$DateTime < as.POSIXct("2023-02-18 17:45",tz="UTC"),]$WLPres_kpa <- NA


#WL_04 shifted on July 18th because of a storm, so I want to split up my rating curve with 2021 data and 2022 data for before and after the storm


```

### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

WL_04 <- left_join(Baro,WL_04,by="DateTime")

WL_04$Corrected_kpa <- WL_04$WLPres_kpa - WL_04$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_04$Total_kpa <- 
  WL_04$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_04$WL_m <- WL_04$Corrected_kpa * 0.101972
WL_04$Corrected_kpa <- NULL

WL_04 <- WL_04%>%filter(WL_m > 0)

```
## plot 2
plot the cm water level so that each station data can be cleaned

```{r plot 2, echo=FALSE}

p2 <- plot_ly(WL_04, x = ~DateTime, y = ~WL_m, type = 'scatter', mode = 'markers') 

```



#Time for discharge!


```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2022-07-27"
#enter start and end time that wetland was sampled
time <- "11:45:00"


WL_m <- WL_04%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m$WL_m)

```

#dischage rating curve
see excel file for station 04_update2023-12-19

#WL_04 shifted on July 18th because of a storm, so I want to split up my rating curve with 2021 data and 2022 data for before and after the storm

we also need to have a high and low rating curve it seems

Before 7/18/21, high
y = 0.8086* x2 + 0.3622* x - 0.0042
R² = 0.986
low
y = 0.0014*exp(47.564*x)R² = 0.9584

breakpoint: 0.0211788


After 7/18/21, high
y = 3.3124* x2 - 0.4161* x + 0.0091
R² = 0.9879

low
y = 0.0003*exp(26.029*x)
R² = 0.9412

breakpoint: 0.119757


```{r discharge, echo=FALSE}


WL_04$Q_m3s <- NA

#subset dataframes
WL_04_BeforeHigh <- WL_04%>%filter(DateTime < as.POSIXct("2021-07-18 02:45",tz="UTC"))%>%filter(WL_m>0.0211788)
WL_04_BeforeLow <- WL_04%>%filter(DateTime < as.POSIXct("2021-07-18 02:45",tz="UTC"))%>%filter(WL_m<=0.0211788)
WL_04_AfterHigh <- WL_04%>%filter(DateTime > as.POSIXct("2021-07-18 06:00",tz="UTC"))%>%filter(WL_m>0.119757)
WL_04_AfterLow <- WL_04%>%filter(DateTime > as.POSIXct("2021-07-18 06:00",tz="UTC"))%>%filter(WL_m<=0.119757)

WL_04_BeforeHigh$Q_m3s <- 0.8086*WL_04_BeforeHigh$WL_m^2 + 0.3622*WL_04_BeforeHigh$WL_m - 0.0042

WL_04_BeforeLow$Q_m3s <- 0.0014*exp(47.564*WL_04_BeforeLow$WL_m)


WL_04_AfterHigh$Q_m3s <- 3.3124*WL_04_AfterHigh$WL_m^2 - 0.4161* WL_04_AfterHigh$WL_m + 0.0091

WL_04_AfterLow$Q_m3s <- 0.0003*exp(26.029*WL_04_AfterLow$WL_m)

WL_04 <- rbind(WL_04_BeforeHigh,WL_04_BeforeLow,WL_04_AfterHigh,WL_04_AfterLow)


```

## plot 3
plot the Q so that each station data can be cleaned

```{r plot 2, echo=FALSE}

p3 <- plot_ly(WL_04, x = ~DateTime, y = ~Q_m3s, type = 'scatter', mode = 'markers') 


p3 <- plot_ly(WL_04, x = ~DateTime, y = ~Q_m3s, type = 'scatter', mode = 'markers') 

WL_04 <- WL_04[order(as.POSIXct(WL_04$DateTime, format="%Y-%m-%d %H:%M:%S")),]

#write.csv(WL_04, here::here("data_cleaned/WL_04_cleaned.csv"),row.names = FALSE)


```


#CO2 time

```{r pressure, echo=FALSE}

setwd(here::here("CO2"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names="CO2_04"


#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(site == "CO2_02"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time),  format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
#   CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins")

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}

CO2_04$Station <- "Stn04"

```

#check data 

```{r check CO2 data plot, echo=FALSE}
##check data
p1 <- plot_ly(CO2_04, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

#plot_ly(CO2_01%>%
#  filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```

#clean data

```{r clean, echo=FALSE}
#CO2_04
CO2_04 <- CO2_04%>%
  filter(DateTime > as.POSIXct("2021-06-11 12:00:00", tz = "UTC"))%>%
  filter(DateTime <= as.POSIXct("2021-06-14 03:00:00", tz = "UTC")|DateTime >= as.POSIXct("2021-06-14 14:30:00", tz = "UTC"))%>%
   filter(DateTime != as.POSIXct("2021-07-05 11:15:05", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-12 15:59:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 13:00:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2021-07-28 12:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-28 13:15:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-10-20 12:45:05", tz = "UTC")) %>%
#injection July 14
  filter(DateTime < as.POSIXct("2021-07-14 09:00:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 15:30:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-12 12:00:00", tz = "UTC")|DateTime > as.POSIXct("2022-10-19 14:30:00", tz = "UTC"))%>%
   filter(DateTime != as.POSIXct("2023-04-01 11:15:05", tz = "UTC"))%>%
  filter(ppm > 21)


CO2_04$DateTime <- round_date(CO2_04$DateTime,unit="15 minutes")
CO2_04 <- CO2_04 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))

```


#plot

```{r plot, echo=FALSE}
##check data
p2 <- plot_ly(CO2_04, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers')

ggplot(data = CO2_04, aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 

```

##Create Station Dataframes
we two different models of vaisala

#correction vaisala data
make adjustments to ppm using water level data

```{r corect viaslal, echo=FALSE}
Stn04_df <- right_join(WL_04,CO2_04, by=c("DateTime"))

#convert baro to hpa
#1 kPa = 10 hPa
#1 kPa = 0.101972 m
Stn04_df$WLPres_hPa <- Stn04_df$WLPres_kpa * 10

#correction vaisala data: make adjustments to ppm using water level data

#new

#The new viasalas are set to 700hPa and have an internal temperature, so do not ned to be corrected for temp
#the units for new vasialas are half of what they should be! 

#In 2021
#Station 2, 3 and Well 1 and 2 are new V

Stn04_df$adjusted_ppm <- Stn04_df$ppm * (1 + (700 - Stn04_df$WLPres_hPa) * 0.0015) * (1 - (6.7 - Stn04_df$WLTemp_c) * 0.003)

Stn04_df$Total_hpa <- Stn04_df$Total_kpa * 10

Stn04_df <- Stn04_df%>%select(
  Station,DateTime,Total_hpa,WLTemp_c,ppm,adjusted_ppm
)%>%rename(WLTemp_01_c=WLTemp_c,CO2_ppm = ppm,CO2_ppm_adjusted = adjusted_ppm)
Stn04_df$max_detect_ppm <- 10000

#write.csv(Stn04_df, here::here("data_cleaned/CO2_04_max1000_cleaned.csv"),row.names = FALSE)


```

#Dissolved Oxygen

```{r loop}

setwd(here::here("DO"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "DO_04"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(DOData)
rm(Temp_DOData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("DOData")){
      DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
  
        colnames(DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        DOData <- DOData[2:4]
        DOData$DO_mgL <- as.numeric(as.character(DOData$DO_mgL), digits=6)
        DOData$DOTemp_c <- as.numeric(as.character(DOData$DOTemp_c), digits=5)
      

    DOData$DateTime <- as.POSIXct(DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("DOData")){
      Temp_DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  

        colnames(Temp_DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        Temp_DOData <- Temp_DOData[2:4]
        Temp_DOData$DO_mgL <- as.numeric(as.character(Temp_DOData$DO_mgL), digits=6)
        Temp_DOData$DOTemp_c <- as.numeric(as.character(Temp_DOData$DOTemp_c), digits=5)
        }
      

          Temp_DOData$DateTime <- as.POSIXct(Temp_DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      DOData <- rbind(DOData, Temp_DOData)
      rm(Temp_DOData)
#    }
    
  }
  DOData$DateTime <- round_date(DOData$DateTime, "15 mins")
  DOData$Station <- site
  DOData=unique(DOData)
  assign((paste(site,sep="_")),DOData) #creates object with new appended data
  rm(DOData) #removes DOdata so that multiple sites aren't appended together
}

DO_04$Station <- "Stn04"

```

#check do data

```{r check CO2 data plot, echo=FALSE}


#clean 
DO_04 <- DO_04%>%filter(DO_mgL > -100)%>%
  filter(DateTime > as.POSIXct("2021-06-10 16:15:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2022-03-16 13:30:00", tz = "UTC") | DateTime > as.POSIXct("2022-03-16 14:15:00", tz = "UTC"))%>%
  
  filter(DateTime < as.POSIXct("2022-03-20 04:30:00", tz = "UTC") | DateTime > as.POSIXct("2022-03-26 02:00:00", tz = "UTC"))%>%
  
    filter(DateTime < as.POSIXct("2022-04-01 00:30:00", tz = "UTC") | DateTime > as.POSIXct("2022-04-02 08:30:00", tz = "UTC"))%>%
  
    
    filter(DateTime < as.POSIXct("2022-04-03 17:30:00", tz = "UTC") | DateTime > as.POSIXct("2022-04-19 22:15:00", tz = "UTC"))%>%
  
      filter(DateTime < as.POSIXct("2022-04-30 21:45:00", tz = "UTC") | DateTime > as.POSIXct("2022-05-16 08:00:00", tz = "UTC"))%>%
  
   filter(DateTime < as.POSIXct("2022-04-19 22:30:00", tz = "UTC") | DateTime > as.POSIXct("2022-04-30 18:45:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2022-06-02 10:00:00", tz = "UTC") | DateTime > as.POSIXct("2022-07-28 11:45:00", tz = "UTC"))%>%
   filter(DateTime < as.POSIXct("2022-10-12 10:45:00", tz = "UTC") | DateTime > as.POSIXct("2022-10-19 15:30:00", tz = "UTC"))


##check data
p1 <- plot_ly(DO_04, x = ~DateTime, y = ~DO_mgL, type = 'scatter', mode = 'markers') 


#write out
#write.csv(DO_04, here::here("data_cleaned/DO_04_cleaned.csv"),row.names = FALSE)
```


```{r check Lux data plot, echo=FALSE}
##set folder for site ##

setwd(here::here("Lux"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("LUXabajo_04","LUXarriba_04")

#rm old files, if they exist
rm(LuxData)
rm(Temp_LuxData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("LuxData")){
      LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      LuxData=LuxData[,2:4]
      colnames(LuxData)=c("DateTime","Temp_C","Lux")  
      
    }
    if (exists("LuxData")){
      Temp_LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #if (!"Temp_C" %in% colnames(Temp_LuxData)){Temp_LuxData$Temp_C <- NA}
      Temp_LuxData=Temp_LuxData[,2:4]
      colnames(Temp_LuxData)=c("DateTime","Temp_C","Lux")  
      
      
      LuxData <- rbind(LuxData, Temp_LuxData)
      rm(Temp_LuxData)
    }
    
    
  }
  #colnames(LuxData)=c("row","DateTime","Temp_C","Lux")
  #LuxData=LuxData[,2:4]
  LuxData=unique(LuxData)
  LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
  assign((paste(site,"Lux_data",sep="_")),LuxData) #creates object with new appended data
  rm(LuxData) #removes WLdata so that multiple sites aren't appended together
}

LUXabajo_04_Lux_data$Station <- "Stn04"
LUXabajo_04_Lux_data <- LUXabajo_04_Lux_data%>%
  select(Station,DateTime,Lux,Temp_C)

LUXarriba_04_Lux_data$Station  <- "Stn04"
LUXarriba_04_Lux_data$Lux <- as.numeric(LUXarriba_04_Lux_data$Lux)


```

#plot lux

```{r check CO2 data plot, echo=FALSE}


##check data
p1 <- plot_ly(LUXabajo_04_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 


p2 <- plot_ly(LUXarriba_04_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 

#read out

#write.csv(LUXabajo_04_Lux_data, here::here("data_cleaned/LUX_underwater_04_cleaned.csv"),row.names = FALSE)

#write.csv(LUXarriba_04_Lux_data, here::here("data_cleaned/LUX_abovewater_04_cleaned.csv"),row.names = FALSE)

```

