---
title: 'Long Term Data: Station02'
author: "Kriddie"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(dplyr)
library(reshape2)
library(purrr)
library(sjmisc)
library(ggpubr)
library(gridExtra)

```

## ABOUT

long term data for station 1

##read in wl03

```{r read in WL 03}
WL_03 <- read.csv(here::here("merged_data_raw/WL_03_merged_raw.csv"))
WL_03$DateTime <- as.POSIXct(WL_03$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

Baro <- read.csv(here::here("data_cleaned/Baro_cleaned.csv"))
Baro$DateTime <- as.POSIXct(Baro$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")

```
## plot 
plot the water level so that each station data can be cleaned
xs
```{r plot, echo=FALSE}

##clean data

p1 <- plot_ly(WL_03, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```




```{r clean, echo=FALSE}

WL_03 <- WL_03%>%filter(DateTime != as.POSIXct("2021-06-18 13:00:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2021-06-25 13:00:00", tz = "UTC")| DateTime > as.POSIXct("2021-06-25 13:45:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-07-27 11:45:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-10-20 13:15:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-19 16:15:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-12-01 12:45:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-02-18 11:15:00", tz = "UTC"))

```

##Unresolved issues
missing big chunk of data in field season 2022 :(

```{r plot, echo=FALSE}

ggplot(WL_03, aes(x=DateTime, y=WLPres_kpa)) + geom_point()
```


### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

WL_03 <- left_join(Baro,WL_03,by="DateTime")

WL_03$Corrected_kpa <- WL_03$WLPres_kpa - WL_03$AirPres_kpa

#calculate total pressure to correct viasala readings
WL_03$Total_kpa <- 
  WL_03$WLPres_kpa

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
WL_03$WL_m <- WL_03$Corrected_kpa * 0.101972
WL_03$Corrected_kpa <- NULL

```
#plot wl_m data

```{r plot, echo=FALSE}
##clean data
p2 <- plot_ly(WL_03, x = ~DateTime, y = ~WL_m, type = 'scatter', mode = 'markers') 

WL_03 <- WL_03%>%filter(DateTime < as.POSIXct("2023-02-18 10:45:00",tz="UTC") |
                          DateTime > as.POSIXct("2023-02-18 13:45:00",tz="UTC") )
```

#Time for discharge!
this will take awhile so buckle up, baby

```{r Find WL data for rating curve, echo=FALSE}

#enter date of collection
date <- "2022-07-27"
#enter start and end time that wetland was sampled
time <- "10:30:00"


WL_m <- WL_03%>%filter(DateTime == as.POSIXct(paste(date, time), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))

print(WL_m)

```

#dischage rating curve
see excel file for station 03
field season 2022 looks compatible with field season 2021

with dummy data:

y = 1.3749*x^2 - 0.4518*x + 0.0356
R2 = 0.944

```{r discharge, echo=FALSE}

WL_03$Q_m3s <- 1.3749*(WL_03$WL_m)^2 - 0.4518*WL_03$WL_m + 0.0356

```

```{r plot, echo=FALSE}
##clean data
p3 <- plot_ly(WL_03, x = ~DateTime, y = ~Q_m3s, type = 'scatter', mode = 'markers') 

#write.csv(WL_03,here::here("data_cleaned/WL_03_cleaned.csv"))


```


#CO2 time

```{r pressure, echo=FALSE}

setwd(here::here("CO2"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names="CO2_03"


#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(site == "CO2_02"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time),  format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
#   CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins")

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}

CO2_03$Station <- "Stn03"

```


#check data 
stn3 data is pretty messy. perhapes because it is out of the water sometime? but I really don't know. Everything after 2022 looks bad though and I think we should delete it

```{r check CO2 data plot, echo=FALSE}

CO2_03 <- CO2_03%>%filter(DateTime < as.POSIXct("2022-07-01 00:00:00"))
##check data
plot_ly(CO2_03, x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

#plot_ly(CO2_01%>%
#  filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```

```{r clean, echo=FALSE}

#CO2_03
CO2_03  <- CO2_03 %>%
  filter(DateTime < as.POSIXct("2021-06-25 13:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-02 12:15:00", tz = "UTC"))


CO2_03$DateTime <- round_date(CO2_03$DateTime,unit="15 minutes")
CO2_03 <- CO2_03 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))
CO2_03$Station <- "Stn03"

```



```{r plot, echo=FALSE}


ggplot(data = CO2_03, aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 

```

##Create Station Dataframes
we two different models of vaisala

```{r stations df, echo=FALSE}

Stn03 <- right_join(WL_03,CO2_03, by=c("DateTime","Station"))

#convert baro to hpa
#1 kPa = 10 hPa
#1 kPa = 0.101972 m
Stn03$Total_hPa <- Stn03$Total_kpa * 10

```

#correction vaisala data
make adjustments to ppm using water level data

```{r corect viaslal, echo=FALSE}
#new

#The new viasalas are set to 700hPa and have an internal temperature, so do not ned to be corrected for temp
#the units for new vasialas are half of what they should be! 

#Station 2, 3 and Well 1 and 2 are new V

#df_new$adjusted_ppm <- df_new$ppm * (1 + (700 - df_new$Total_hPa) * 0.0015) * (1 - (6.7 - df_new$WLTemp_c) * 0.003)
Stn03$adjusted_ppm <- NA
Stn03$adjusted_ppm <- (Stn03$ppm * 2 )* (1 + (700 - Stn03$Total_hPa) * 0.0015) 

```

#plot

```{r plot, echo=FALSE}


co2 <- ggplot(data = Stn03, aes(DateTime, adjusted_ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") 
  
Q <- ggplot(data = Stn03, aes(DateTime, Q_m3s)) +
  geom_point(color = "steelblue") +
  labs(#title = "Q  stations",
       y = "Q", x = "") 

```

#dissolved o2


```{r loop}

setwd(here::here("DO"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "DO_03"
#site_names = site_names[c(2,3,5,6)]

#rm old files, if they exist
rm(DOData)
rm(Temp_DOData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("DOData")){
      DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
  
        colnames(DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        DOData <- DOData[2:4]
        DOData$DO_mgL <- as.numeric(as.character(DOData$DO_mgL), digits=6)
        DOData$DOTemp_c <- as.numeric(as.character(DOData$DOTemp_c), digits=5)
      

    DOData$DateTime <- as.POSIXct(DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("DOData")){
      Temp_DOData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  

        colnames(Temp_DOData)=c("row","DateTime","DO_mgL","DOTemp_c")
        Temp_DOData <- Temp_DOData[2:4]
        Temp_DOData$DO_mgL <- as.numeric(as.character(Temp_DOData$DO_mgL), digits=6)
        Temp_DOData$DOTemp_c <- as.numeric(as.character(Temp_DOData$DOTemp_c), digits=5)
        }
      

          Temp_DOData$DateTime <- as.POSIXct(Temp_DOData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      DOData <- rbind(DOData, Temp_DOData)
      rm(Temp_DOData)
#    }
    
  }
  DOData$DateTime <- round_date(DOData$DateTime, "15 mins")
  DOData$Station <- site
  DOData=unique(DOData)
  assign((paste(site,sep="_")),DOData) #creates object with new appended data
  rm(DOData) #removes DOdata so that multiple sites aren't appended together
}

DO_03$Station <- "Stn03"

```

#check do data

```{r check CO2 data plot, echo=FALSE}

#clean 
#everything after november 2022 looks wierd. some is maybe salvagiblem but I just want to delete it
DO_03 <- DO_03%>%filter(DO_mgL > -100)%>%
  filter(DateTime > as.POSIXct("2021-06-10 14:45",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2022-11-19 10:45",tz="UTC"))
##check data
p1 <- plot_ly(DO_03, x = ~DateTime, y = ~DO_mgL, type = 'scatter', mode = 'markers') 

#read out
#write.csv(DO_03, here::here("data_cleaned/DO_03_cleaned.csv"),row.names = FALSE)

```


```{r check Lux data plot, echo=FALSE}
##set folder for site ##

setwd(here::here("Lux"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = c("LUXabajo_03","LUXarriba_03")

#rm old files, if they exist
rm(LuxData)
rm(Temp_LuxData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("LuxData")){
      LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      LuxData=LuxData[,2:4]
      colnames(LuxData)=c("DateTime","Temp_C","Lux")  
      
    }
    if (exists("LuxData")){
      Temp_LuxData <- read.csv(file, skip=2, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #if (!"Temp_C" %in% colnames(Temp_LuxData)){Temp_LuxData$Temp_C <- NA}
      Temp_LuxData=Temp_LuxData[,2:4]
      colnames(Temp_LuxData)=c("DateTime","Temp_C","Lux")  
      
      
      LuxData <- rbind(LuxData, Temp_LuxData)
      rm(Temp_LuxData)
    }
    
    
  }
  #colnames(LuxData)=c("row","DateTime","Temp_C","Lux")
  #LuxData=LuxData[,2:4]
  LuxData=unique(LuxData)
  LuxData$DateTime <- as.POSIXct(LuxData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
  assign((paste(site,"Lux_data",sep="_")),LuxData) #creates object with new appended data
  rm(LuxData) #removes WLdata so that multiple sites aren't appended together
}

LUXabajo_03_Lux_data$Station <- "Stn03"
LUXarriba_03_Lux_data$Station <- "Stn03"

```


#now we merge everything together!!

```{r merge dataframe, echo=FALSE}
Stn03_df <- full_join(WL_03, DO_03, by=c("DateTime","Station"))
Stn03_df <- full_join(Stn03_df, LUXabajo_03_Lux_data, by=c("DateTime","Station"))
Stn03_df <- full_join(Stn03_df, LUXarriba_03_Lux_data, by=c("DateTime","Station"))

```

```{r write out data, echo=FALSE}
write.csv(Stn03_df,here::here("MergedFiles/Stn03_df_2023-12-19.csv"))

```

#plot lux

```{r check CO2 data plot, echo=FALSE}


##check data
plot_ly(LUXabajo_03_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 


plot_ly(LUXarriba_03_Lux_data, x = ~DateTime, y = ~Lux, type = 'scatter', mode = 'lines') 

#clean 
#DO_06 <- DO_06%>%filter(DO_mgL > -100)
```