---
title: "LongTermData Plots Feb17"
author: "Kriddie"
date: "2025-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This R markdown is intended to contain all plots used for the publication of continuous long term data collected at cayambe coaca national park from 2019 to 2023

```{r import library}
library(here)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(zoo)
library(plotly)
library(cowplot)
library(viridis)
library(ggpubr)
library(scales)
```

## Read in data

```{r read in data and merge, echo=FALSE}
####stn01
WL_df <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
WL_df$DateTime_1 <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime <- ifelse(is.na(WL_df$DateTime_1)==TRUE,paste(WL_df$DateTime,"00:00:00",sep=" "),WL_df$DateTime )
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime_1 <- NULL

CO2_df <- read.csv(here::here("data_cleaned/CO2_01_max10000_cleaned.csv")) 
CO2_df$DateTime_1 <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime <- ifelse(is.na(CO2_df$DateTime_1)==TRUE,paste(CO2_df$DateTime,"00:00:00",sep=" "),CO2_df$DateTime )
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime_1 <- NULL

CO2_df <- unique(CO2_df)
CO2_df <- CO2_df%>%filter(DateTime!=as.POSIXct("2022-06-10 14:11:00",tz='UTC'))

stn01 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))


#### station 2
WL_df <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_df$DateTime_1 <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime <- ifelse(is.na(WL_df$DateTime_1)==TRUE,paste(WL_df$DateTime,"00:00:00",sep=" "),WL_df$DateTime )
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime_1 <- NULL

CO2_df <- read.csv(here::here("data_cleaned/CO2_02_max10000_cleaned_may14.csv")) 
CO2_df$DateTime_1 <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime <- ifelse(is.na(CO2_df$DateTime_1)==TRUE,paste(CO2_df$DateTime,"00:00:00",sep=" "),CO2_df$DateTime )
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime_1 <- NULL

stn02 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))

###stn03
WL_df <- read.csv(here::here("data_cleaned/WL_03_cleaned.csv"))
WL_df$DateTime_1 <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime <- ifelse(is.na(WL_df$DateTime_1)==TRUE,paste(WL_df$DateTime,"00:00:00",sep=" "),WL_df$DateTime )
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_df$DateTime_1 <- NULL

CO2_df <- read.csv(here::here("data_cleaned/CO2_03_max10000_cleaned.csv")) 
CO2_df$DateTime_1 <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime <- ifelse(is.na(CO2_df$DateTime_1)==TRUE,paste(CO2_df$DateTime,"00:00:00",sep=" "),CO2_df$DateTime )
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
CO2_df$DateTime_1 <- NULL

stn03 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))
stn03 <- stn03%>%filter(DateTime > as.POSIXct("2021-03-15 03:30:00"))

### station 04
##STILL NEED TO FIX time 00:00:00

WL_df <- read.csv(here::here("data_cleaned/WL_04_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
#test for duplicates


CO2_df <- read.csv(here::here("data_cleaned/CO2_04_max10000_cleaned.csv")) 
CO2_df$DateTime <- as.POSIXct(CO2_df$DateTime, format="%Y-%m-%d %H:%M:%S",tz="UTC")
#test for duplicates
test <- CO2_df$DateTime[duplicated(CO2_df$DateTime)]
test2 <- as.data.frame(test)

stn04 <- full_join(WL_df,CO2_df,by=c("DateTime","Station"))

### station 05 & 06
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))%>%drop_na(WL_m)
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
#test for duplicates
test <- stn05$DateTime[duplicated(stn05$DateTime)]
test2 <- as.data.frame(test)

stn06 <- read.csv(here::here("data_cleaned/WL_06_cleaned.csv"))%>%drop_na(WL_m)
stn06$DateTime <- as.POSIXct(stn06$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
#test for duplicates
test <- stn06$DateTime[duplicated(stn06$DateTime)]
test2 <- as.data.frame(test)

stn_colmillo <- full_join(stn05,stn06,by=c("DateTime"))

### join all
all_stn <- full_join(stn01 %>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_01 = Q_m3s,CO2_ppm_01=CO2_ppm_adjusted),
                     stn02%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_02 = Q_m3s,CO2_ppm_02=CO2_ppm_adjusted),
                     by="DateTime")
all_stn <- full_join(all_stn,
                     stn03%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_03 = Q_m3s,CO2_ppm_03=CO2_ppm_adjusted),
                     by="DateTime")
all_stn <- full_join(all_stn,
                     stn04%>%select(DateTime,Q_m3s,CO2_ppm_adjusted)%>%rename(Q_m3s_04 = Q_m3s,CO2_ppm_04=CO2_ppm_adjusted),
                     by="DateTime")

all_stn <- all_stn%>%filter(DateTime < as.POSIXct("2023-04-01 11:15:00",tz="UTC"))


```

# context stats


```{r context stats, echo=FALSE}

#how many days were above detection?
stn01_summary <- stn01
stn01_summary$date <- as.Date(stn01_summary$DateTime)
stn01_summary_1 <- stn01_summary%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))%>%drop_na(mean_co2_adj)

stn01_above_detection  <- stn01
stn01_above_detection$CO2_ppm <- ifelse(stn01_above_detection$CO2_ppm< 10000,NA,stn01$CO2_ppm)
stn01_above_detection$date <- as.Date(stn01_above_detection$DateTime)
stn01_above_detection_sumary <- stn01_above_detection%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm))%>%drop_na(mean_co2)

#how many days of data collection?
stn01_summary_2 <- stn01_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

stn02_summary <- stn02
stn02_summary$date <- as.Date(stn02_summary$DateTime)
stn02_summary_2 <- stn02_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))


stn03_summary <- stn03
stn03_summary$date <- as.Date(stn03_summary$DateTime)
stn03_summary_1 <- stn03_summary%>%group_by(date)%>%
  summarise(mean_co2 = mean(CO2_ppm),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))%>%drop_na(mean_co2_adj)
#how many days of data collection?
stn03_summary_2 <- stn03_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

#how many days of data collection?
stn04_summary <- stn04
stn04_summary$date <- as.Date(stn04_summary$DateTime)
stn04_summary_2 <- stn04_summary%>%group_by(date)%>%
  summarise(mean_Q = mean(Q_m3s,na.rm=TRUE),
            mean_co2_adj = mean(CO2_ppm_adjusted,na.rm=TRUE))

colm_summary <- stn_colmillo
colm_summary$date <- as.Date(colm_summary$DateTime)
colm_summary_2 <- colm_summary%>%group_by(date)%>%
  summarise(mean_Q5 = mean(Q_m3s.x,na.rm=TRUE),
            mean_Q6 = mean(Q_m3s.y,na.rm=TRUE))%>%
  filter(mean_Q6!="NaN")


precip <- read.csv(here::here("Weather_station/M5025_Precipitation.csv"))
precip$DateTime <- as.POSIXct(precip$fecha,format="%m/%d/%y %H:%M",tz="UTC")
precip$date <- as.Date(precip$DateTime)

precip_daily <- precip%>%group_by(date)%>%
  summarise(daily_accu = sum(precipt_mm))

temp <- read.csv(here::here("Weather_station/M5025_AirTemp.csv"))
temp$DateTime <- as.POSIXct(temp$fecha,format="%m/%d/%y %H:%M",tz="UTC")
temp$date <- as.Date(temp$DateTime)

temp_daily <- temp%>%group_by(date)%>%
  summarise(daily_temp = mean(AirTemp_c))

```



## extract highest peaks from each month

```{r storm hysterises, echo=FALSE}

#storm that goes with C6
stormC6_begin = as.POSIXct("2019-07-11 15:30:00",tz="UTC")
stormC6_end = as.POSIXct("2019-07-16 08:45:00",tz="UTC")

storm1_peak = as.POSIXct("2019-07-14 14:30:00",tz="UTC")
storm1_begin = as.POSIXct("2019-07-14 00:45:00",tz="UTC")
storm1_end = as.POSIXct("2019-07-16 08:00:00",tz="UTC")

storm2_peak = as.POSIXct("2019-08-14 07:45:00",tz="UTC")
storm2_begin = as.POSIXct("2019-08-13 18:30:00",tz="UTC")
storm2_end = as.POSIXct("2019-08-15 05:15:00",tz="UTC")

storm2.1_peak = as.POSIXct("2019-08-04 18:30:00",tz="UTC")
storm2.1_begin = as.POSIXct("2019-08-01 13:45:00",tz="UTC")
storm2.1_end = as.POSIXct("2019-08-08 06:15:00",tz="UTC")

storm3_peak = as.POSIXct("2019-09-20 20:45:00",tz="UTC")
storm3_begin = as.POSIXct("2019-09-20 14:30:00",tz="UTC")
storm3_end = as.POSIXct("2019-09-22 07:00:00",tz="UTC")

storm4_peak = as.POSIXct("2019-10-24 05:00:00",tz="UTC")
storm4_begin = as.POSIXct("2019-10-23 11:00:00",tz="UTC")
storm4_end = as.POSIXct("2019-10-29 00:30:00",tz="UTC")


storm5_peak = as.POSIXct("2021-06-21 04:45:00",tz="UTC")
storm5_begin = as.POSIXct("2021-06-19 00:45:00",tz="UTC")
storm5_end = as.POSIXct("2021-06-23 02:15:00",tz="UTC")

storm6_peak = as.POSIXct("2021-07-01 02:45:00",tz="UTC")
storm6_begin = as.POSIXct("2021-06-29 22:45:00",tz="UTC")
storm6_end = as.POSIXct("2021-07-03 22:30:00",tz="UTC")

storm7_peak = as.POSIXct("2021-08-02 15:30:00",tz="UTC")
storm7_begin = as.POSIXct("2021-08-01 23:00:00",tz="UTC")
storm7_end = as.POSIXct("2021-08-04 12:00:00",tz="UTC")

storm8_peak = as.POSIXct("2021-09-06 17:00:00",tz="UTC")
storm8_begin = as.POSIXct("2021-09-05 00:30:00",tz="UTC")
storm8_end = as.POSIXct("2021-09-07 08:30:00",tz="UTC")

storm9_peak = as.POSIXct("2021-10-21 19:30:00",tz="UTC")
storm9_begin = as.POSIXct("2021-10-20 07:30:00",tz="UTC")
storm9_end = as.POSIXct("2021-10-22 16:00:00",tz="UTC")

storm10_peak = as.POSIXct("2021-11-19 10:00:00",tz="UTC")
storm10_begin = as.POSIXct("2021-11-18 22:15:00",tz="UTC")
storm10_end = as.POSIXct("2021-11-20 06:00:00",tz="UTC")

storm11_peak = as.POSIXct("2021-12-18 15:15:00",tz="UTC")
storm11_begin = as.POSIXct("2021-12-16 09:30:00",tz="UTC")
storm11_end = as.POSIXct("2021-12-24 11:00:00",tz="UTC")

storm12_peak = as.POSIXct("2022-03-15 14:15:00",tz="UTC")
storm12_begin = as.POSIXct("2022-03-13 20:00:00",tz="UTC")
storm12_end = as.POSIXct("2022-03-16 20:15:00",tz="UTC")

storm13_peak = as.POSIXct("2022-04-21 01:00:00",tz="UTC")
storm13_begin = as.POSIXct("2022-04-18 20:00:00",tz="UTC")
storm13_end = as.POSIXct("2022-04-23 05:15:00",tz="UTC")

storm14_peak = as.POSIXct("2022-05-16 11:45:00",tz="UTC")
storm14_begin = as.POSIXct("2022-05-14 07:45:00",tz="UTC")
storm14_end = as.POSIXct("2022-05-22 14:00:00",tz="UTC")

storm15_peak = as.POSIXct("2022-06-25 12:00:00",tz="UTC")
storm15_begin = as.POSIXct("2022-06-22 08:15:00",tz="UTC")
storm15_end = as.POSIXct("2022-06-30 03:15:00",tz="UTC")

storm16_peak = as.POSIXct("2022-07-04 07:30:00",tz="UTC")
storm16_begin = as.POSIXct("2022-07-01 22:00:00",tz="UTC")
storm16_end = as.POSIXct("2022-07-08 21:00:00",tz="UTC")

storm17_peak = as.POSIXct("2022-08-10 12:15:00",tz="UTC")
storm17_begin = as.POSIXct("2022-08-09 06:00:00",tz="UTC")
storm17_end = as.POSIXct("2022-08-18 23:30:00",tz="UTC")

storm18_peak = as.POSIXct("2022-09-11 06:30:00",tz="UTC")
storm18_begin = as.POSIXct("2022-09-10 01:45:00",tz="UTC")
storm18_end = as.POSIXct("2022-09-16 07:15:00",tz="UTC")

storm19_peak = as.POSIXct("2022-10-19 12:15:00",tz="UTC")
storm19_begin = as.POSIXct("2022-10-18 21:45:00",tz="UTC")
storm19_end = as.POSIXct("2022-10-21 21:00:00",tz="UTC")

storm20_peak = as.POSIXct("2022-11-20 22:30:00",tz="UTC")
storm20_begin = as.POSIXct("2022-11-20 12:45:00",tz="UTC")
storm20_end = as.POSIXct("2022-11-23 19:15:00",tz="UTC")

storm21_peak = as.POSIXct("2022-12-14 18:15:00",tz="UTC")
storm21_begin = as.POSIXct("2022-12-14 10:00:00",tz="UTC")
storm21_end = as.POSIXct("2022-12-21 10:30:00",tz="UTC")

storm22_peak = as.POSIXct("2023-01-24 16:00:00",tz="UTC")
storm22_begin = as.POSIXct("2023-01-23 22:15:00",tz="UTC")
storm22_end = as.POSIXct("2023-01-28 00:30:00",tz="UTC")

storm23_peak = as.POSIXct("2023-02-21 06:00:00",tz="UTC")
storm23_begin = as.POSIXct("2023-02-20 15:30:00",tz="UTC")
storm23_end = as.POSIXct("2023-02-26 16:30:00",tz="UTC")

storm24_peak = as.POSIXct("2023-03-04 15:15:00",tz="UTC")
storm24_begin = as.POSIXct("2023-03-03 10:30:00",tz="UTC")
storm24_end = as.POSIXct("2023-03-07 15:45:00",tz="UTC")


allstn_stormC6 <- all_stn%>%filter(DateTime>stormC6_begin&DateTime<stormC6_begin)

allstn_storm1 <- all_stn%>%filter(DateTime>storm1_begin&DateTime<storm1_end)
allstn_storm2 <- all_stn%>%filter(DateTime>storm2_begin&DateTime<storm2_end)
allstn_storm2.1 <- all_stn%>%filter(DateTime>storm2.1_begin&DateTime<storm2.1_end)
allstn_storm3 <- all_stn%>%filter(DateTime>storm3_begin&DateTime<storm3_end)
allstn_storm4 <- all_stn%>%filter(DateTime>storm4_begin&DateTime<storm4_end)
allstn_storm5 <- all_stn%>%filter(DateTime>storm5_begin&DateTime<storm5_end)
allstn_storm6 <- all_stn%>%filter(DateTime>storm6_begin&DateTime<storm6_end)
allstn_storm7 <- all_stn%>%filter(DateTime>storm7_begin&DateTime<storm7_end)
allstn_storm8 <- all_stn%>%filter(DateTime>storm8_begin&DateTime<storm8_end)
allstn_storm9 <- all_stn%>%filter(DateTime>storm9_begin&DateTime<storm9_end)
allstn_storm10 <- all_stn%>%filter(DateTime>storm10_begin&DateTime<storm10_end)
allstn_storm11 <- all_stn%>%filter(DateTime>storm11_begin&DateTime<storm11_end)
allstn_storm12 <- all_stn%>%filter(DateTime>storm12_begin&DateTime<storm12_end)
allstn_storm13 <- all_stn%>%filter(DateTime>storm13_begin&DateTime<storm13_end)
allstn_storm14 <- all_stn%>%filter(DateTime>storm14_begin&DateTime<storm14_end)
allstn_storm15 <- all_stn%>%filter(DateTime>storm15_begin&DateTime<storm15_end)
allstn_storm16 <- all_stn%>%filter(DateTime>storm16_begin&DateTime<storm16_end)
allstn_storm17 <- all_stn%>%filter(DateTime>storm17_begin&DateTime<storm17_end)
allstn_storm18 <- all_stn%>%filter(DateTime>storm18_begin&DateTime<storm18_end)
allstn_storm19 <- all_stn%>%filter(DateTime>storm19_begin&DateTime<storm19_end)
allstn_storm20 <- all_stn%>%filter(DateTime>storm20_begin&DateTime<storm20_end)
allstn_storm21 <- all_stn%>%filter(DateTime>storm21_begin&DateTime<storm21_end)
allstn_storm22 <- all_stn%>%filter(DateTime>storm22_begin&DateTime<storm22_end)
allstn_storm23 <- all_stn%>%filter(DateTime>storm23_begin&DateTime<storm23_end)
allstn_storm24 <- all_stn%>%filter(DateTime>storm24_begin&DateTime<storm24_end)

#label storms
allstn_storm1$storm_name <- "July 2019"
allstn_storm2$storm_name <- "Aug. 2019 incomplete"
allstn_storm2.1$storm_name <- "Aug. 2019"
allstn_storm3$storm_name <- "Sept. 2019"
allstn_storm4$storm_name <- "Oct. 2019"
allstn_storm5$storm_name <- "June 2021"
allstn_storm6$storm_name <- "July 2021"
allstn_storm7$storm_name <- "Aug. 2021"
allstn_storm8$storm_name <- "Sept. 2021"
allstn_storm9$storm_name <- "Oct. 2021"
allstn_storm10$storm_name <- "Nov. 2021"
allstn_storm11$storm_name <- "Dec. 2021"
# no large storms Jan and feb
allstn_storm12$storm_name <- "March 2022"
allstn_storm13$storm_name <- "April 2022"
allstn_storm14$storm_name <- "May 2022"
allstn_storm15$storm_name <- "June 2022"
allstn_storm16$storm_name <- "July 2022"
allstn_storm17$storm_name <- "Aug. 2022"
allstn_storm18$storm_name <- "Sept. 2022"
allstn_storm19$storm_name <- "Oct. 2022"
allstn_storm20$storm_name <- "Nov. 2022"
allstn_storm21$storm_name <- "Dec. 2022"
allstn_storm22$storm_name <- "Jan. 2023"
allstn_storm23$storm_name <- "Feb. 2023"
allstn_storm24$storm_name <- "March 2023"

#now calc time elapsed since storm start
allstn_storm1$time_elapsed <- allstn_storm1$DateTime - storm1_begin
allstn_storm2$time_elapsed <- allstn_storm2$DateTime - storm2_begin
allstn_storm2.1$time_elapsed <- allstn_storm2.1$DateTime - storm2.1_begin
allstn_storm3$time_elapsed <- allstn_storm3$DateTime - storm3_begin
allstn_storm4$time_elapsed <- allstn_storm4$DateTime - storm4_begin
allstn_storm5$time_elapsed <- allstn_storm5$DateTime - storm5_begin
allstn_storm6$time_elapsed <- allstn_storm6$DateTime - storm6_begin
allstn_storm7$time_elapsed <- allstn_storm7$DateTime - storm7_begin
allstn_storm8$time_elapsed <- allstn_storm8$DateTime - storm8_begin
allstn_storm9$time_elapsed <- allstn_storm9$DateTime - storm9_begin
allstn_storm10$time_elapsed <- allstn_storm10$DateTime - storm10_begin
allstn_storm11$time_elapsed <- allstn_storm11$DateTime - storm11_begin
allstn_storm12$time_elapsed <- allstn_storm12$DateTime - storm12_begin
allstn_storm13$time_elapsed <- allstn_storm13$DateTime - storm13_begin
allstn_storm14$time_elapsed <- allstn_storm14$DateTime - storm14_begin
allstn_storm15$time_elapsed <- allstn_storm15$DateTime - storm15_begin
allstn_storm16$time_elapsed <- allstn_storm16$DateTime - storm16_begin
allstn_storm17$time_elapsed <- allstn_storm17$DateTime - storm17_begin
allstn_storm18$time_elapsed <- allstn_storm18$DateTime - storm18_begin
allstn_storm19$time_elapsed <- allstn_storm19$DateTime - storm19_begin
allstn_storm20$time_elapsed <- allstn_storm20$DateTime - storm20_begin
allstn_storm21$time_elapsed <- allstn_storm21$DateTime - storm21_begin
allstn_storm22$time_elapsed <- allstn_storm22$DateTime - storm22_begin
allstn_storm23$time_elapsed <- allstn_storm23$DateTime - storm23_begin
allstn_storm24$time_elapsed <- allstn_storm24$DateTime - storm24_begin

allstn_storm <- rbind(allstn_storm1,allstn_storm2,allstn_storm2.1,allstn_storm3,allstn_storm4,allstn_storm5,allstn_storm6,allstn_storm7,allstn_storm8,allstn_storm9,allstn_storm10,allstn_storm11,allstn_storm12,allstn_storm13,allstn_storm14,allstn_storm15,allstn_storm16,allstn_storm17,allstn_storm18,allstn_storm19,allstn_storm20,allstn_storm21,allstn_storm22,allstn_storm23,allstn_storm24)
allstn_storm$month <- format(as.Date(allstn_storm$Date), "%m")
allstn_storm$year_month <- format(as.Date(allstn_storm$DateTime), "%Y-%m")


ggplot(allstn_storm11,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point()
ggplot(allstn_storm12,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point()

ggplot(allstn_storm,aes(x=Q_m3s_01,y=CO2_ppm_01,color=time_elapsed/60)) + geom_point() + 
  scale_x_continuous(transform = "log") + scale_y_continuous(transform = "log")

```

## storm plots

```{r storm sterf, echo=FALSE}

storm_subset <- allstn_storm %>%filter(storm_name!="Aug. 2019 incomplete"& storm_name!="Aug. 2022"& storm_name!="Aug. 2022"& storm_name!="Dec. 2022"& storm_name!="Feb. 2023"& storm_name!="Jan. 2023"& storm_name!="June 2022"& storm_name!="July 2022"& storm_name!="Jan. 2022"& storm_name!="March 2022" & storm_name!="March 2023"& storm_name!="Oct. 2019"& storm_name!="Sept. 2019"& storm_name!="Sept. 2022")
storm_subset$pCO2_ppm <- NA
#use CO2_ppm_02 for June 2021 storm
storm_subset$pCO2_ppm <- ifelse(storm_subset$storm_name == "June 2021", storm_subset$CO2_ppm_02, storm_subset$CO2_ppm_01)

storm_subset <- storm_subset%>%rename(Q = Q_m3s_02)

storm_subset$storm_name_1= factor(storm_subset$storm_name, levels=c("July 2019","Aug. 2019","June 2021","July 2021","Aug. 2021","Sept. 2021","Oct. 2021","Nov. 2021","Dec. 2021","April 2022","May 2022","Oct. 2022","Nov. 2022")) 

storm_subset$time_elapsed_day <- as.numeric(storm_subset$time_elapsed)/60/24

#facet wrap
p1 <- ggplot(storm_subset, aes(x=Q*1000,y=pCO2_ppm,color=as.numeric(time_elapsed)/60/24))+ 
  facet_wrap( ~ storm_name_1#, scales = "free"
              )  + geom_point() + 
  scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
    scale_color_viridis_c() +
  theme_bw(base_size = 18)

p2 <- ggplot(storm_subset%>%filter(storm_name!="July 2019"&storm_name!="Aug. 2019"&storm_name!="Nov. 2022"&storm_name!="Oct. 2022"), aes(x=Q*1000,y=pCO2_ppm,color=time_elapsed_day))+ 
  facet_wrap( ~ storm_name_1#, scales = "free"
              )  + geom_point() + 
  scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
    scale_color_viridis(option = "H",name= "days since\nstart of storm",guide=guide_colourbar(reverse = TRUE)) +
  ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18)

#now for all storms
allstn_storm$month_number <- format(as.Date(allstn_storm$Date), "%m")
allstn_storm$month_number  <- as.numeric(allstn_storm$month_number )
allstn_storm$month <- format(as.Date(allstn_storm$Date), "%B")

allstn_storm$month <- reorder(allstn_storm$month, allstn_storm$month_number)

p3 <- ggplot(allstn_storm,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) + geom_point() +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 


```

# Base flow

```{r base flow stn01, echo=FALSE}

all_stn$month_number <- format(as.Date(all_stn$Date), "%m")
all_stn$month_number  <- as.numeric(all_stn$month_number )
all_stn$month <- format(as.Date(all_stn$Date), "%B")

all_stn$month <- reorder(all_stn$month, all_stn$month_number)

p1<-ggplot(all_stn,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) + geom_point() +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

p2<-ggplot() + geom_point(data=all_stn,aes(x=Q_m3s_02*1000,y=CO2_ppm_01),color="grey") +
  geom_point(data=allstn_storm,aes(x=Q_m3s_02*1000,y=CO2_ppm_01,color=month)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

#load
p3<-ggplot() + geom_point(data=all_stn,aes(x=Q_m3s_02*1000,y=CO2_ppm_01*Q_m3s_02*1000),color="grey") +
  geom_point(data=allstn_storm,aes(x=Q_m3s_02*1000,y=CO2_ppm_01*Q_m3s_02*1000,color=month)) +
  #  scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)~CO[2] ~'load (ppm*L/s)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

p_full <- ggarrange(p2, p3, ncol=2, common.legend = TRUE, legend="bottom")  

```

# loading
```{r  CO2 load, echo=FALSE}
#extract base flow

ggplot(stn01,aes(x=DateTime,y=Q_Ls)) + geom_point()

fig <- plot_ly(data = stn01, x = ~DateTime, y = ~Q_Ls)
```
# Station 2

```{r  stn02, echo=FALSE}
all_stn$dif <- all_stn$CO2_ppm_01 - all_stn$CO2_ppm_02

test1 <- all_stn%>%filter(dif>0) 
test2 <- all_stn%>%filter(dif<0) 

p1 <- ggplot(all_stn%>%filter(dif>40)%>%
               filter(DateTime>"2020-01-01") , aes(x=Q_m3s_02,y=dif)) + geom_point() +  #scale_y_continuous(transform="log10", 
  theme_bw(base_size = 18)

p2 <- ggplot(all_stn %>%filter(dif< -40)%>%
               filter(DateTime>"2020-01-01"),
            aes(x=Q_m3s_02,y=abs(dif),color=CO2_ppm_02)) + geom_point() + scale_y_reverse()+ 
 # scale_x_log10() + 
  theme_bw(base_size = 18)

p3 <- ggplot(all_stn# %>%filter(dif < -40 |dif > 40 )
             %>%
               filter(DateTime>"2020-01-01"),
            aes(x=Q_m3s_02,y=dif,color=CO2_ppm_02)) + geom_point() + #scale_y_reverse()+ 
 # scale_x_log10() + 
  theme_bw(base_size = 18)

p_full <- plot_grid(p1,p2,ncol=1, align = "hv")

```
#Station 3
```{r  stn03, echo=FALSE}

#plot_ly(data=all_stn%>%filter(DateTime > as.POSIXct("2021-06-05 00:00:00")), x=~DateTime,y= ~CO2_ppm_03)

all_stn_remove_3 <- all_stn%>%filter(DateTime>as.POSIXct("2021-06-24 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-06-25 12:15:00",tz="UTC") | DateTime>as.POSIXct("2021-07-07 06:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-08-13 22:45:00",tz="UTC") | DateTime>as.POSIXct("2021-08-18 00:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-10-03 11:00:00",tz="UTC") | DateTime>as.POSIXct("2021-12-18 13:45:00",tz="UTC"))

all_stn_remove_3 <- all_stn_remove_3%>%filter(DateTime>as.POSIXct("2021-09-02 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-09-26 00:00:00",tz="UTC") | DateTime>as.POSIXct("2021-12-31 00:00:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-12-27 00:00:00",tz="UTC") | DateTime>as.POSIXct("2022-02-09 00:00:00",tz="UTC"))

#plot_ly(data=all_stn_remove, x=~DateTime,y= ~CO2_ppm_03)

stn3_p <- ggplot() + 
  geom_point(data=all_stn_remove_3,aes(x=CO2_ppm_01,y=CO2_ppm_03,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 

p4 <- ggplot() + 
  geom_point(data=all_stn,aes(x=Q_m3s_04,y=CO2_ppm_03,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 


```


# Station 4

```{r  stn04, echo=FALSE}

#plot_ly(data=all_stn%>%filter(DateTime > as.POSIXct("2021-06-05 00:00:00")), x=~DateTime,y= ~CO2_ppm_04)

all_stn_remove_4 <- all_stn%>%filter(DateTime!=as.POSIXct("2021-07-05 11:15:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2021-10-20 12:30:00",tz="UTC") | DateTime>as.POSIXct("2021-12-30 16:30:00",tz="UTC"))%>%
  filter(DateTime<as.POSIXct("2022-03-17 12:30:00",tz="UTC") | DateTime>as.POSIXct("2022-06-16 00:00:00",tz="UTC"))

p1 <-ggplot() + geom_point(data=allstn_storm,aes(x=Q_m3s_04*1000,y=CO2_ppm_04,color=month)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+ ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 

p2 <-ggplot() + geom_point(data=all_stn,aes(x=Q_m3s_04*1000,y=CO2_ppm_04)) +
    scale_y_continuous(transform = "log", breaks = c(1000,3000,10000,30000))+ 
  scale_x_continuous(transform = "log", breaks = c(3,10,30,100,300))+
  ylab(expression(italic(p)*CO[2] ~'(ppm)')) +     xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 18) 


p3 <- ggplot() + 
  geom_point(data=all_stn,aes(x=CO2_ppm_01,y=CO2_ppm_04,color=log(Q_m3s_04))) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,30000))+
  ylab(expression(italic(p)*CO[2] ~'upstream (ppm)')) +    xlab(expression(italic(p)*CO[2] ~'downstream (ppm)')) +   
  theme_bw(base_size = 18) 

all_stn_remove_4 <- all_stn_remove_4%>%rename(Month=month)
p4_stn4 <- ggplot() + 
  geom_point(data=all_stn_remove_4%>%filter(DateTime>"2021-06-06 00:00:00"), aes(x=CO2_ppm_01,y=CO2_ppm_04,color=Month)) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,25000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,25000),limits = c(1000,26000))+
  xlab(expression('Downstream'~italic(p)*CO[2] ~'(ppm)')) +
  ylab(expression(~italic(p)*CO[2] ~'(ppm)')) + 
  annotate("text", x = 1800, y = 11000, label = "Station 4") +
  theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1) 

all_stn_remove_3 <- all_stn%>%rename(Month=month)
p3_stn3 <- ggplot() + 
  geom_point(data=all_stn%>%filter(DateTime>"2021-07-06 00:00:00"&CO2_ppm_03>2500),aes(x=CO2_ppm_01,y=CO2_ppm_03,color=Month)) +
   scale_y_continuous(transform = "log", breaks = c(300,1000,3000,5000,10000,25000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,25000),limits = c(1000,26000))+
  xlab(expression('Downstream'~italic(p)~CO[2] ~'(ppm)')) +
  ylab(expression(~italic(p)*CO[2] ~'(ppm)')) + 
    annotate("text", x = 1800, y = 13000, label = "Station 3") +
  theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1) 

all_stn <- all_stn%>%rename(Month=month)
p2_stn2 <- ggplot() + 
  geom_point(data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
             ,aes(x=CO2_ppm_01,y=CO2_ppm_02,color=Month)) +
    scale_y_continuous(transform = "log", breaks = c(300,1000,3000,10000,15000,25000))+
  scale_x_continuous(transform = "log", breaks = c(300,1000,3000,10000,25000),limits = c(1000,26000))+
  xlab(expression('Downstream'~italic(p)*CO[2] ~'(ppm)')) +
  ylab(expression(~italic(p)*CO[2] ~'(ppm)')) + 
    annotate("text", x = 1800, y = 10000, label = "Station 2") +
theme_bw(base_size = 14) +  geom_abline(intercept = 0, slope = 1,linetype="dashed",linewidth=1)
##########
###this one for paper###
##########
plot_all <- ggarrange(p2_stn2+ rremove("xlab"),p3_stn3+ rremove("xlab"),p4_stn4, ncol=1, nrow=3, common.legend = TRUE, legend="right",labels="auto",heights = c(1,1,1.1))

#SOME STATS

lm_2 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_02), data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
           )
summary(lm_2)

lm_2 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_02), data=all_stn#%>%filter(DateTime>"2021-06-06 00:00:00")
           )
summary(lm_2)

lm_1 <- lm(log(CO2_ppm_01) ~ log(CO2_ppm_04), data=all_stn_remove)
summary(lm_1)

```

#summarize days of deployment
```{r  summarize, echo=FALSE}
#summarize days
all_stn_remove_4$Date <-as.Date(all_stn_remove_4$DateTime)
stn4_remove_sum <- all_stn_remove_4%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_04,na.rm=TRUE))
stn4_remove_sum <- all_stn_remove_4%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_04,na.rm=TRUE))
stn4_remove_sum <- stn4_remove_sum%>%filter(mean_Q!="NaN")

all_stn_remove_3$Date <-as.Date(all_stn_remove_3$DateTime)
stn3_remove_sum <- all_stn_remove_3%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_03,na.rm=TRUE))
stn3_remove_sum <- stn3_remove_sum%>%filter(mean_co2!="NaN")
stn3_remove_sum <- all_stn_remove_3%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_03,na.rm=TRUE))
stn3_remove_sum <- stn3_remove_sum%>%filter(mean_Q!="NaN")

all_stn$Date <-as.Date(all_stn$DateTime)
all_stn_sum_01 <- all_stn%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_01,na.rm=TRUE))
all_stn_sum_01 <- all_stn_sum_01%>%filter(mean_co2!="NaN")
stn1_remove_sum <- all_stn%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_01,na.rm=TRUE))
stn1_remove_sum <- stn1_remove_sum%>%filter(mean_Q!="NaN")

all_stn_sum_02 <- all_stn%>%group_by(Date)%>%
  summarise(mean_co2 = mean(CO2_ppm_02,na.rm=TRUE))
all_stn_sum_02 <- all_stn_sum_02%>%filter(mean_co2!="NaN")
all_stn_sum_02 <- all_stn%>%group_by(Date)%>%
  summarise(mean_Q = mean(Q_m3s_02,na.rm=TRUE))
all_stn_sum_02 <- all_stn_sum_02%>%filter(mean_Q!="NaN")



DO_05 <- read.csv(here::here("data_cleaned/DO_05_cleaned.csv"))
DO_05$DateTime <- as.POSIXct(DO_05$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
DO_05$date <- as.Date(DO_05$DateTime)
DO_05_sum <- DO_05%>%group_by(date)%>%summarise(
  DO_mean = mean(DO_mgL,rm.na=TRUE))%>%filter(DO_mean!="NaN")

```

## DOC read in data

```{r  DOC read in data, echo=FALSE}
DOC_2022 <- read.csv(here::here("DOC/DOC_KW_08-25-2022.csv"))%>%select(Date,time,site,DOC..mg.L.,TDN..mg.L.)%>%rename(Time=time,DOC=DOC..mg.L.,TDN=TDN..mg.L.,Station=site)%>%filter(Station=="Stn02"|Station=="Stn05")
DOC_2022$SampleType <- "Station"
DOC_2021 <- read.csv(here::here("DOC/DOC_9-1-2021_UNC_EDIT3.csv"))%>%select(Date,Time,Station,SampleType,DOC,TDN)
DOC_synop <-  read.csv(here::here("DOC/WaterChem_synoptic_2022-01-28.csv")) 
DOC_2019 <- read.csv(here::here("DOC/WaterChem_2019_EDIT.csv"))%>%select(Date,Time,Station,DOC..mg.L.,TDN..mg.L.)%>%rename(
  DOC=DOC..mg.L.,TDN=TDN..mg.L.)%>%drop_na(DOC)
DOC_2019$SampleType <- "Station"

DOC_df <- rbind(DOC_2022,DOC_2021#,DOC_2019
                )

DOC_df$DateTime <- as.POSIXct(paste(DOC_df$Date, DOC_df$Time), format="%m/%d/%y %H:%M", tz = "UTC")
DOC_df$DateTime <- round_date(DOC_df$DateTime,unit="15 minutes")

#formating 2021 DOC data
DOC_2021$Distance_from_peatland <- 
  ifelse(DOC_2021$Station=="Stn01",5,
         ifelse(DOC_2021$Station=="Stn02",56,
                ifelse(DOC_2021$Station=="Stn03",288,
                       ifelse(DOC_2021$Station=="Stn04",454,
                              ifelse(DOC_2021$Station=="Stn05",0+1,52+1)))))
DOC_2021$WS <- ifelse(DOC_2021$Station=="Stn05"|DOC_2021$Station=="Stn06","Colmillo","Gavilan")



#c6 data
C6_df <-read.csv(here::here("DOC/C6_df.csv"))
C6_df$DateTime <- as.POSIXct(C6_df$DateTime, format="%Y-%m-%d %H:%M:%S", tz = "UTC")
C6_df$DateTime <- round_date(C6_df$DateTime, unit="15 minute")
C6_df <- C6_df%>%drop_na(DateTime)
C6_df <- unique(C6_df)


#### station 2
WL_df_1 <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))%>%select(DateTime,Q_m3s)
WL_df_1$DateTime <- as.POSIXct(WL_df_1$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
WL_df_1 <- WL_df_1%>%filter(DateTime>as.POSIXct("2020-01-01 00:00"))

WL_df_2 <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))%>%select(DateTime,Q_m3s)
WL_df_2$DateTime <- as.POSIXct(WL_df_2$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
#WL_df_2 <- WL_df_2%>%filter(DateTime<as.POSIXct("2020-01-01 00:00"))

WL_df <- rbind(WL_df_1,WL_df_2
               )

##merge with doc
mergeDOC_df <- left_join(DOC_df,WL_df_2#%>%select(!Station)
                         , by=(c("DateTime")))

#DOC data from stn02 just seems a bit better than stn01
mergeDOC_df_subset1 <- mergeDOC_df%>%filter(DateTime < "2021-01-01")%>%filter(Station=="Stn01")
mergeDOC_df_subset2 <- mergeDOC_df%>%filter(DateTime > "2021-01-01")%>%filter(Station=="Stn02")

DOC_PeatlandOutlet <- rbind(mergeDOC_df_subset1,mergeDOC_df_subset2)

#merge C with station01 Q
C6_Q_df <- left_join(C6_df,WL_df,by="DateTime")
C6_Q_df <- C6_Q_df%>%filter(DateTime != as.POSIXct("2019-07-15 14:45",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 15:15",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 15:45",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 21:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 22:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 22:15",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2019-07-15 23:00",tz="UTC"))
C6_Q_df <- C6_Q_df[order(as.Date(C6_Q_df$DateTime, format="%Y-%m-%d %H:%M:%S")),]
#merge c6 (I think I will do this manually because otherwise it is too complicated)
C6_Q_df$DOC <- NA
C6_Q_df$TDN <- NA

#this sample was collected 2019-07-11 14:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-11 15:30:00",tz="UTC"), "DOC"] <- 3.7630
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-11 15:30:00",tz="UTC"), "TDN"] <- 0.11140

#This sample was collected at 2019-07-16 14:30:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-16 08:45:00",tz="UTC"), "DOC"] <- 4.6100
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-16 08:45:00",tz="UTC"), "TDN"] <- 0.16920

#This sample was collected at 2019-07-19 13:15:00
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-19 13:00:00",tz="UTC"), "DOC"] <- 3.7400
C6_Q_df[C6_Q_df$DateTime==as.POSIXct("2019-07-19 13:00:00",tz="UTC"), "TDN"] <- 0.10280


start <- as.POSIXct("2019-07-14 00:15",tz="UTC")
end <- as.POSIXct("2019-07-16 09:00",tz="UTC")
C6_Q_df_storm <- C6_Q_df%>%filter(DateTime>start&DateTime<end)
C6_Q_df_storm$time_elapsed <- C6_Q_df_storm$DateTime - start


#merge with co3 data
C6_Q_df <- left_join(C6_Q_df,all_stn,by="DateTime")
C6_Q_df_storm <- left_join(C6_Q_df_storm,all_stn,by="DateTime")
```
#plot paired C6 and CO2

```{r  plot CH4, echo=FALSE}
#hysteresis
C6_p3 <- ggplot(C6_Q_df_storm) + 
  geom_point(aes(x=Q_m3s*1000,y=CDOM_ppb,color=time_elapsed/60/24),size=4)+
    scale_color_viridis_c(name= "days since\nstart of storm",guide=guide_colourbar(reverse = TRUE)) +
#  scale_y_log10() + #scale_x_log10( limits = c(30,200)) +
  scale_y_continuous(breaks=c(30,35,40,45,50),labels=c("30.0","35.0","40.0","45.0","50.0")) +
 ylab('CDOM (ppb)') +  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 14)+
#  annotate('curve', x = 200, y = 45, xend = 130, yend = 50,
#  linewidth = 1, curvature = 0.3, arrow = arrow(length = unit(0.5, 'cm'))) +
#  annotate('curve', x = 120, y = 30, xend = 200, yend = 34, linewidth = 1, curvature = 0.2, arrow = arrow(length = unit(0.5, 'cm'))) 
  #this is the annotation layer for when there is not log transform
  annotate('curve', x = 170, y = 45, xend = 100, yend = 50,
  linewidth = 1, curvature = 0.3, arrow = arrow(length = unit(0.5, 'cm'))) +
  annotate('curve', x = 125, y = 29.5, xend = 175, yend = 34, linewidth = 1, curvature = 0.2, arrow = arrow(length = unit(0.5, 'cm')))

CO2_c6_hyst <- ggplot(C6_Q_df_storm) + 
  geom_point(aes(x=Q_m3s*1000,y=CO2_ppm_01,color=time_elapsed/60/24),size=4)+
    scale_color_viridis_c(name= "days since\nstart of storm", guide=guide_colourbar(reverse = TRUE)) +
#  scale_y_log10() + scale_x_log10( limits = c(30,200)) +
   ylab(expression(~italic(p)*CO[2] ~'(ppm)')) + 
 xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  theme_bw(base_size = 14)+
#  annotate('curve', x = 75, y = 4000, xend = 100, yend = 3100,
#  linewidth = 1, curvature = -0.2, arrow = arrow(length = unit(0.5, 'cm'))) +
#  annotate('curve', x = 100, y = 1100, xend = 55, yend = 1600, linewidth = 1, curvature = -0.2, arrow = arrow(length = unit(0.5, 'cm')))
  #this is annotation for when I don't log the axis
  annotate('curve', x = 75, y = 4000, xend = 120, yend = 3000,
  linewidth = 1, curvature = -0.1, arrow = arrow(length = unit(0.5, 'cm'))) +
  annotate('curve', x = 75, y = 1100, xend = 50, yend = 1600, linewidth = 1, curvature = -0.1, arrow = arrow(length = unit(0.5, 'cm')))

legend <- get_legend(
  # create some space to the left of the legend
  C6_p3 + theme(legend.box.margin = margin(0, 0, 0, 12))
)

plot_hyst_1 <- plot_grid(
  C6_p3+rremove("xlab")+rremove("legend"),        
  CO2_c6_hyst+rremove("legend"), 
  labels = "auto",ncol=1,align = "v")

plot_hyst_2 <- plot_grid(plot_hyst_1,legend,ncol = 2,rel_widths = c(1,.4))

```

# methane

```{r  plot CH4, echo=FALSE}
CH4_df <- read.csv(here::here("WaterChem/methane_df_merged.csv"))
CH4_df$DateTime <- as.POSIXct(CH4_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
CH4_df$pCH4_ppmv <- CH4_df$pCH4_ppm/(CH4_df$AirPres_kpa/101.3)

CH4_df_summary <- CH4_df%>%group_by(Site,Site2,DateTime)%>%
  summarise(
    Watertemp_c = mean(Watertemp_c),
    DO_mgL = mean(DO_mgL,na.rm=TRUE),
    Q_m3s = mean(Q_m3s),
    pCH4_ppmv = mean(pCH4_ppmv),
    CH4_umol.L = mean(CH4_umol.L)
  )

#DO a good predictor
site_names <- list(
  'Gavilan Outlet'="Wetland outlet",
  'Gavilan Center'="Wetland center")

site_labeller <- function(variable,value){
  return(site_names[value])
}

```

#temporal plots
```{r temporal plots,echo=FALSE}
#stats
m1 <- lm(log(DOC) ~ log(Q_m3s), data = DOC_PeatlandOutlet %>%filter(DateTime  > as.POSIXct("2020-01-01 00:00")))
summary(m1)

#spatial variance upstream to down
DOC_PeatlandOutlet$Date_format <- as.Date(DOC_PeatlandOutlet$Date,format = "%m/%d/%y")
DOC_PeatlandOutlet$Date_plot <- as.character(format(DOC_PeatlandOutlet$Date_format,format="%Y %B %d"))
DOC_PeatlandOutlet$Date_plot <- reorder(DOC_PeatlandOutlet$Date_plot, DOC_PeatlandOutlet$Date_format)

DOC_temporal <- ggplot(DOC_PeatlandOutlet %>%filter(DateTime  > as.POSIXct("2020-01-01 00:00")))+
  geom_point(aes(x=Q_m3s*1000, y=DOC#,fill=Date_plot
                 ),fill="black",shape=21,size=3) +   geom_smooth(aes(x=Q_m3s*1000, y=DOC),method='lm',color="grey50",linewidth=.5 ,se = FALSE) +
  ylab(expression(paste('DOC (mg ' , L^-1,")"))) +
  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  scale_x_continuous(transform = "log",breaks=c(10,30,100,300,1000)) + scale_y_continuous(transform = "log",breaks=c(1,2,3,4,5,6,7)) +
  labs(fill="Date") +
   theme_bw(base_size = 14)+
  annotate("text", label = paste0("atop('adj. '* R^2==0.87,p-value<.0001)"),
           x = 100, y = 2.6, size = 3, parse = TRUE)


###methane
#stats
#ch4
m2 <- lm(log(pCH4_ppmv) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Outlet")%>%filter(Site2!="50m")%>%filter(Site2!="100m"))
summary(m2)

#wetland center
m3 <- lm(log(pCH4_ppmv) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Center"))
summary(m3)


#spatial variance upstream to down
CH4_plot_df <-  CH4_df_summary%>%filter(Site!="Gavilan Edges")
CH4_plot_df$Site <- ifelse(CH4_plot_df$Site=="Gavilan Center","Waterbody Center","Outlet")


CH4_plot_df$Date_format <- as.Date(CH4_plot_df$DateTime,format = "%m/%d/%y")
CH4_plot_df$Date_plot <- as.character(format(CH4_plot_df$Date_format,format="%Y %B %d"))
CH4_plot_df$Date_plot <- reorder(CH4_plot_df$Date_plot, CH4_plot_df$Date_format)

p1_ch4 <- ggplot(CH4_plot_df%>%drop_na(DO_mgL)%>%filter(Site2!="50m")%>%filter(Site2!="100m")) +
  geom_smooth(method='lm',aes(x=DO_mgL,y=pCH4_ppmv,linetype=Site),linewidth=.5 ,se = FALSE)  +
    geom_point(aes(x=DO_mgL,y=pCH4_ppmv#,fill=Date_plot
                   ),fill="black",size=3,shape=21) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("DO at outlet (mg/l)")  + labs(linetype="") +
  scale_y_log10() + scale_x_continuous(transform = "log10",limits = c(4.5,7.5)) +
  theme_bw(base_size = 14) +
  guides(linetype=guide_legend(nrow=2,byrow=TRUE)) +
    theme(legend.position = "top")+

  annotate("text", label = paste0("atop('adj. '* R^2==1.0,p-value==0.02)"),
           x = 6.5, y = 1500/(60/101), size = 3, parse = TRUE) +
  annotate("text", label = paste0("atop('adj. '* R^2==0.54,p-value==0.32)"),
           x = 6.5, y = 280/(60/101), size = 3, parse = TRUE)


temporal_full_plot <- ggarrange(DOC_temporal,p1_ch4#,common.legend = TRUE
                                )

```

#spatial plots

```{r  spatial plots DOC ch4, echo=FALSE}

WL_df_2 <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))%>%select(DateTime,Q_m3s)
WL_df_2$DateTime <- as.POSIXct(WL_df_2$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
WL_df_2$Date <- as.Date(WL_df_2$DateTime)
#WL_df_2_summary <- WL_df_2%>%group_by(Date)%>%
#  summarise(Q_m3s=mean(Q_m3s,na.rm = TRUE))

DOC_2021_plot$Date <- as.Date(DOC_2021_plot$Date,format="%m/%d/%y")

#without colmillo data
DOC_spatial <- ggplot(DOC_2021_plot %>%filter(SampleType=="Station")%>%filter(WS=="Gavilan"))+
  geom_point(aes(x=Distance_from_peatland, y=DOC, fill=Date_plot), shape=21,size=3) + 
   geom_line(aes(x=Distance_from_peatland, y=DOC,color=Date_plot)) + 
    xlab("Distance from peatland outlet") +
  ylab(expression(paste('DOC (mg ' , l^-1,")"))) +
  labs(fill="Date",color="Date") +
   theme_bw(base_size = 14) +
  theme(legend.position = "top",
        legend.title = element_blank())  +
  guides(color=guide_legend(nrow=3,byrow=TRUE),
         fill=guide_legend(nrow=3,byrow=TRUE)) 

##longitudinal

CH4_df_summary$Date_format <- as.Date(CH4_df_summary$DateTime)
CH4_df_summary$Date_plot <- as.character(format(CH4_df_summary$Date_format,format="%Y %B %d"))
CH4_df_summary$Date_plot <- reorder(CH4_df_summary$Date_plot, CH4_df_summary$Date_format)


ch4_spatial <- ggplot(CH4_df_summary %>%filter(Site=="Gavilan Outlet")) +
    geom_point(aes(x=as.numeric(gsub('m','',Site2)),y=pCH4_ppmv, fill=Date_plot), size=3,shape=21) +
   geom_line(aes(x=as.numeric(gsub('m','',Site2)), y=pCH4_ppmv,color=Date_plot)) +
#  scale_y_continuous(transform = "log",breaks=c(2000,1000,500,200)) +
#  scale_fill_manual(labels = c("June-06","July-01","July-06"),values=c("#e41a1c","#377eb8","#4daf4a")) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("Distance from outlet (m)")  + labs(fill="Date collected",color="Date collected") +
  theme_bw(base_size = 14)+
  theme(legend.position = "top",
        legend.title = element_blank()) +
  guides(color=guide_legend(nrow=3,byrow=TRUE),
         fill=guide_legend(nrow=3,byrow=TRUE))

spatial_full_plot <- ggarrange(DOC_spatial,ch4_spatial#,common.legend = TRUE
)
```
#temporal TDN
```{r  plot tdn final, echo=FALSE}

#stats
m4 <- lm(log(TDN) ~ log(Q_m3s), data = DOC_PeatlandOutlet %>%filter(DateTime  > as.POSIXct("2020-01-01 00:00")))
summary(m4)

TDN_temporal <- ggplot(DOC_PeatlandOutlet %>%filter(DateTime  > as.POSIXct("2020-01-01 00:00")))+
  geom_point(aes(x=Q_m3s*1000, y=TDN#,fill=Date_plot
                 ),fill="black",shape=21,size=3) +   geom_smooth(aes(x=Q_m3s*1000, y=TDN),method='lm',color="grey50",linewidth=.5 ,se = FALSE) +
  ylab(expression(paste('TDN (mg ' , L^-1,")"))) +
  xlab(expression(paste('Discharge (L ' , s^-1,")"))) +
  scale_x_continuous(transform = "log",breaks=c(10,30,100,300,1000)
                     ) + scale_y_continuous(transform = "log"#,breaks=c(1,2,3,4,5,6,7)
                                            ) +
  labs(fill="Date") +
   theme_bw(base_size = 14)+
  annotate("text", label = paste0("atop('adj. '* R^2==0.53,p-value==0.03)"),
           x = 100, y = .08, size = 3, parse = TRUE)

```

#plot methane final
```{r  plot ch4 final, echo=FALSE}

#stats
#ch4
m2 <- lm(log(pCH4_ppm) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Outlet")%>%filter(Site2!="50m")%>%filter(Site2!="100m"))
summary(m2)

#wetland center
m3 <- lm(log(pCH4_ppm) ~ log(DO_mgL), data = CH4_df_summary %>%filter(Site=="Gavilan Center"))
summary(m3)

p1_ch4 <- ggplot(CH4_df_summary%>%filter(Site!="Gavilan Edges")%>%filter(Site2!="50m")%>%filter(Site2!="100m")%>%filter(DateTime<"2022-09-01")) +
  geom_smooth(method='lm',aes(x=DO_mgL,y=pCH4_ppm),color="grey50",linewidth=.5 ,se = FALSE) +
      facet_wrap(.~Site, labeller=site_labeller,ncol=1,scales="free_y") +
    geom_point(aes(x=DO_mgL,y=pCH4_ppm),fill="orange",size=3,shape=21) +
     ylab(expression(italic(p)*CH[4] ~'(ppm)')) + xlab("DO at outlet (mg/l)")  + labs(fill="Date collected") +
  scale_y_log10() + scale_x_log10() +
  theme_bw(base_size = 14) 


```


#plot DO

```{r  O2, echo=FALSE}

Stn01 <- read.csv(here::here("MergedFiles/Stn01_May7.csv"))
Stn01$Date <- as.Date(Stn01$Date)
Stn01 <- Stn01%>%drop_na(CO2_departure)%>%drop_na(DO_departure)

Stn01_0 <- Stn01%>%group_by(Date)%>%summarise(mean_do = mean(DO_mgL,na.rm=TRUE))

#how many days are DO = 0?
#stn 1 144
#stn 5 
do_stn1 <- read.csv(here::here("data_cleaned/DO_01_cleaned.csv"))
do_stn1$DateTime <- as.POSIXct(do_stn1$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
do_stn1$Date <- as.Date(do_stn1$DateTime)
do_stn1 <- do_stn1%>%filter(DO_mgL<=0)%>%group_by(Date)%>%summarise(mean_do = mean(DO_mgL,na.rm=TRUE))
ggplot(do_stn1,aes(x=DateTime,y=DO_mgL)) + geom_point()
```

# waterfall

```{r  waterfall, echo=FALSE}
inj_df <- read.csv(here::here("MergedFiles/all_2019_Data.csv"))%>%filter(Inj.x=="Yes")
inj_df$DateTime <- as.POSIXct(inj_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

inj_df_2021 <- read.csv(here::here("MergedFiles/Inj_df_2019July14.csv"))%>%select(DateTime,pCO2_80m_adj,pCO2_120m_adj)
inj_df_2021$DateTime <- as.POSIXct(inj_df_2021$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
inj_df_2021 <- inj_df_2021%>%melt(id.vars = "DateTime")

#discharge
WL_df <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_df$DateTime <- as.POSIXct(WL_df$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
WL_df <- WL_df%>%filter(DateTime<"2019-08-31")%>%select(DateTime,Q_m3s)

inj_df <- left_join(inj_df,WL_df,by="DateTime")
inj_df_summary <- inj_df%>%group_by(as.Date(DateTime))%>%
  summarise(Q_mean = mean(Q_m3s,na.rm=TRUE))

#injection 1
inj_df_1 <- inj_df%>%filter(DateTime < "2019-07-22")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_1$inj_number <- "inj_1"

inj_df_2 <- inj_df%>%
  filter(DateTime > "2019-07-22"&
            DateTime < "2019-07-24")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_2$inj_number <- "inj_2"

inj_df_3 <- inj_df%>%
  filter(DateTime > "2019-07-24"&DateTime < "2019-07-29")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_3$inj_number <- "inj_3"

inj_df_4 <- inj_df%>%filter(DateTime > "2019-07-29"&
                              DateTime < "2019-08-05")%>%select(
  DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% melt(id.vars = "DateTime")
inj_df_4$inj_number <- "inj_4"

inj_df_5 <- inj_df%>%
  filter(DateTime > "2019-08-05"& DateTime < "2019-08-08")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>% 
  melt(id.vars = "DateTime")
inj_df_5$inj_number <- "inj_5"

inj_df_6 <- inj_df%>%
  filter(DateTime > "2019-08-08")%>%
  select(DateTime,V1_adjusted,V2_adjusted,V3_adjusted,V4_adjusted)%>%
  melt(id.vars = "DateTime")
inj_df_6$inj_number <- "inj_6"

inj_all <- rbind(inj_df_1,inj_df_2,inj_df_3,inj_df_4,inj_df_5,inj_df_6)


p_2 <- ggplot(inj_df_2,aes(x=DateTime,y=value,color=variable)) + geom_point()

p_3 <- ggplot(inj_df_3,aes(x=DateTime,y=value,color=variable)) + geom_point()


p_5 <- ggplot(inj_df_5,aes(x=DateTime,y=value,color=variable)) + geom_point()

p_6 <- ggplot(inj_df_6,aes(x=DateTime,y=value,color=variable)) + geom_point()



p_45 <- ggplot(inj_df_2021%>%filter(variable!="pCO2_45m")%>%filter(DateTime < as.POSIXct("2021-07-14 12:00:00",tz="UTC")),aes(x=DateTime,y=value,color=variable)) + geom_point() + 
  x_lab()


```

# metabolism

```{r  metabolism, echo=FALSE}

#station 1
stn01 <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
stn01$DateTime <- as.POSIXct(stn01$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn01$date <- as.Date(stn01$DateTime,format="%Y-%m-%d")
stn01_summary<- stn01 %>%group_by(date)%>%summarise(discharge_stn01 = mean(Q_Ls))

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn1_metab$GPP_mean <- ifelse(df_stn1_metab$GPP_mean < 0,0,df_stn1_metab$GPP_mean )
df_stn1_metab$date <- as.Date(df_stn1_metab$date)

stn01_summary <- left_join(df_stn1_metab,stn01_summary,by="date")

p_test <- ggplot(stn01_summary,aes(x=discharge_stn01,y=ER_mean)) + geom_point()

m.stn1 <- lm(ER_mean~discharge_stn01,data=stn01_summary)
summary(m.stn1)

#staton 2
df_stn2_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station2_fieldlight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn2_metab$GPP_mean <- ifelse(df_stn2_metab$GPP_mean < 0,0,df_stn2_metab$GPP_mean )
df_stn2_metab$date <- as.Date(df_stn2_metab$date)


#station 5
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn05$date <- as.Date(stn05$DateTime,format="%Y-%m-%d")
stn05_summary<- stn05 %>%group_by(date)%>%
  summarise(discharge_stn05 = mean(Q_m3s))

df_stn5_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station5_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%
  filter(ER_Rhat < 1.05)%>%
  filter(GPP_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn5_metab$GPP_mean <- ifelse(df_stn5_metab$GPP_mean < 0,0,df_stn5_metab$GPP_mean )
df_stn5_metab$date <- as.Date(df_stn5_metab$date)

df_stn5_metab <- left_join(df_stn5_metab,stn05_summary,by="date")

m.stn5 <- lm(ER_mean~discharge_stn05,data=df_stn5_metab)
summary(m.stn5)
#evaluate Q v ER correlation
p_test <- ggplot(df_stn5_metab,aes(x=discharge_stn05,y=ER_mean)) + geom_point()

p_test <-ggplot(df_stn5_metab,aes(x=date,y=discharge_stn05)) + geom_point()

#remove high flows
df_stn5_metab <- df_stn5_metab%>%filter(discharge_stn05 < .1)



m2.stn5 <- lm(ER_mean~discharge_stn05,data=df_stn5_metab)
summary(m2.stn5)
#merge dataframes
df_metabe <- full_join(df_stn5_metab,df_stn1_metab,by="date")
#plot

dates <- data.frame(
  seq(as.Date('2019-07-13'), as.Date('2022-04-03'), by = 'days'))
colnames(dates) <- "date"

df_stn1_metab <- full_join(df_stn1_metab,dates,by="date")

df_stn1_metab$GPP_mean_CO2 <- (df_stn1_metab$GPP_mean*44/32)
df_stn1_metab$GPP_97.5pct_CO2 <- (df_stn1_metab$GPP_97.5pct*44/32)
df_stn1_metab$ER_mean_CO2 <- (df_stn1_metab$ER_mean*44/32)
df_stn1_metab$ER_97.5pct_CO2 <- (df_stn1_metab$ER_97.5pct*44/32)

p_1.1 <-ggplot(df_stn1_metab%>%
               filter(date > as.Date("2021-07-01")&date < as.Date("2021-10-01")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
  ylab(expression(paste('Metabolim (g C' ,~m^-2~y^-1,")"))) + xlab("Station 1: 2022") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2021-07-05"),as.Date("2021-07-05")), y = c(8,9), label = c("ER", "GPP"),size = 3)


p_1.2 <-ggplot(df_stn1_metab%>%
               filter(date < as.Date("2020-01-10")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
  ylab(expression(paste('Metabolim (g C' ,~m^-2~y^-1,")"))) + xlab("Station 1: 2019 - 2020") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2019-07-20"), xend = as.Date("2019-07-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2019-07-20"), xmax = as.Date("2019-07-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2019-07-20"), xend = as.Date("2019-07-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2019-07-20"), xmax = as.Date("2019-07-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2019-08-07"),as.Date("2019-08-07")), y = c(8,9), label = c("ER", "GPP"),size = 3)



df_stn5_metab <- full_join(df_stn5_metab,dates,by="date")

df_stn5_metab$GPP_mean_CO2 <- (df_stn5_metab$GPP_mean*44/32)
df_stn5_metab$GPP_97.5pct_CO2 <- (df_stn5_metab$GPP_97.5pct*44/32)
df_stn5_metab$ER_mean_CO2 <- (df_stn5_metab$ER_mean*44/32)
df_stn5_metab$ER_97.5pct_CO2 <- (df_stn1_metab$ER_97.5pct*44/32)


p_2 <- ggplot(df_stn5_metab%>%
            filter(date > as.Date("2021-06-15")& date < as.Date("2021-10-20")))  +
    geom_ribbon(aes(x=date,ymin=GPP_mean_CO2-GPP_97.5pct_CO2, ymax=GPP_mean_CO2+GPP_97.5pct_CO2),fill = "darkgreen",alpha=.3) +
  geom_line(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
  geom_point(aes(x=date,y=GPP_mean_CO2),color="darkgreen") +
    geom_ribbon(aes(x=date,ymin=ER_mean_CO2-ER_97.5pct_CO2, ymax=ER_mean_CO2+ER_97.5pct_CO2),fill = "darkorange",alpha=.3) +
  geom_line(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_point(aes(x=date,y=ER_mean_CO2),color="darkorange") +
  geom_hline(yintercept = 0) +
    ylab(expression(paste('Metabolim (g C' ~m^-2~y^-1,")"))) + xlab("Station 5: 2022") +
  theme_bw(base_size = 13)+
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 9, yend = 9, colour = "darkgreen") +
 annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 9-.2, ymax = 9+.2, fill="darkgreen", alpha = .3) +
  annotate("segment", x = as.Date("2021-06-20"), xend = as.Date("2021-06-30"), y = 8, yend = 8, colour = "darkorange") +
   annotate("rect", xmin = as.Date("2021-06-20"), xmax = as.Date("2021-06-30"), ymin = 8-.2, ymax = 8+.2, fill="darkorange", alpha = .3) + 
  annotate("text", x = c(as.Date("2021-07-05"),as.Date("2021-07-05")), y = c(8,9), label = c("ER", "GPP"),size = 3)


full_p <- plot_grid(p_1.2,p_1.1,NULL,p_2,labels =c("a","b","","c"),nrow=2,ncol=2)

```
#stn 1 and 5 comparison
```{r  compare, echo=FALSE}

#station 1
stn01 <- read.csv(here::here("data_cleaned/WL_01_cleaned.csv"))
stn01$DateTime <- as.POSIXct(stn01$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn01$Date <- as.Date(stn01$DateTime,format="%Y-%m-%d")
stn01_summary<- stn01 %>%group_by(Date)%>%
  summarise(discharge_stn01 = mean(Q_m3s),
            Watertemp_c = mean(WLTemp_c))

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn1_metab$GPP_mean <- ifelse(df_stn1_metab$GPP_mean < 0,0,df_stn1_metab$GPP_mean )
df_stn1_metab$Date <- as.Date(df_stn1_metab$date)
df_stn1_metab <- left_join(df_stn1_metab,stn01_summary,by="Date")
df_stn1_metab <- df_stn1_metab%>%select(Date,GPP_mean,ER_mean,Watertemp_c)
df_stn1_metab$Station <- "Stn01"
df_stn1_metab$GPP_mean_CO2 <- (df_stn1_metab$GPP_mean*44/32)
df_stn1_metab$ER_mean_CO2 <- (df_stn1_metab$ER_mean*44/32)
df_stn1_metab <- df_stn1_metab%>%select(Station,Date,GPP_mean_CO2,ER_mean_CO2,Watertemp_c)

#stn 5
stn05 <- read.csv(here::here("data_cleaned/WL_05_cleaned.csv"))
stn05$DateTime <- as.POSIXct(stn05$DateTime, format="%Y-%m-%d %H:%M",tz="UTC")
stn05$Date <- as.Date(stn05$DateTime,format="%Y-%m-%d")
stn05_summary<- stn05 %>%group_by(Date)%>%
  summarise(discharge_stn05 = mean(Q_m3s),
            Watertemp_c = mean(WLTemp_c))

df_stn5_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station5_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn5_metab$GPP_mean <- ifelse(df_stn5_metab$GPP_mean < 0,0,df_stn5_metab$GPP_mean )
df_stn5_metab$Date <- as.Date(df_stn5_metab$date)
df_stn5_metab <- left_join(df_stn5_metab,stn05_summary,by="Date")
#remove high flows
df_stn5_metab <- df_stn5_metab%>%filter(discharge_stn05 < .1)
df_stn5_metab$Station <- "Stn05"
df_stn5_metab$GPP_mean_CO2 <- (df_stn5_metab$GPP_mean*44/32)
df_stn5_metab$ER_mean_CO2 <- (df_stn5_metab$ER_mean*44/32)
df_stn5_metab <- df_stn5_metab%>%select(Station,Date,GPP_mean_CO2,ER_mean_CO2,Watertemp_c)

df_metab <- rbind(df_stn1_metab,df_stn5_metab)

DOC_2021 <- read.csv(here::here("DOC/DOC_9-1-2021_UNC_EDIT3.csv"))%>%select(Date,Station,DOC,TDN)%>%filter(Station=="Stn01"|Station=="Stn05")
DOC_2021$Date <- as.Date(DOC_2021$Date,format="%m/%d/%y")

df_full <- full_join(df_metab,DOC_2021,by=c("Date","Station"))




df_full_pivot <- df_full%>%select(!Date)%>%
  pivot_longer(!Station, names_to = "variable", values_to = "value")%>%drop_na(value)



p1 <- ggplot(df_full ,aes(x=Station,y=DOC,fill=Station)) +geom_boxplot()+   ylab(expression(paste('DOC'))) + xlab("") +
  scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(DOC ~ Station, data = df_full)
#summary(model)

p2 <- ggplot(df_full ,aes(x=Station,y=TDN,fill=Station)) +geom_boxplot()+   ylab(expression(paste('TDN'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 14)

model <- aov(TDN ~ Station, data = df_full)
#summary(model)

p3 <- ggplot(df_full ,aes(x=Station,y=GPP_mean_CO2,fill=Station)) +geom_boxplot()+  ylab(expression(paste('GPP'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(GPP_mean_CO2 ~ Station, data = df_full)
#summary(model)

p4 <- ggplot(df_full ,aes(x=Station,y=ER_mean_CO2,fill=Station)) +geom_boxplot() +
  ylab(expression(paste('ER'))) + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(ER_mean_CO2 ~ Station, data = df_full)
#summary(model)

p5 <- ggplot(df_full ,aes(x=Station,y=Watertemp_c,fill=Station)) +geom_boxplot() +
  ylab("Water temp.") + xlab("") +
    scale_x_discrete(labels= c("station 1","station 5")) +
  theme_bw(base_size = 12)

model <- aov(Watertemp_c ~ Station, data = df_full)
#summary(model)

p_full <- plot_grid(p3 + rremove("legend"),
                    p4 + rremove("legend"),
                 #   p5 + rremove("legend"),
                    p1 + rremove("legend"),
                    p2 + rremove("legend"),
                    #labels = "auto",
                    ncol=2,nrow=2)

full_p <- plot_grid(p_1.2,p_1.1,p_full,p_2,labels =c("a","b","c","d"),nrow=2,ncol=2)

```

# Departure

```{r  departure, echo=FALSE}

Stn01 <- read.csv(here::here("MergedFiles/Stn01_May7.csv"))
Stn01$Date <- as.Date(Stn01$Date)
Stn01 <- Stn01%>%drop_na(CO2_departure)%>%drop_na(DO_departure)
departure_metrics <- read.csv(here::here("Departure_files/departure_metrics_may6.csv"))
departure_metrics$date <- as.Date(departure_metrics$date)

plot_df <- left_join(departure_metrics ,Stn01,by=c("date"="Date"))
plot_df$month <- format(plot_df$date,"%m")
plot_df <- plot_df%>%drop_na(month)

plot_df <- plot_df %>%drop_na(month)%>%arrange(desc(month))
#plot_df$color_column <- ifelse(plot_df$month=="05","red","blue")

hex <- hue_pal()(7)
p <-ggplot(plot_df) +
  geom_smooth(aes(x = CO2_departure, y = DO_departure,color=as.factor(date)), formula = y ~ x,method='lm')+
    geom_point(aes(x = meanCO2dep, y = meanO2dep), color="black", shape=1) +
  theme_bw(base_size = 14)+
  theme(axis.line=element_blank(), panel.background=element_blank(), panel.border=element_blank(), panel.grid.major=element_blank()) +
  scale_color_manual(labels = NULL,
                     values = c("2019-07-13" = hex[5],
                                "2019-07-14" = hex[5],
                                "2019-07-15" = hex[5],
                                "2019-07-23" = hex[5],
                                "2019-07-24" = hex[5],
                                "2019-07-25" = hex[5],
                                "2019-07-27" = hex[5],
                                "2019-07-28" = hex[5],
                                "2019-07-30" = hex[5],
                                "2019-07-31" = hex[5],
                                "2019-08-02" = hex[6],
                                "2019-08-03" = hex[6],
                                "2019-08-04" = hex[6],
                                "2019-08-06" = hex[6],
                                "2019-08-07" = hex[6],
                                "2019-08-09" = hex[6],
                                "2019-08-10" = hex[6],
                                "2019-08-11" = hex[6],
                                "2019-08-12" = hex[6],
                                "2019-08-13" = hex[6],
                                "2021-06-12" = hex[6],
                                "2021-06-13" = hex[4],
                                "2021-06-14" = hex[4],
                                "2021-06-15" = hex[4],
                                "2021-06-16" = hex[4],
                                "2021-06-17" = hex[4],
                                "2021-06-18" = hex[4],
                                "2021-06-26" = hex[4],
                                "2021-06-27" = hex[4],
                                "2021-06-28" = hex[4],
                                "2021-06-29" = hex[4],
                                "2021-06-30" = hex[4],
                                "2021-07-01" = hex[5],
                                "2021-07-02" = hex[5],
                                "2021-07-03" = hex[5],
                                "2021-07-04" = hex[5],
                                "2021-07-05" = hex[5],
                                "2021-07-06" = hex[5],
                                "2021-07-07" = hex[5],
                                "2021-07-08" = hex[5],
                                "2021-07-09" = hex[5],
                                "2021-07-10" = hex[5],
                                "2021-07-11" = hex[5],
                                "2021-07-12" = hex[5],
                                "2021-07-29" = hex[5],
                                "2021-07-30" = hex[5],
                                "2021-07-31" = hex[5],
                                "2021-08-01" = hex[6],
                                "2021-08-02" = hex[6],
                                "2021-08-03" = hex[6],
                                "2021-08-05" = hex[6],
                                "2021-08-06" = hex[6],
                                "2021-08-07" = hex[6],
                                "2021-08-08" = hex[6],
                                "2021-08-09" = hex[6],
                                "2021-08-10" = hex[6],
                                "2021-08-11" = hex[6],
                                "2021-08-12" = hex[6],
                                "2021-08-13" = hex[6],
                                "2021-08-14" = hex[6],
                                "2021-08-15" = hex[6],
                                "2021-08-16" = hex[6],
                                "2021-08-17" = hex[6],
                                "2021-08-18" = hex[6],
                                "2021-08-19" = hex[6],
                                "2021-08-20" = hex[6],
                                "2021-08-23" = hex[6],
                                "2021-08-24" = hex[6],
                                "2021-08-25" = hex[6],
                                "2021-08-27" = hex[6],
                                "2021-08-28" = hex[6],
                                "2021-08-29" = hex[6],
                                "2021-08-30" = hex[6],
                                "2021-09-02" = hex[7],
                                "2021-09-03" = hex[7],
                                "2021-09-04" = hex[7],
                                "2021-09-05" = hex[7],
                                "2021-09-06" = hex[7],
                                "2021-09-07" = hex[7],
                                "2021-09-08" = hex[7],
                                "2021-09-09" = hex[7],
                                "2021-09-10" = hex[7],
                                "2021-09-11" = hex[7],
                                "2021-09-12" = hex[7],
                                "2021-09-13" = hex[7],
                                "2021-09-14" = hex[7],
                                "2021-09-15" = hex[7],
                                "2021-09-16" = hex[7],
                                "2021-09-17" = hex[7],
                                "2021-09-18" = hex[7],
                                "2021-09-19" = hex[7],
                                "2021-09-20" = hex[7],
                                "2021-09-23" = hex[7],
                                "2021-09-24" = hex[7],
                                "2021-09-25" = hex[7],
                                "2021-09-26" = hex[7],
                                "2021-09-27" = hex[7],
                            
                                "2022-03-17" = hex[1],
                                "2022-03-27" = hex[1],
                                "2022-04-13" = hex[2],
                                "2022-04-14" = hex[2],
                                "2022-04-15" = hex[2],
                                "2022-04-16" = hex[2],
                                "2022-04-17" = hex[2],
                                "2022-04-19" = hex[2],
                                "2022-04-20" = hex[2],
                                "2022-04-21" = hex[2],
                                "2022-04-22" = hex[2],
                                "2022-04-23" = hex[2],
                                "2022-04-24" = hex[2],
                                "2022-04-25" = hex[2],
                                
                                "2022-05-06" = hex[3],
                                "2022-05-07" = hex[3],
                                "2022-05-15" = hex[3],
                                "2022-05-16" = hex[3],
                                "2022-05-17" = hex[3],
                                "2022-05-18" = hex[3],
                                "2022-05-19" = hex[3],
                                "2022-05-20" = hex[3],
                                "2022-05-26" = hex[3],
                                "2022-05-27" = hex[3],
                                "2022-05-28" = hex[3],
                                "2022-05-29" = hex[3],
                                "2022-05-30" = hex[3]

                                )) +
   xlab(expression(CO[2] ~'departure ('~mu*'mol' ~ L^-1~')')) +
  ylab(expression(O[2] ~'departure ('~mu*'mol' ~ L^-1~')'))+
  geom_abline(intercept = 0, slope = -1,color="blue",linetype="dashed",linewidth=1) + 
  annotate('text', x = 60, y = 40, 
           label = expression('RQ = 1.9'~frac(CO[2], O[2])), size = 4, angle='330',color="black") +
  annotate('text', x = 40, y = -75, 
           label = '1:-1', size = 4, angle='300',color="blue") +
  xlim(-10,700) + ylim(-300,10) +
    geom_vline(xintercept = 0) + geom_hline(yintercept = 0) +
  coord_fixed()

plot_df$month_code <- format(as.Date(plot_df$date), "%B")
plot_df$month_code <- reorder(plot_df$month_code, as.numeric( plot_df$month))

#legend code
p_leg <-ggplot(plot_df) +
  geom_line(aes(x = CO2_departure, y = DO_departure,color=month_code),linewidth=2) +
  theme_bw(base_size = 14) +
# theme(legend.background=element_blank())# +
  labs(color = "month")

leg <- get_legend(p_leg)
p_full <- ggarrange(p+rremove("legend"),leg,widths = c(3,1))


```
#departure 2

```{r  departure2 , echo=FALSE}

departure_metrics <- read.csv(here::here("Departure_files/departure_metrics_may6.csv"))
departure_metrics$date <- as.Date(departure_metrics$date)
#read in other explanitory variabiles
stn01_LUX <- read.csv(here::here("data_cleaned/LUX_abovewater_01_cleaned.csv"))
stn01_LUX$DateTime <- as.POSIXct(stn01_LUX$DateTime,format="%m/%d/%Y %H:%M",tz='UTC')
stn01_LUX$date <- as.Date(stn01_LUX$DateTime)
stn01_LUX_summary <- stn01_LUX%>%group_by(date)%>%
  summarise(LUX_dayave=mean(LUX))

# la virgin
weather_station <- read.csv(here::here("Weather_station/M5025_SolarRed.csv"))
weather_station$date <- gsub('([0-9]+) .*', '\\1', weather_station$fecha)
weather_station$date <- as.Date(weather_station$date,format="%m/%d/%y")
weather_station_summary <- weather_station%>%group_by(date)%>%
  summarise(SolarRad_W.m2_dayave=mean(SolarRad_W.m2))

#metabolism

df_stn1_metab <- read.csv(here::here("StreamMetabolizer/Predictions_bestones/station1_calclight_march9.csv"))%>%drop_na(GPP_mean)%>%filter(GPP_Rhat < 1.05)%>%filter(ER_Rhat < 1.05)%>%filter(GPP_Rhat < 1.05)%>%filter(GPP_75pct >= 0)
df_stn1_metab$GPP_mean <- ifelse(df_stn1_metab$GPP_mean < 0,0,df_stn1_metab$GPP_mean )
df_stn1_metab$date <- as.Date(df_stn1_metab$date)


#join
departure_metrics <- left_join(departure_metrics,stn01_LUX_summary,by="date")
departure_metrics <- left_join(departure_metrics,weather_station_summary,by="date")
departure_metrics <- left_join(departure_metrics,df_stn1_metab%>%select(date,GPP_mean,ER_mean),by="date")

#check rising limbs
WL_02 <- read.csv(here::here("data_cleaned/WL_02_cleaned.csv"))
WL_02$DateTime_1 <- as.POSIXct(WL_02$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_02$DateTime <- ifelse(is.na(WL_02$DateTime_1)==TRUE,paste(WL_02$DateTime,"00:00:00",sep=" "),WL_02$DateTime )
WL_02$DateTime <- as.POSIXct(WL_02$DateTime,format="%Y-%m-%d %H:%M",tz="UTC")
WL_02$DateTime_1 <- NULL

########Best ones IMO#######

#offset v DO_ave is strong. Q is not related if we remove high flows

lm.1.1 <- lm(data=departure_metrics,offset*sqrt(2) ~ DO_mgL_ave)
summary(lm.1.1)

departure_metrics$month_code <- format(as.Date(departure_metrics$date), "%B")
departure_metrics$month_code <- reorder(departure_metrics$month_code, as.numeric( departure_metrics$month))

p2 <- ggplot(departure_metrics #%>%filter(Q_m3s_ave<0.02)
             ,aes(x=DO_mgL_ave,y=offset*sqrt(2)#,fill=log(Q_m3s_ave*1000)
                  )) + 
   geom_point() + 
    geom_smooth(method = lm, formula = y ~ x,color="blue") +
  ylab("Offset") + xlab(expression(paste("DO (mg"~l^-1~")"))) +
  scale_fill_continuous(
    name= expression('Discharge ( L'~s^-1~')'),
    breaks = c(log(50),log(15),log(5)), 
    labels = c("50", "15","5")) +
  theme_bw(base_size = 14) +
  theme(legend.position = "top") +
  annotate("text", label = paste0("atop('p-value < 0.001','adj. R-sq = 0.72')"),
           x = 5, y = 600, size = 3, parse = TRUE)



#strong relationship btw stretch and GPP, even better when high delta Q removed 
#stretch and ER not related
lm.1 <- lm(data=departure_metrics,stretch ~ GPP_mean)
summary(lm.1)
lm.2 <- lm(data=departure_metrics%>%filter(Q_mgL_delta<.008),stretch ~ GPP_mean)
summary(lm.2)

p5.1 <- ggplot(departure_metrics, aes(x=GPP_mean,y=stretch)) +
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x,color="blue") +
   xlab(expression(paste('Average GPP (g C' ,~m^-2~y^-1,")"))) + ylab("Stretch") +
  theme_bw(base_size = 14) +
  annotate("text", label = paste0("atop('p-value < 0.001','adj. R-sq = 0.33')"),
           x = 1.5, y = 500, size = 3, parse = TRUE)

p5.2 <- ggplot(departure_metrics%>%filter(Q_mgL_delta<.008), aes(x=GPP_mean,y=stretch)) + geom_point() +
  geom_smooth(method = lm, formula = y ~ x) +
   xlab(expression(paste('Average GPP (g C' ,~m^-2~y^-1,")"))) + ylab("Stretch") +
  theme_bw(base_size = 16) + ggtitle("high delta Q removed")

p_full1 <- ggarrange(p2,p5.1,widths = c(1,1),labels=c("b","c"))

p_full2 <- ggarrange(p_full,p_full1,heights = c(1.5,1),nrow = 2,
                     labels=c("a",""))


```
